### 2018-11-02 lab_notebook.Rmd
creating folders

---
title: "lab_notebook"
author: "Juliette Verstaen"
date: "November 2, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 2018-11-09 lab_notebook.Rmd
- loaded in data (projection and MPA now in .rds not .csv

@@
 ```
+
+#Loading packages
+```{r}
+suppressPackageStartupMessages({
+  library(tidyverse)
+  library(tidyr)
+  library(here)
+  library(ggplot2)
+  library(dplyr)
+  library(readxl)
+  library(devtools)
+  library(plotly)
+  library(base)
+  library(rio)
+})
+
+```
+
+#converting projection csv into rds
+no longer need the code because have already used it to create the files
+```{r}
+
+#Upside data
+#projection_data_csv <- read_csv("data/ProjectionData.csv")
+
+#saveRDS(projection_data_csv, "projection_data.rds")
+
+#WDPA_Nov2018.csv <- read_csv("data/WDPA_Nov2018.csv")
+
+#saveRDS(WDPA_Nov2018.csv, "WDPA_Nov2018.rds")
+
+```
+
+#Load Data
+```{r}
+
+#Corbet data: when countries began using RBFs
+countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
+
+#Upside data
+projection_data <- readRDS("data/projection_data.rds")
+
+#MPA data
+MPA <- readRDS("data/WDPA_Nov2018.rds")
+
+#RAMS
+load("data/DBdata-model_fits_included.RData")
+
+number_species <- unique(stock$scientificname)
+#341 different species
+
+```
+
+#RAM data wrangling
+```{r}
+
+ram <- select(timeseries_values_views, "stockid", "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")
+
+colnames(ram) <- c("stockid", "CommName", "Year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")
+
+ram_merge <- ram %>%
+  unite(Name_Year, "CommName", "Year", sep = "-")
+
+ITQ_projection_year <- ITQ_projection %>%
+  unite(Name_Year, "CommName", "Year", sep = "-")
+
+```
+
+Important/Necessary Data
+tcbest.data #the best estimate of catch for that stock
+tbbest.dat # the best estimate of biomass for that stock
+divbpref # B/bmsy
+divupref.data # u/umsy
+
+Juliette Notes:
+
+Handy functions for updating data frames:
+match()
+separate()
+
+Useful Websites:
+https://uc-r.github.io/tidyr
+
+#Data Wrangling: Projection and Countries ITQ
+```{r}
+
+#seperate out IdOrig column for Projection Data
+separate_projection <- projection_data %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "species"))
+    ###unsure what the last column actually is, double check
+
+head(separate_projection, 10)
+
+#reunite just the two parts we care about: agency and stock
+unite_projection <- separate_projection %>% unite(assess_id_short, agency, stock, sep = "-")
+
+#simplifying Countries ITQ with unique columns to prepare to merge
+countries_ITQ_simple <- select(countries_ITQ, "assess_id_short", "year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
+
+#rename year to be capitalized to merge with projection data
+colnames(countries_ITQ_simple) <- c("assess_id_short", "Year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
+
+#merging ITQ and Projection
+ITQ_projection_merge <- merge(unite_projection,countries_ITQ_simple, by = c("assess_id_short", "Year"))
+
+#cleaning it up
+ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, species, sep = "-")
+
+```

### 2018-11-09 lab_notebook.Rmd
- merged projection data and itq - fun graphs - trying to figure out how to update itq/projection with RAMS

@@
 
-#RAM data wrangling
-```{r}
-
-ram <- select(timeseries_values_views, "stockid", "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")
-
-colnames(ram) <- c("stockid", "CommName", "Year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")
-
-ram_merge <- ram %>%
-  unite(Name_Year, "CommName", "Year", sep = "-")
-
-ITQ_projection_year <- ITQ_projection %>%
-  unite(Name_Year, "CommName", "Year", sep = "-")
-
-```
-
 Important/Necessary Data
@@
 ```
+
+#Graphs for fun
+
+ABARES_BGRDRSE
+implemented ITQs in 1992
+```{r}
+
+ABARES_BGRDRSE <- filter(ITQ_projection, IdOrig == "ABARES-BGRDRSE-1960-2011-CHING")
+
+graph_ABARES_BGRDRSE <-ggplot(ABARES_BGRDRSE, aes(x=Year, y=Biomass))+
+  geom_line(size=1)+
+  ggtitle("ABARES_BGRDRSE (Australia")+
+  geom_point()+
+  geom_line()+
+  labs(x="Year", y="Yearly total biomass")+
+  theme_classic()+
+  scale_x_continuous(expand=c(0,0))+
+  scale_y_continuous(expand=c(0,0))+
+  geom_vline(xintercept = 1992)+
+  theme(legend.title=element_blank())
+
+ggplotly(graph_ABARES_BGRDRSE)
+
+#figure out an if then statement for line?
+
+```
+
+ADFG-HERRTOGE
+never implemented ITQs
+```{r}
+ADFG_HERRTOGE <- filter(ITQ_projection, IdOrig == "ADFG-HERRTOG-1990-2010-HIVELY")
+
+graph_ADFG_HERRTOGE <-ggplot(ADFG_HERRTOGE, aes(x=Year, y=Biomass))+
+  geom_line(size=1)+
+  ggtitle("ADFG-HERRTOGE (USA)")+
+  geom_point()+
+  geom_line()+
+  labs(x="Year", y="Yearly total biomass")+
+  theme_classic()+
+  scale_x_continuous(expand=c(0,0))+
+  scale_y_continuous(expand=c(0,0))+
+  theme(legend.title=element_blank())
+
+ggplotly(graph_ADFG_HERRTOGE)
+
+#figure out an if then statement for line?
+```
+
+#RAM data wrangling
+```{r}
+ram <- select(timeseries_values_views, "stockid", "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")
+
+colnames(ram) <- c("stockid", "CommName", "Year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")
+
+ram_merge <- ram %>%
+  unite(Name_Year, "CommName", "Year", sep = "-")
+
+ITQ_projection_year <- ITQ_projection %>%
+  unite(Name_Year, "CommName", "Year", sep = "-")
+```
+
+#Attemps at merging ITQ_projection with rams
+Playing with Data
+
+```{r}
+
+IdOrig <- unique(ITQ_projection$IdOrig)
+IdOrig
+#337 species total
+
+ITQ_projection_implemented <- filter(ITQ_projection, programstart != "NA")
+
+IdOrig_implemented <- unique(ITQ_projection_implemented$IdOrig)
+IdOrig_implemented
+#115 species with ITQ implemented
+
+```
+
+#Total number of species with stocks
+#Number of stocks with ITQs implemented
+```{r}
+IdOrig <- unique(ITQ_projection$IdOrig)
+IdOrig
+#337 species total
+
+ITQ_projection_implemented <- filter(ITQ_projection, programstart != "NA")
+
+IdOrig_implemented <- unique(ITQ_projection_implemented$IdOrig)
+IdOrig_implemented
+#115 species with ITQ implemented
+```
+
+Attemts at updating ITQ_projection with Rams
+```{r}
+
+##this doesn't work
+RAMS_ITQ_projection <- match(ITQ_projection_year$CommYear, ram_merge$CommYear)
+
+```

### 2018-11-09 lab_notebook.Rmd
edf turf data

@@
 
-number_species <- unique(stock$scientificname)
+#number_species <- unique(stock$scientificname)
 #341 different species
+
+#cooperative data from "Conservation incentives and collective choices in cooperative fisheries" paper (Ovando et al 2013)
+jc_coop <- read_csv("data/clean_cooperatives_data.csv")
 
@@
 
+```
+
+Playing with Data
+
+#Total number of species with stocks
+#Number of stocks with ITQs implemented
+```{r}
+IdOrig <- unique(ITQ_projection$IdOrig)
+IdOrig
+#337 species total
+
+ITQ_projection_implemented <- filter(ITQ_projection, programstart != "NA")
+
+IdOrig_implemented <- unique(ITQ_projection_implemented$IdOrig)
+IdOrig_implemented
+#115 species with ITQ implemented
 ```
@@
 
+Important/Necessary Data
+tcbest.data #the best estimate of catch for that stock
+tbbest.dat # the best estimate of biomass for that stock
+divbpref # B/bmsy
+divupref.data # u/umsy
+
 #RAM data wrangling
 ```{r}
-ram <- select(timeseries_values_views, "stockid", "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")
+ram <- select(timeseries_values_views, "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")
 
-colnames(ram) <- c("stockid", "CommName", "Year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")
+colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy")
 
@@
   unite(Name_Year, "CommName", "Year", sep = "-")
-```
 
-#Attemps at merging ITQ_projection with rams
-Playing with Data
-
-```{r}
-
-IdOrig <- unique(ITQ_projection$IdOrig)
-IdOrig
-#337 species total
-
-ITQ_projection_implemented <- filter(ITQ_projection, programstart != "NA")
-
-IdOrig_implemented <- unique(ITQ_projection_implemented$IdOrig)
-IdOrig_implemented
-#115 species with ITQ implemented
-
-```
-
-#Total number of species with stocks
-#Number of stocks with ITQs implemented
-```{r}
-IdOrig <- unique(ITQ_projection$IdOrig)
-IdOrig
-#337 species total
-
-ITQ_projection_implemented <- filter(ITQ_projection, programstart != "NA")
-
-IdOrig_implemented <- unique(ITQ_projection_implemented$IdOrig)
-IdOrig_implemented
-#115 species with ITQ implemented
 ```
@@
 
-##this doesn't work
+##this doesn't work; gives you vector not updated data frame
 RAMS_ITQ_projection <- match(ITQ_projection_year$CommYear, ram_merge$CommYear)
 
+#what happens when i just merge the two?
+#test_merge <- merge(ITQ_projection_year, ram_merge, by = c("Name_Year"))
+
 ```

### 2018-11-09 lab_notebook.Rmd
load edf data
- merged turf data into projection/ITQ datafram. issue: only 2 species from the edf data set match with the projection/ITQ data. will wait and see if Gina sends any more info on TURFS

@@
 jc_coop <- read_csv("data/clean_cooperatives_data.csv")
+
+#EDF turf data
+edf_turf <- read_excel("data/EDF_TURF_data.xlsx")
 
@@
 ```
+
+##edf turf data wrangling
+```{r}
+
+edf_turf_unite <- edf_turf %>% unite(SciName, genus, species, sep = " ")
+
+edf_turf_simple <- select(edf_turf_unite, "country", "start_date", "SciName")
+
+colnames(edf_turf_simple) <- c("Country", "turfstart", "SciName")
+
+##want to merge the edf simple with ITQ/Projections but maybe wait for Gina to respond with her TURF data
+##in ITQ data says only one species of fish in japan has TURFs but not true
+
+edf_projection_itq <- merge(ITQ_projection, edf_turf_simple, by = c("Country", "SciName"))
+#only three species from the EDF data match with the species from the upside/projection data; all in Japan
+
+```
+
+Need to create new dataset (half upside half ITQ): Species, turf/itq, country,and then matching all the parameters with the species

### 2018-11-11 lab_notebook.Rmd
playing with updating upside data

@@
   library(rio)
+  library(plyr)
 })
@@
 
+#RAM data wrangling
+```{r}
+ram <- select(timeseries_values_views, "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")
+
+colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy")
+
+ram_2012 <- ram %>%
+  filter(Year > "2012") 
+##this wont work because projection data has projected out past 2012. need to UPDATE
+
+#updated 
+projection_ram <- bind_rows(list(projection_data, ram_2012))
+
+2012-1950
+#62
+2050- 2012
+#38
+162+38
+
+acheck <- filter(projection_ram, Year == "2013") %>%
+  select("IdOrig", "CommName", "Year", "Biomass")
+
+acheck_count <- unique(acheck$IdOrig)
+acheck_count
+#4714
+
+yearcheck <- unique(projection_data$Year)
+yearcheck
+#101 years starts 1950 end 2050
+
+join_project_ram <- join(projection_data, ram, by = c("CommName", "Year"), type = "full")
+
+#check that is worked
+projectramcheck <- join_project_ram %>%
+  filter(Year == "2013") %>%
+  select("IdOrig", "Year", "CommName")
+
+unite_projection_commname <- projection_data %>% 
+  unite(name_year, CommName, Year, sep = "-")
+unite_ram_commname <- ram %>% 
+  unite (name_year, CommName, Year, sep = "-")
+join_project_ram_2 <- join(unite_projection_commname, unite_projection_commname, by = "name_year", type = "full")
+
+```
+
 #Data Wrangling: Projection and Countries ITQ
@@
 #seperate out IdOrig column for Projection Data
-separate_projection <- projection_data %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "species"))
+separate_projection <- projection_ram %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
     ###unsure what the last column actually is, double check
@@
 
-#merging ITQ and Projection
-ITQ_projection_merge <- merge(unite_projection,countries_ITQ_simple, by = c("assess_id_short", "Year"))
+ITQ_projection_merge <- merge(unite_projection, countries_ITQ_simple, by = c("assess_id_short", "Year"), all = TRUE)
 
 #cleaning it up
-ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, species, sep = "-")
+ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, data_enterer, sep = "-")
 
@@
 
-#RAM data wrangling
-```{r}
-ram <- select(timeseries_values_views, "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")
-
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy")
-
-ram_merge <- ram %>%
-  unite(Name_Year, "CommName", "Year", sep = "-")
-
-ITQ_projection_year <- ITQ_projection %>%
-  unite(Name_Year, "CommName", "Year", sep = "-")
-
-```
-
-Attemts at updating ITQ_projection with Rams
+Attempts at updating ITQ_projection with Rams
+#asked ana about this -> waiting to hear back
 ```{r}
@@
 ##edf turf data wrangling
+# waiting for data from Gina if its more comprehensive than the EDF one
 ```{r}

### 2018-11-11 scripts/projection_ITQ.Rmd
playing with updating upside data

--- 2018-11-09 lab_notebook.Rmd
@@
 ---
-title: "lab_notebook"
+title: "Updating Projection Data and Merging with ITQ"
 author: "Juliette Verstaen"
-date: "November 2, 2018"
+date: "November 11, 2018"
 output: html_document
@@
 
-#Loading packages
+#Load Packages
+
 ```{r}
@@
   library(rio)
+  library(plyr)
 })
-
-```
-
-#converting projection csv into rds
-no longer need the code because have already used it to create the files
-```{r}
-
-#Upside data
-#projection_data_csv <- read_csv("data/ProjectionData.csv")
-
-#saveRDS(projection_data_csv, "projection_data.rds")
-
-#WDPA_Nov2018.csv <- read_csv("data/WDPA_Nov2018.csv")
-
-#saveRDS(WDPA_Nov2018.csv, "WDPA_Nov2018.rds")
-
 ```
@@
 
-#Corbet data: when countries began using RBFs
-countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
-
 #Upside data
 projection_data <- readRDS("data/projection_data.rds")
-
-#MPA data
-MPA <- readRDS("data/WDPA_Nov2018.rds")
 
@@
 
-#number_species <- unique(stock$scientificname)
-#341 different species
-
-#cooperative data from "Conservation incentives and collective choices in cooperative fisheries" paper (Ovando et al 2013)
-jc_coop <- read_csv("data/clean_cooperatives_data.csv")
-
+#Corbet data: when countries began using RBFs
+countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
 ```
 
-Important/Necessary Data
-tcbest.data #the best estimate of catch for that stock
-tbbest.dat # the best estimate of biomass for that stock
-divbpref # B/bmsy
-divupref.data # u/umsy
+#RAM Data Tiddying
+```{r}
+ram <- timeseries_values_views %>%
+  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
+  add_column("RAM")
 
-Juliette Notes:
+colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
+```
 
-Handy functions for updating data frames:
-match()
-separate()
+#Updata Projection with RAM
+```{r}
+projection_updated <- join(projection_data, ram, by = c("CommName", "Year"), type = "full")
+```
 
-Useful Websites:
-https://uc-r.github.io/tidyr
-
-#Data Wrangling: Projection and Countries ITQ
+#Merge Projection and ITQ
 ```{r}
@@
 #seperate out IdOrig column for Projection Data
-separate_projection <- projection_data %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "species"))
+separate_projection <- projection_updated %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
     ###unsure what the last column actually is, double check
@@
 
-#merging ITQ and Projection
-ITQ_projection_merge <- merge(unite_projection,countries_ITQ_simple, by = c("assess_id_short", "Year"))
+ITQ_projection_merge <- merge(unite_projection, countries_ITQ_simple, by = c("assess_id_short", "Year"), all = TRUE)
 
 #cleaning it up
-ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, species, sep = "-")
-
+ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, data_enterer, sep = "-")
 ```
-
-Playing with Data
 
@@
 ```
-
-#Graphs for fun
-
-ABARES_BGRDRSE
-implemented ITQs in 1992
-```{r}
-
-ABARES_BGRDRSE <- filter(ITQ_projection, IdOrig == "ABARES-BGRDRSE-1960-2011-CHING")
-
-graph_ABARES_BGRDRSE <-ggplot(ABARES_BGRDRSE, aes(x=Year, y=Biomass))+
-  geom_line(size=1)+
-  ggtitle("ABARES_BGRDRSE (Australia")+
-  geom_point()+
-  geom_line()+
-  labs(x="Year", y="Yearly total biomass")+
-  theme_classic()+
-  scale_x_continuous(expand=c(0,0))+
-  scale_y_continuous(expand=c(0,0))+
-  geom_vline(xintercept = 1992)+
-  theme(legend.title=element_blank())
-
-ggplotly(graph_ABARES_BGRDRSE)
-
-#figure out an if then statement for line?
-
-```
-
-ADFG-HERRTOGE
-never implemented ITQs
-```{r}
-ADFG_HERRTOGE <- filter(ITQ_projection, IdOrig == "ADFG-HERRTOG-1990-2010-HIVELY")
-
-graph_ADFG_HERRTOGE <-ggplot(ADFG_HERRTOGE, aes(x=Year, y=Biomass))+
-  geom_line(size=1)+
-  ggtitle("ADFG-HERRTOGE (USA)")+
-  geom_point()+
-  geom_line()+
-  labs(x="Year", y="Yearly total biomass")+
-  theme_classic()+
-  scale_x_continuous(expand=c(0,0))+
-  scale_y_continuous(expand=c(0,0))+
-  theme(legend.title=element_blank())
-
-ggplotly(graph_ADFG_HERRTOGE)
-
-#figure out an if then statement for line?
-```
-
-Important/Necessary Data
-tcbest.data #the best estimate of catch for that stock
-tbbest.dat # the best estimate of biomass for that stock
-divbpref # B/bmsy
-divupref.data # u/umsy
-
-#RAM data wrangling
-```{r}
-ram <- select(timeseries_values_views, "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")
-
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy")
-
-ram_merge <- ram %>%
-  unite(Name_Year, "CommName", "Year", sep = "-")
-
-ITQ_projection_year <- ITQ_projection %>%
-  unite(Name_Year, "CommName", "Year", sep = "-")
-
-```
-
-Attemts at updating ITQ_projection with Rams
-```{r}
-
-##this doesn't work; gives you vector not updated data frame
-RAMS_ITQ_projection <- match(ITQ_projection_year$CommYear, ram_merge$CommYear)
-
-#what happens when i just merge the two?
-#test_merge <- merge(ITQ_projection_year, ram_merge, by = c("Name_Year"))
-
-```

### 2018-11-11 lab_notebook.Rmd
updated projection data merged ITQ data simplified data frame for regressions

@@
 ```{r}
-ram <- select(timeseries_values_views, "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")
+ram <- timeseries_values_views %>%
+  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
+  add_column("RAM")
 
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy")
+colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
 
-ram_2012 <- ram %>%
-  filter(Year > "2012") 
+#ram_2012 <- ram %>%
+#  filter(Year > "2012") 
 ##this wont work because projection data has projected out past 2012. need to UPDATE
@@
 #updated 
-projection_ram <- bind_rows(list(projection_data, ram_2012))
+#projection_ram <- bind_rows(list(projection_data, ram_2012))
 
@@
 
-#check that is worked
-projectramcheck <- join_project_ram %>%
-  filter(Year == "2013") %>%
-  select("IdOrig", "Year", "CommName")
+projectramcheck <- filter(join_project_ram, IdOrig == "NA")
+#returns no rows with NA, could still be right if updated projected
 
-unite_projection_commname <- projection_data %>% 
-  unite(name_year, CommName, Year, sep = "-")
-unite_ram_commname <- ram %>% 
-  unite (name_year, CommName, Year, sep = "-")
-join_project_ram_2 <- join(unite_projection_commname, unite_projection_commname, by = "name_year", type = "full")
+#Checking to see if better way to do join
+# end up with WAY to many rows, something is off
+#unite_projection_commname <- projection_data %>% 
+#  unite(name_year, CommName, Year, sep = "-")
+#unite_ram_commname <- ram %>% 
+#  unite (name_year, CommName, Year, sep = "-")
+#join_project_ram_2 <- join(unite_projection_commname, unite_projection_commname, by = "name_year", type = "left")
+
+match_project_ram <- match(projection_data, ram)
 
@@
 ```{r}
-IdOrig <- unique(ITQ_projection$IdOrig)
+IdOrig <- unique(ITQ_projection$SciName)
 IdOrig
-#337 species total
+#1228 species total
 
@@
 
-IdOrig_implemented <- unique(ITQ_projection_implemented$IdOrig)
+IdOrig_implemented <- unique(ITQ_projection_implemented$SciName)
 IdOrig_implemented
-#115 species with ITQ implemented
+#80 species with ITQ implemented
 ```

### 2018-11-11 scripts/projection_ITQ.Rmd
updated projection data merged ITQ data simplified data frame for regressions

@@
 
-IdOrig_implemented <- unique(ITQ_projection_implemented$IdOrig)
+IdOrig_implemented <- unique(ITQ_projection_implemented$SciName)
 IdOrig_implemented
-#115 species with ITQ implemented
+#80 species with ITQ implemented
 ```
+
+#Simplified Projection Data
+```{r}
+
+ITQ_projection_simple <- ITQ_projection %>%
+  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi", "yearitq", "itq_now", "turf", "programstart")
+
+```

### 2018-11-13 scripts/updating_projection.R
creating script fro updating data saving updating projection to rds file

@@ -1,0 +1,77 @@
+#Load Packages
+suppressPackageStartupMessages({
+  library(tidyverse)
+  library(tidyr)
+  library(here)
+  library(ggplot2)
+  library(dplyr)
+  library(readxl)
+  library(devtools)
+  library(plotly)
+  library(base)
+  library(rio)
+  library(plyr)
+})
+
+
+#Load Data
+#Upside data
+projection_data <- readRDS("data/projection_data.rds")
+
+#RAMS
+load("data/DBdata-model_fits_included.RData")
+
+#Corbet data: when countries began using RBFs
+countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
+
+
+
+#RAM Data Tiddying
+ram <- timeseries_values_views %>%
+  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
+  add_column("RAM")
+
+colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
+
+
+
+#Update Projection with RAM
+projection_updated <- join(projection_data, ram, by = c("CommName", "Year"), type = "full")
+
+#Merge Projection and ITQ
+#seperate out IdOrig column for Projection Data
+separate_projection <- projection_updated %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
+
+head(separate_projection, 10)
+
+#reunite just the two parts we care about: agency and stock
+unite_projection <- separate_projection %>% unite(assess_id_short, agency, stock, sep = "-")
+
+#simplifying Countries ITQ with unique columns to prepare to merge
+countries_ITQ_simple <- select(countries_ITQ, "assess_id_short", "year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
+
+#rename year to be capitalized to merge with projection data
+colnames(countries_ITQ_simple) <- c("assess_id_short", "Year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
+
[…]

### 2018-11-14 lab_notebook.Rmd
in progress

@@
 
-edf_turf_simple <- select(edf_turf_unite, "country", "start_date", "SciName")
+edf_turf_simple <- edf_turf_unite %>%
+  add_column("turf") %>%
+  select("country", "start_date", "SciName") %>%
+  gsub('\\bNA NA\\b', 'NA')
 
@@
 Need to create new dataset (half upside half ITQ): Species, turf/itq, country,and then matching all the parameters with the species
+
+################
+################
+###############
+PART 2
+
+From updating_projection.R script file
+```{r}
+
+#Load Data
+#Upside data
+projection_data <- readRDS("data/projection_data.rds")
+
+#RAMS
+load("data/DBdata-model_fits_included.RData")
+
+#Corbet data: when countries began using RBFs
+countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
+
+#RAM Data Tiddying
+ram <- timeseries_values_views %>%
+  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
+  add_column("RAM")
+
+colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
+
+#Update Projection with RAM
+projection_updated <- join(projection_data, ram, by = c("CommName", "Year"), type = "full")
+
+#Merge Projection and ITQ
+#seperate out IdOrig column for Projection Data
+separate_projection <- projection_updated %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
+
+head(separate_projection, 10)
+
+#reunite just the two parts we care about: agency and stock
+unite_projection <- separate_projection %>% unite(assess_id_short, agency, stock, sep = "-")
+
+#simplifying Countries ITQ with unique columns to prepare to merge
+countries_ITQ_simple <- select(countries_ITQ, "assess_id_short", "year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
+
+#rename year to be capitalized to merge with projection data
+colnames(countries_ITQ_simple) <- c("assess_id_short", "Year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
+
+ITQ_projection_merge <- merge(unite_projection, countries_ITQ_simple, by = c("assess_id_short", "Year"), all = TRUE)
+
+#cleaning it up
+ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, data_enterer, sep = "-")
+
+#Simplified Projection Data
+ITQ_projection_simple <- ITQ_projection %>%
+  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi", "yearitq", "itq_now","iq", "itq", "ivq", "turf", "programstart")
+
+#create RDS from datafram
+#saveRDS(ITQ_projection_simple, "projection_updated.rds")
+
+```
+
+1) pull the ITQ, IVQ, IQ fisheries out of upside.
+2) pull the TURF fisheries from EDF.
+3) For each fishery, we want species, location, and ITQ vs. TURF.
+
+```{r}
+
+# create dataframe with 
+itq <- ITQ_projection %>%
+  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "yearitq", "itq_now","iq", "itq", "ivq", "turf", "programstart")
+
+#Load EDF TURF data
+
+edf_turf <- read_excel("data/EDF_TURF_data.xlsx")
+
+```
+
+```{r}
+
+edf_turf_unite <- edf_turf %>% unite(SciName, genus, species, sep = " ")
+
+edf_turf_simple <- select(edf_turf_unite, "country", "start_date", "SciName")
+
+colnames(edf_turf_simple) <- c("Country", "programstart", "SciName")
+
+##want to merge the edf simple with ITQ/Projections but maybe wait for Gina to respond with her TURF data
+##in ITQ data says only one species of fish in japan has TURFs but not true
+
+edf_projection_1 <- join(edf_turf_simple, itq, by = c("Country", "programstart", "SciName"), type = "full")
+
+```

### 2018-11-14 scripts/updating_projection.R

@@ -63,8 +63,8 @@ ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf
 ITQ_projection_simple <- ITQ_projection %>%
   select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi", "yearitq", "itq_now", "turf", "programstart")
 
-#create CSV file from datafram
-write.csv(ITQ_projection_simple, file = "ITQ_projection_updated.csv")
+#create RDS from datafram
+#saveRDS(ITQ_projection_simple, "projection_updated.rds")
 
 
 

### 2018-11-15 lab_notebook.Rmd
combine discover turf, edf, rams, upside.
not fully cleaned up yet

@@
 itq <- ITQ_projection %>%
-  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "yearitq", "itq_now","iq", "itq", "ivq", "turf", "programstart")
+  select("Country", "Year", "SciName", "itq_now","iq", "itq", "ivq", "turf", "programstart")
 
@@
 
+#load in DiscoverTURFs data
+
+d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx")
+
 ```
@@
 
-edf_turf_unite <- edf_turf %>% unite(SciName, genus, species, sep = " ")
+edf_turf_simple <- select(edf_turf, "country", "start_date", "SciName", "turf")
+#create new column that says "turf" and TRUE or FALSE
 
-edf_turf_simple <- select(edf_turf_unite, "country", "start_date", "SciName")
+colnames(edf_turf_simple) <- c("Country", "programstart", "SciName", "turf")
 
-colnames(edf_turf_simple) <- c("Country", "programstart", "SciName")
+#combining edf turf data from upside data
+edf_projection_1 <- join(edf_turf_simple, itq, by = c("Country", "programstart", "SciName", "turf"), type = "full")
 
-##want to merge the edf simple with ITQ/Projections but maybe wait for Gina to respond with her TURF data
-##in ITQ data says only one species of fish in japan has TURFs but not true
+#combine edf/upside with discover turfs
+all_turf_1 <- join(edf_projection_1, d_turfs, by = c("Country", "SciName", "turf"), type = "full")
 
-edf_projection_1 <- join(edf_turf_simple, itq, by = c("Country", "programstart", "SciName"), type = "full")
+#change "blank" NAs to real NAs
+all_turf_1[is.na(all_turf_1)] <- "NA"
+
+#rearrange columns
+all_turf_2 <- all_turf_1[, c(1,3,5,2,6,7,8,9,4)]
+
+#turning NAs from no ITQ data to FALSE
+
+all_turf_2 %>% replace(is.na(.), FALSE)
 

### 2018-11-15 lab_notebook.Rmd
creating turf/itq data set almost done

@@
 ```{r}
+
 suppressPackageStartupMessages({
@@
 
-#Simplified Projection Data
+#simplified projection data
 ITQ_projection_simple <- ITQ_projection %>%
@@
 
-#create RDS from datafram
+#create RDS from dataframe
 #saveRDS(ITQ_projection_simple, "projection_updated.rds")
+
+#upside updated
+upside_2018_updated <- ITQ_projection %>%
+  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi")
+
+#create RDS from dataframe
+#saveRDS(upside_2018_updated, "upside_2018_updated")
 
@@
 itq <- ITQ_projection %>%
-  select("Country", "Year", "SciName", "itq_now","iq", "itq", "ivq", "turf", "programstart")
+  select("Country", "SciName", "itq_now","iq", "itq", "ivq", "turf", "programstart")
 
@@
 #rearrange columns
-all_turf_2 <- all_turf_1[, c(1,3,5,2,6,7,8,9,4)]
+all_turf_2 <- all_turf_1[, c(1,3,2,5,6,7,8,4)]
 
 #turning NAs from no ITQ data to FALSE
+#all_turf_2$itq_now[all_turf_2$itq_now == 0] <- NA
 
-all_turf_2 %>% replace(is.na(.), FALSE)
+#all_turf_2 %>% replace(is.na(.), FALSE)
+
+#doublecheckworked <- all_turf_2 %>%
+#  filter( itq_now == "1" & turf == "TRUE")
 

### 2018-11-15 scripts/itq_turf_data.R

@@ -1,0 +1,49 @@
+##Creating datafram with countries, species, and itq/turf info
+
+#Load Packages
+suppressPackageStartupMessages({
+  library(tidyverse)
+  library(tidyr)
+  library(here)
+  library(ggplot2)
+  library(dplyr)
+  library(readxl)
+  library(devtools)
+  library(plotly)
+  library(base)
+  library(rio)
+  library(plyr)
+})
+
+#load data
+
+ITQ_projection <- readRDS("processed_data/ITQ_projection.rds")
+
+# create dataframe with 
+itq <- ITQ_projection %>%
+  select("Country", "SciName", "itq_now","iq", "itq", "ivq", "turf", "programstart")
+
+#Load EDF TURF data
+edf_turf <- read_excel("data/EDF_TURF_data.xlsx")
+
+#load in DiscoverTURFs data
+d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx")
+
+#data tidyying
+edf_turf_simple <- select(edf_turf, "country", "start_date", "SciName", "turf")
+
+colnames(edf_turf_simple) <- c("Country", "programstart", "SciName", "turf")
+
+#combining edf turf data from upside data
+edf_projection_1 <- join(edf_turf_simple, itq, by = c("Country", "programstart", "SciName", "turf"), type = "full")
+
+#combine edf/upside with discover turfs
+all_turf_1 <- join(edf_projection_1, d_turfs, by = c("Country", "SciName", "turf"), type = "full")
+
+#change "blank" NAs to real NAs
+all_turf_1[is.na(all_turf_1)] <- "NA"
+
+#rearrange columns
+all_turf_2 <- all_turf_1[, c(1,3,2,5,6,7,8,4)]
+
+#rename itq_now from NA -> 0 and all other NAs to FALSE

### 2018-11-15 scripts/updating_projection.R

@@ -60,6 +60,7 @@ ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf
 
 
 #Simplified Projection Data
+#this includes ITQ information
 ITQ_projection_simple <- ITQ_projection %>%
   select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi", "yearitq", "itq_now", "turf", "programstart")
 
@@ -67,6 +68,13 @@ ITQ_projection_simple <- ITQ_projection %>%
 #saveRDS(ITQ_projection_simple, "projection_updated.rds")
 
 
+#upside updated
+#this does not include ITQ information
+upside_2018_updated <- ITQ_projection %>%
+  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi")
+
+#create RDS from dataframe
+#saveRDS(upside_2018_updated, "upside_2018_updated")
 
 
 

### 2018-11-15 lab_notebook.Rmd
updated turf/itq data finished

@@
 
+#create RDS from dataframe
+#saveRDS(ITQ_projection, "ITQ_projection")
+
 #simplified projection data
@@
 
+#load data
 ```{r}
@@
 # create dataframe with 
+ITQ_projection <- readRDS("processed_data/ITQ_projection.rds")
+
 itq <- ITQ_projection %>%
@@
 
+#data wrangling
 ```{r}
@@
 #change "blank" NAs to real NAs
-all_turf_1[is.na(all_turf_1)] <- "NA"
+#all_turf_1[is.na(all_turf_1)] <- "NA"
 
 #rearrange columns
-all_turf_2 <- all_turf_1[, c(1,3,2,5,6,7,8,4)]
+all_turf_itq <- all_turf_1[, c(1,3,2,5,6,7,8,4)]
 
 #turning NAs from no ITQ data to FALSE
-#all_turf_2$itq_now[all_turf_2$itq_now == 0] <- NA
+#all_turf_2[all_turf_2 == 0] <- NA
 
-#all_turf_2 %>% replace(is.na(.), FALSE)
+all_turf_itq$iq[is.na(all_turf_itq$iq)] <- FALSE
 
-#doublecheckworked <- all_turf_2 %>%
-#  filter( itq_now == "1" & turf == "TRUE")
+all_turf_itq$itq[is.na(all_turf_itq$itq)] <- FALSE
+
+all_turf_itq$ivq[is.na(all_turf_itq$ivq)] <- FALSE
+
+all_turf_itq$itq_now[is.na(all_turf_itq$itq_now)] <- 0
+
+#create RDS from dataframe
+#saveRDS(all_turf_itq, "all_turf_itq.rds")
+#write.csv(all_turf_itq, file = "all_turf_itq.csv")
 

### 2018-11-15 scripts/itq_turf_data.R

@@ -1,4 +1,6 @@
-##Creating datafram with countries, species, and itq/turf info
+################################################################
+##Creating dataframe with countries, species, and itq/turf info##
+################################################################
 
 #Load Packages
 suppressPackageStartupMessages({
@@ -44,6 +46,17 @@ all_turf_1 <- join(edf_projection_1, d_turfs, by = c("Country", "SciName", "turf
 all_turf_1[is.na(all_turf_1)] <- "NA"
 
 #rearrange columns
-all_turf_2 <- all_turf_1[, c(1,3,2,5,6,7,8,4)]
+all_turf_itq <- all_turf_1[, c(1,3,2,5,6,7,8,4)]
 
-#rename itq_now from NA -> 0 and all other NAs to FALSE
+#turning NAs from no ITQ data to FALSE
+#all_turf_2[all_turf_2 == 0] <- NA
+
+all_turf_itq$iq[is.na(all_turf_itq$iq)] <- FALSE
+
+all_turf_itq$itq[is.na(all_turf_itq$itq)] <- FALSE
+
+all_turf_itq$ivq[is.na(all_turf_itq$ivq)] <- FALSE
+
+all_turf_itq$itq_now[is.na(all_turf_itq$itq_now)] <- 0
+
+

### 2018-11-15 scripts/updating_projection.R

@@ -75,6 +75,7 @@ upside_2018_updated <- ITQ_projection %>%
 
 #create RDS from dataframe
 #saveRDS(upside_2018_updated, "upside_2018_updated")
+write.csv(upside_2018_updated, file = "upside_2018_updated")
 
 
 

### 2018-11-15 scripts/updating_projection.R
forgot to save a file

@@ -1,3 +1,8 @@
+####################################
+##Updating Upside Data with RAMS##
+###################################
+
+
 #Load Packages
 suppressPackageStartupMessages({
   library(tidyverse)

### 2018-11-17 lab_notebook.Rmd
simplified itq/turf data - only species that are turf, itq, ivq, iq - fishery only represented once per country

@@
 PART 2
+1) pull the ITQ, IVQ, IQ fisheries out of upside.
+2) pull the TURF fisheries from EDF.
+3) For each fishery, we want species, location, and ITQ vs. TURF.
 
@@
 
-1) pull the ITQ, IVQ, IQ fisheries out of upside.
-2) pull the TURF fisheries from EDF.
-3) For each fishery, we want species, location, and ITQ vs. TURF.
-
 #load data
@@
 ```
+
+###################
+##################
+
+Part 3
+
+1) include only species that are either TURF, ITQ, IVQ, etc. (omit species that are FALSE for everything).
+2) Include each fishery only once (not multiple years).
+3) so then see how hard it is to collect other characteristics for each species (like growth rate or ISCAAP category).
+
+```{r}
+
+#filter out all countries that don't have itqs or turfs
+true_turf_itq_1 <- all_turf_itq %>%
+  filter (iq == "TRUE" | itq == "TRUE" | ivq == "TRUE" | turf == "TRUE") %>%
+  filter( Country != "NA") %>%
+  select("Country", "SciName", "iq", "itq", "ivq", "turf")
+
+true_turf_itq <- unique(true_turf_itq_1 [ , 1:6])
+
+unique(true_turf_itq$Country)
+#33 countries
+#Chile, Fiji, Italy, Japan, Mexico, Papua New Guinea, Samoa, Solomon Islands, Spain, Sri Lanka, Sweden, Vanuatu, Vietnam, Australia, USA, Canada, Peru, Argentina, South Africa, New Zealand, American Samoa, Belize, Brazil, Ecuador, France, Greece, India, Netherlands, Nigeria, Philippines, St Lucia, United States, United Kingdom
+
+#chile_itq_turf <- filter(only_turf_itq, Country == "Chile")
+unique(chile_itq_turf$SciName)
+# 67
+
+#fiji_itq_turf <- filter(only_turf_itq, Country == "Fiji")
+#unique(fiji_itq_turf$SciName)
+
+#test_duplicate <- unique(fiji_itq_turf[ , 1:8])
+
+```

### 2018-11-17 lab_notebook.Rmd
playing with fishbase

@@
 
+1 & 2
 ```{r}
@@
 
-#chile_itq_turf <- filter(only_turf_itq, Country == "Chile")
-unique(chile_itq_turf$SciName)
+#chile_itq_turf <- filter(true_turf_itq, Country == "Chile")
+#unique(chile_itq_turf$SciName)
 # 67
@@
 ```
+
+3
+ISCAAP
+```{r}
+
+iscaap_cat_1 <- upside_2018_updated %>%
+  select("SciName", "SpeciesCat")
+
+iscaap_cat <- unique(iscaap_cat_1 [ , 1:2])
+
+true_turf_itq_iscaap_1 <- merge(true_turf_itq, iscaap_cat, by = "SciName", all = T)
+
+true_turf_itq_iscaap <- true_turf_itq_iscaap_1 %>%
+  filter( itq != "NA" & ivq != "NA" & iq != "NA" & turf != "NA")
+
+true_turf_itq_iscaap[is.na(true_turf_itq_iscaap)] <- "NA"
+
+missing_speccat <- true_turf_itq_iscaap %>%
+  filter(SpeciesCat == "NA")
+
+determine_spec_cat <- as.vector(missing_speccat$SciName)
+determine_spec_cat
+
+```
+
+FishBase
+
+```{r}
+
+library("rfishbase")
+
+species <- as.vector(true_turf_itq_iscaap$SciName)
+species
+
+table_species <- species(species)
+
+#fishtest <- species_list(Genus = "Labroides")
+#fishtest
+#species(fishtest)
+#even running the practice online tutorial get this error :Error in curl::curl_fetch_memory(url, handle = handle) : Timeout was reached: Connection timed out after 10004 milliseconds
+
+#fishbase_test <- validate_names(species, fields = c("Species", ""))
+
+```

### 2018-11-25 lab_notebook.Rmd
playing with fishbase
making sure scripts run and are organized and adding species_rightsbased file

@@
 
+#write.csv(true_turf_itq_iscaap, file = "true_turf_itq_iscaap.csv")
+
 determine_spec_cat <- as.vector(missing_speccat$SciName)
@@
 
+growth <- popgrowth(species)
+
 #fishtest <- species_list(Genus = "Labroides")
@@
 ```
+
+FAO website with fisheries data is currently unavaliable. Updated by hand for now; read in below 
+```{r}
+species_rightsbased <- read_csv("processed_data/species_rightsbased.csv")
+```
+-	used FAO 3-Alpha species codes (ASFIS) updated 2/2009
+-	ones with no ISSCAPP # still are shellfish, snails, crabs, not species specific, common name, species in NA, or a family name with more than 1 #

### 2018-11-25 scripts/itq_turf_data.R

@@ -31,8 +31,10 @@ edf_turf <- read_excel("data/EDF_TURF_data.xlsx")
 #load in DiscoverTURFs data
 d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx")
 
-#data tidyying
+
 edf_turf_simple <- select(edf_turf, "country", "start_date", "SciName", "turf")
+#create new column that says "turf" and TRUE or FALSE
+
 
 colnames(edf_turf_simple) <- c("Country", "programstart", "SciName", "turf")
 
@@ -43,7 +45,7 @@ edf_projection_1 <- join(edf_turf_simple, itq, by = c("Country", "programstart",
 all_turf_1 <- join(edf_projection_1, d_turfs, by = c("Country", "SciName", "turf"), type = "full")
 
 #change "blank" NAs to real NAs
-all_turf_1[is.na(all_turf_1)] <- "NA"
+#all_turf_1[is.na(all_turf_1)] <- "NA"
 
 #rearrange columns
 all_turf_itq <- all_turf_1[, c(1,3,2,5,6,7,8,4)]
@@ -59,4 +61,29 @@ all_turf_itq$ivq[is.na(all_turf_itq$ivq)] <- FALSE
 
 all_turf_itq$itq_now[is.na(all_turf_itq$itq_now)] <- 0
 
+#filter out all countries that don't have itqs or turfs
+true_turf_itq_1 <- all_turf_itq %>%
+  filter (iq == "TRUE" | itq == "TRUE" | ivq == "TRUE" | turf == "TRUE") %>%
+  filter( Country != "NA") %>%
+  select("Country", "SciName", "iq", "itq", "ivq", "turf") 
 
+true_turf_itq <- unique(true_turf_itq_1 [ , 1:6])
+
+##Using ISSCAPP species numbers from upsideside data
+iscaap_cat_1 <- upside_2018_updated %>%
+  select("SciName", "SpeciesCat") 
+
+iscaap_cat <- unique(iscaap_cat_1 [ , 1:2])
+
+true_turf_itq_iscaap_1 <- merge(true_turf_itq, iscaap_cat, by = "SciName", all = T)
+
+true_turf_itq_iscaap <- true_turf_itq_iscaap_1 %>%
+  filter( itq != "NA" & ivq != "NA" & iq != "NA" & turf != "NA") 
+
[…]

### 2018-11-25 scripts/updating_projection.R

@@ -80,7 +80,7 @@ upside_2018_updated <- ITQ_projection %>%
 
 #create RDS from dataframe
 #saveRDS(upside_2018_updated, "upside_2018_updated")
-write.csv(upside_2018_updated, file = "upside_2018_updated")
+#write.csv(upside_2018_updated, file = "upside_2018_updated")
 
 
 

### 2018-11-29 lab_notebook.Rmd
nothing
gdp data and start of logit

@@
 -	ones with no ISSCAPP # still are shellfish, snails, crabs, not species specific, common name, species in NA, or a family name with more than 1 #
+
+###########
+11/26/2018
+
+```{r}
+
+species_rightsbased <- read_csv("data/species_rightsbased_binary.csv")
+
+upside_2018_updated <- readRDS("/GitHub/global_fisheries_managment/processed_data/upside_2018_updated.rds")
+
+gdp_all <- read_csv("/GitHub/global_fisheries_managment/data/gpd.csv")
+
+```
+
+Part 4:
+For TURF/ITQ data, add GDP/capita for each country, also do ISCAAP categories. Combine all ITQ,IQ etc. Run logit of Prob(ITQ) = f(ISCAAP, GDP).
+
+```{r}
+
+gdp <- filter(gdp_all, current_gdp != "NA")
+
+join_gdp_rightsbased <- join(gdp, species_rightsbased, by = c("Country"), type = "full")
+
+gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )
+
+```
+
+```{r}
+
+as_factor <- gdp_rightsbased$i_right
+as_factor <- gdp_rightsbased$turf
+
+itq_glm <- glm(i_right ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
+itq_glm
+
+turf_glm <- glm(turf ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
+turf_glm
+
+```

### 2018-11-29 lab_notebook.Rmd
edited f_b_rights

@@
 ###########
-11/26/2018
 
+Part 4:
+For TURF/ITQ data, add GDP/capita for each country, also do ISCAAP categories. Combine all ITQ,IQ etc. Run logit of Prob(ITQ) = f(ISCAAP, GDP).
 ```{r}
@@
 ```
-
-Part 4:
-For TURF/ITQ data, add GDP/capita for each country, also do ISCAAP categories. Combine all ITQ,IQ etc. Run logit of Prob(ITQ) = f(ISCAAP, GDP).
 
@@
 
-as_factor <- gdp_rightsbased$i_right
-as_factor <- gdp_rightsbased$turf
+#gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
 
-itq_glm <- glm(i_right ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
+itq_glm <- glm(formula = i_right ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
 itq_glm
 
-turf_glm <- glm(turf ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
-turf_glm
+#turf_glm <- glm(turf ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
+#turf_glm
 
 ```
+
+Part 5:
+RAM only: F/Fmsy vs. B/Bmsy for all fisheries. Color ITQ differently.
+
+```{r}
+
+ITQ_projection <- readRDS("processed_data//not_actively_used/ITQ_projection.rds")
+
+f_b_itq <- ITQ_projection %>%
+  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq") %>%
+  filter( itq != "NA", iq != "NA", ivq != "NA")
+
+#write.csv(f_b_itq, file = "f_b_itq.csv")
+f_b_irights <- read_csv("data/f_b_irights.csv")
+
+F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights ))+
+  geom_point()+
+  labs(x = "B/Bmsy", y= "F/Fsmy") +
+  theme_minimal()+
+  theme(legend.title=element_blank())+
+  ylim(-1, 22)+
+  xlim(-.3, 3)+
+  geom_hline(aes(yintercept=1))+
+  geom_vline(aes(xintercept=1))
+
+#F_B_graph
+ggplotly(F_B_graph)
+
+```

### 2018-12-04 lab_notebook.Rmd
glm Prob(ITQ) ~F(gdp, ISSCAAP)

@@
 
+#write.csv(gdp_rightsbased, file = "gdp_rightsbased.csv")
+
 ```
@@
 ```
+
+######
+MPA data wrangling
+######
+```{r}
+
+ISO_country_codes <- read_excel("data/ISO_country_codes.xlsx")
+MPA <- readRDS("data/WDPA_Nov2018.rds")
+
+mpa_simple <- MPA %>%
+  select("NAME", "PA_DEF", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS", "PARENT_ISO3") %>%
+  filter(MARINE != "0")
+
+colnames(mpa_simple) <- c("NAME", "PA_DEF", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS", "code")
+
+mpa_join <- join(mpa_simple, ISO_country_codes, by = c("code"), type = "full")
+
+mpa_updated <- mpa_join %>%
+  select("Country", "NAME", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS" ) %>%
+  filter(NAME != "NA" & DESIG_ENG != "NA" & DESIG_TYPE != "NA" & IUCN_CAT != "NA" & MARINE != "NA" & REP_M_AREA != "NA" & NO_TAKE != "NA" & STATUS != "NA")
+
+write.csv(mpa_updated, file = "mpa_updated.csv")
+
+```
+
+PA_DEF: Allowed values: 1 (meets IUCN and/or CBD PA definition); 0 (does not meet IUCN and/or CBD PA definition (currently stored outside WDPA)).
+
+MARINE: Allowed values: 0 (100% Terrestrial PA), 1 (Coastal: marine and terrestrial PA), and 2 (100 % marine PA).

### 2018-12-07 lab_notebook.Rmd
Rmarkdown for 12/6 meeting
going back and fixing some of the fisheries post 2012 in updated upside that are na for itqs but had them before

@@
 separate_projection <- projection_ram %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
-    ###unsure what the last column actually is, double check
 
@@
 #create RDS from dataframe
-#saveRDS(ITQ_projection, "ITQ_projection")
+saveRDS(ITQ_projection, "ITQ_projection.rds")
 
@@
 
-#gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
+##make sure that these stats are not effected by year 2012 onward not having info on itq or not. i think this data was not year specific so it should be fine? but look at the data
+
+gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
 
@@
 
+summary(itq_glm)
+
 #turf_glm <- glm(turf ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
 #turf_glm
+#summary(turf_glm)
 
@@
 
-F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights ))+
+# get data frame that was
+F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights, size = catch ))+
   geom_point()+
@@
 
-write.csv(mpa_updated, file = "mpa_updated.csv")
+#write.csv(mpa_updated, file = "mpa_updated.csv")
 
@@
 MARINE: Allowed values: 0 (100% Terrestrial PA), 1 (Coastal: marine and terrestrial PA), and 2 (100 % marine PA).
+
+#############
+############
+1.	From upside want to know the catch in ITQ versus non ITQ for most recent year
+
+- issues: unsure what year real data ends and projectio/modeling begins
+- pretty sure its 2016. there are thee fisheries with 2017 data in the updated RAMS dataset but more for 2016
+
+update recent years fisheries
+
+issue: the projection data updated with RAMs doens't have ITQ data associated with the countries
+- need a list of all the countries and whether or not they have ITQ in 2016 -> this can be pulled from Corbett's data. need to check if his data is from that year
+
+```{r}
+ITQ_projection <- readRDS("data/ITQ_projection.rds")
+
+#filter down the data to create a data set of countries that have ITQs so I can add that to the rams data. upside has this info but not the updated part
+
+#2012 is the most updated version of the upside data.
+used this to figure out which counties have ITQs and will make a data frame from that of a list of countires that have itqs and then update the final datafram (or inital rams dataframe)
+countries_with_ITQ <- ITQ_projection %>%
+  select (Country, itq, iq, ivq, Year, IdOrig) %>%
+  filter(Year == "2012")
+
+countries_with_ITQ_2 <- unique(countries_with_ITQ[, 1:6])
+countries_with_ITQ_3 <- filter(countries_with_ITQ_2, itq != "NA" | iq != "NA" | ivq != "NA")
+
+countries_with_ITQ_3$rightsbased <- 1
+countries_itq_2012 <- select(countries_with_ITQ_3, Country, IdOrig, rightsbased)
+
+#now need to create new column thats rights based fishereise 0 o for projection 2016
+
+ITQ_projection_2016 <- ITQ_projection %>%
+  filter(Year == "2016") %>%
+  select(IdOrig, Country, Catch)
+
+itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012, by= c("IdOrig", "Country"), type= "full")
+
+itq_2016_updated$rightsbased[is.na(itq_2016_updated$rightsbased)] <- 0
+
+#seperate rights based and not
+itq_2016_rightsbasedTRUE <- filter(itq_2016_updated, rightsbased == "1")
+
+itq_2016_rightsbasedFALSE <- filter(itq_2016_updated, rightsbased == "0")
+
+sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
+#27,830,933
+sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
+#266,328,075
+
+##units???
+
+```
+
+In the updated ITQ projection data there are lines of data that have 2012 with NA instead of TRUE/FALSE for itq.
+
+#data we have says that Mexico does not have ITQs?
+in 2012 only ones it says we have are Australia, USA, Canda, Japan, Peru, Argentina, South Africa, New Zealand
+
+Fixing upsie data
+- take ITQ projection an filter it down to idorig, year, BvBmsy", "FvFmsy", "itq", "iq", "ivq"
+- filter out just ones with itqs, create a column thats rights based fisherse and make it one
+- filter out specifics of itq
+- merge/join that data with the countries_itq2012 with country, idorig, and rihgts based
+- make nas zero
+-redo kobe plot with this data
+- also cut off at 5
+
+```{r}
+
+ITQ_projection <- readRDS("processed_data//not_actively_used/ITQ_projection.rds")
+
+countries_with_ITQ <- ITQ_projection %>%
+  select (Country, itq, iq, ivq, Year, IdOrig) %>%
+  filter(Year == "2012")
+
+countries_with_ITQ_2 <- unique(countries_with_ITQ[, 1:6])
+countries_with_ITQ_3 <- filter(countries_with_ITQ_2, itq != "NA" | iq != "NA" | ivq != "NA")
+
+countries_with_ITQ_3$rightsbased <- 1
+countries_itq_2012 <- select(countries_with_ITQ_3, Country, IdOrig, rightsbased)
+
+##need to update projection data
+
+f_b_itq <- ITQ_projection %>%
+  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq") %>%
+  filter( itq != "NA", iq != "NA", ivq != "NA")
+
+#write.csv(f_b_itq, file = "f_b_itq.csv")
+f_b_irights <- read_csv("data/f_b_irights.csv")
+
+# get data frame that was
+F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights, size = catch ))+
+  geom_point()+
+  labs(x = "B/Bmsy", y= "F/Fsmy") +
+  theme_minimal()+
+  theme(legend.title=element_blank())+
+  ylim(-1, 22)+
+  xlim(-.3, 3)+
+  geom_hline(aes(yintercept=1))+
+  geom_vline(aes(xintercept=1))
+
+#F_B_graph
+ggplotly(F_B_graph)
+
+```

### 2018-12-07 lab_notebook_2.Rmd
going back and fixing some of the fisheries post 2012 in updated upside that are na for itqs but had them before

--- 2018-11-29 lab_notebook.Rmd
@@
 ---
-title: "lab_notebook"
+title: "lab_notebook_2"
 author: "Juliette Verstaen"
-date: "November 2, 2018"
+date: "12/7/2018"
 output: html_document
@@
 })
-
-```
-
-#converting projection csv into rds
-no longer need the code because have already used it to create the files
-```{r}
-
-#Upside data
-#projection_data_csv <- read_csv("data/ProjectionData.csv")
-
-#saveRDS(projection_data_csv, "projection_data.rds")
-
-#WDPA_Nov2018.csv <- read_csv("data/WDPA_Nov2018.csv")
-
-#saveRDS(WDPA_Nov2018.csv, "WDPA_Nov2018.rds")
 
@@
 ```
-
-Important/Necessary Data
-tcbest.data #the best estimate of catch for that stock
-tbbest.dat # the best estimate of biomass for that stock
-divbpref # B/bmsy
-divupref.data # u/umsy
-
-Juliette Notes:
-
-Handy functions for updating data frames:
-match()
-separate()
-
-Useful Websites:
-https://uc-r.github.io/tidyr
-
-#RAM data wrangling
-```{r}
-ram <- timeseries_values_views %>%
-  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
-  add_column("RAM")
-
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
-
-#ram_2012 <- ram %>%
-#  filter(Year > "2012") 
-##this wont work because projection data has projected out past 2012. need to UPDATE
-
-#updated 
-#projection_ram <- bind_rows(list(projection_data, ram_2012))
-
-2012-1950
-#62
-2050- 2012
-#38
-162+38
-
-acheck <- filter(projection_ram, Year == "2013") %>%
-  select("IdOrig", "CommName", "Year", "Biomass")
-
-acheck_count <- unique(acheck$IdOrig)
-acheck_count
-#4714
-
-yearcheck <- unique(projection_data$Year)
-yearcheck
-#101 years starts 1950 end 2050
-
-join_project_ram <- join(projection_data, ram, by = c("CommName", "Year"), type = "full")
-
-projectramcheck <- filter(join_project_ram, IdOrig == "NA")
-#returns no rows with NA, could still be right if updated projected
-
-#Checking to see if better way to do join
-# end up with WAY to many rows, something is off
-#unite_projection_commname <- projection_data %>% 
-#  unite(name_year, CommName, Year, sep = "-")
-#unite_ram_commname <- ram %>% 
-#  unite (name_year, CommName, Year, sep = "-")
-#join_project_ram_2 <- join(unite_projection_commname, unite_projection_commname, by = "name_year", type = "left")
-
-match_project_ram <- match(projection_data, ram)
-
-```
-
-#Data Wrangling: Projection and Countries ITQ
-```{r}
-
-#seperate out IdOrig column for Projection Data
-separate_projection <- projection_ram %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
-    ###unsure what the last column actually is, double check
-
-head(separate_projection, 10)
-
-#reunite just the two parts we care about: agency and stock
-unite_projection <- separate_projection %>% unite(assess_id_short, agency, stock, sep = "-")
-
-#simplifying Countries ITQ with unique columns to prepare to merge
-countries_ITQ_simple <- select(countries_ITQ, "assess_id_short", "year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-#rename year to be capitalized to merge with projection data
-colnames(countries_ITQ_simple) <- c("assess_id_short", "Year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-ITQ_projection_merge <- merge(unite_projection, countries_ITQ_simple, by = c("assess_id_short", "Year"), all = TRUE)
-
-#cleaning it up
-ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, data_enterer, sep = "-")
-
-```
-
-Playing with Data
-
-#Total number of species with stocks
-#Number of stocks with ITQs implemented
-```{r}
-IdOrig <- unique(ITQ_projection$SciName)
-IdOrig
-#1228 species total
-
-ITQ_projection_implemented <- filter(ITQ_projection, programstart != "NA")
-
-IdOrig_implemented <- unique(ITQ_projection_implemented$SciName)
-IdOrig_implemented
-#80 species with ITQ implemented
-```
-
-#Graphs for fun
-
-ABARES_BGRDRSE
-implemented ITQs in 1992
-```{r}
-
-ABARES_BGRDRSE <- filter(ITQ_projection, IdOrig == "ABARES-BGRDRSE-1960-2011-CHING")
-
-graph_ABARES_BGRDRSE <-ggplot(ABARES_BGRDRSE, aes(x=Year, y=Biomass))+
-  geom_line(size=1)+
-  ggtitle("ABARES_BGRDRSE (Australia")+
-  geom_point()+
-  geom_line()+
-  labs(x="Year", y="Yearly total biomass")+
-  theme_classic()+
-  scale_x_continuous(expand=c(0,0))+
-  scale_y_continuous(expand=c(0,0))+
-  geom_vline(xintercept = 1992)+
-  theme(legend.title=element_blank())
-
-ggplotly(graph_ABARES_BGRDRSE)
-
-#figure out an if then statement for line?
-
-```
-
-ADFG-HERRTOGE
-never implemented ITQs
-```{r}
-ADFG_HERRTOGE <- filter(ITQ_projection, IdOrig == "ADFG-HERRTOG-1990-2010-HIVELY")
-
-graph_ADFG_HERRTOGE <-ggplot(ADFG_HERRTOGE, aes(x=Year, y=Biomass))+
-  geom_line(size=1)+
-  ggtitle("ADFG-HERRTOGE (USA)")+
-  geom_point()+
-  geom_line()+
-  labs(x="Year", y="Yearly total biomass")+
-  theme_classic()+
-  scale_x_continuous(expand=c(0,0))+
-  scale_y_continuous(expand=c(0,0))+
-  theme(legend.title=element_blank())
-
-ggplotly(graph_ADFG_HERRTOGE)
-
-#figure out an if then statement for line?
-```
-
-Important/Necessary Data
-tcbest.data #the best estimate of catch for that stock
-tbbest.dat # the best estimate of biomass for that stock
-divbpref # B/bmsy
-divupref.data # u/umsy
-
-Attempts at updating ITQ_projection with Rams
-#asked ana about this -> waiting to hear back
-```{r}
-
-##this doesn't work; gives you vector not updated data frame
-RAMS_ITQ_projection <- match(ITQ_projection_year$CommYear, ram_merge$CommYear)
-
-#what happens when i just merge the two?
-#test_merge <- merge(ITQ_projection_year, ram_merge, by = c("Name_Year"))
-
-```
-
-##edf turf data wrangling
-# waiting for data from Gina if its more comprehensive than the EDF one
-```{r}
-
-edf_turf_unite <- edf_turf %>% unite(SciName, genus, species, sep = " ")
-
-edf_turf_simple <- edf_turf_unite %>%
-  add_column("turf") %>%
-  select("country", "start_date", "SciName") %>%
-  gsub('\\bNA NA\\b', 'NA')
-
-colnames(edf_turf_simple) <- c("Country", "turfstart", "SciName")
-
-##want to merge the edf simple with ITQ/Projections but maybe wait for Gina to respond with her TURF data
-##in ITQ data says only one species of fish in japan has TURFs but not true
-
-edf_projection_itq <- merge(ITQ_projection, edf_turf_simple, by = c("Country", "SciName"))
-#only three species from the EDF data match with the species from the upside/projection data; all in Japan
-
-```
-
-Need to create new dataset (half upside half ITQ): Species, turf/itq, country,and then matching all the parameters with the species
-
-################
-################
-###############
-PART 2
-1) pull the ITQ, IVQ, IQ fisheries out of upside.
-2) pull the TURF fisheries from EDF.
-3) For each fishery, we want species, location, and ITQ vs. TURF.
-
-From updating_projection.R script file
-```{r}
-
-#Load Data
-#Upside data
-projection_data <- readRDS("data/projection_data.rds")
-
-#RAMS
-load("data/DBdata-model_fits_included.RData")
-
-#Corbet data: when countries began using RBFs
-countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
-
-#RAM Data Tiddying
-ram <- timeseries_values_views %>%
-  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
-  add_column("RAM")
-
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
-
-#Update Projection with RAM
-projection_updated <- join(projection_data, ram, by = c("CommName", "Year"), type = "full")
-
-#Merge Projection and ITQ
-#seperate out IdOrig column for Projection Data
-separate_projection <- projection_updated %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
-
-head(separate_projection, 10)
-
-#reunite just the two parts we care about: agency and stock
-unite_projection <- separate_projection %>% unite(assess_id_short, agency, stock, sep = "-")
-
-#simplifying Countries ITQ with unique columns to prepare to merge
-countries_ITQ_simple <- select(countries_ITQ, "assess_id_short", "year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-#rename year to be capitalized to merge with projection data
-colnames(countries_ITQ_simple) <- c("assess_id_short", "Year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-ITQ_projection_merge <- merge(unite_projection, countries_ITQ_simple, by = c("assess_id_short", "Year"), all = TRUE)
-
-#cleaning it up
-ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, data_enterer, sep = "-")
-
-#create RDS from dataframe
-#saveRDS(ITQ_projection, "ITQ_projection")
-
-#simplified projection data
-ITQ_projection_simple <- ITQ_projection %>%
-  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi", "yearitq", "itq_now","iq", "itq", "ivq", "turf", "programstart")
-
-#create RDS from dataframe
-#saveRDS(ITQ_projection_simple, "projection_updated.rds")
-
-#upside updated
-upside_2018_updated <- ITQ_projection %>%
-  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi")
-
-#create RDS from dataframe
-#saveRDS(upside_2018_updated, "upside_2018_updated")
-
-```
-
-#load data
-```{r}
-
-# create dataframe with 
-ITQ_projection <- readRDS("processed_data/ITQ_projection.rds")
-
-itq <- ITQ_projection %>%
-  select("Country", "SciName", "itq_now","iq", "itq", "ivq", "turf", "programstart")
-
-#Load EDF TURF data
-
-edf_turf <- read_excel("data/EDF_TURF_data.xlsx")
-
-#load in DiscoverTURFs data
-
-d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx")
-
-```
-
-#data wrangling
-```{r}
-
-edf_turf_simple <- select(edf_turf, "country", "start_date", "SciName", "turf")
-#create new column that says "turf" and TRUE or FALSE
-
-colnames(edf_turf_simple) <- c("Country", "programstart", "SciName", "turf")
-
-#combining edf turf data from upside data
-edf_projection_1 <- join(edf_turf_simple, itq, by = c("Country", "programstart", "SciName", "turf"), type = "full")
-
-#combine edf/upside with discover turfs
-all_turf_1 <- join(edf_projection_1, d_turfs, by = c("Country", "SciName", "turf"), type = "full")
-
-#change "blank" NAs to real NAs
-#all_turf_1[is.na(all_turf_1)] <- "NA"
-
-#rearrange columns
-all_turf_itq <- all_turf_1[, c(1,3,2,5,6,7,8,4)]
-
-#turning NAs from no ITQ data to FALSE
-#all_turf_2[all_turf_2 == 0] <- NA
-
-all_turf_itq$iq[is.na(all_turf_itq$iq)] <- FALSE
-
-all_turf_itq$itq[is.na(all_turf_itq$itq)] <- FALSE
-
-all_turf_itq$ivq[is.na(all_turf_itq$ivq)] <- FALSE
-
-all_turf_itq$itq_now[is.na(all_turf_itq$itq_now)] <- 0
-
-#create RDS from dataframe
-#saveRDS(all_turf_itq, "all_turf_itq.rds")
-#write.csv(all_turf_itq, file = "all_turf_itq.csv")
-
-```
-
-###################
-##################
-
-Part 3
-
-1) include only species that are either TURF, ITQ, IVQ, etc. (omit species that are FALSE for everything).
-2) Include each fishery only once (not multiple years).
-3) so then see how hard it is to collect other characteristics for each species (like growth rate or ISCAAP category).
-
-1 & 2
-```{r}
-
-#filter out all countries that don't have itqs or turfs
-true_turf_itq_1 <- all_turf_itq %>%
-  filter (iq == "TRUE" | itq == "TRUE" | ivq == "TRUE" | turf == "TRUE") %>%
-  filter( Country != "NA") %>%
-  select("Country", "SciName", "iq", "itq", "ivq", "turf")
-
-true_turf_itq <- unique(true_turf_itq_1 [ , 1:6])
-
-unique(true_turf_itq$Country)
-#33 countries
-#Chile, Fiji, Italy, Japan, Mexico, Papua New Guinea, Samoa, Solomon Islands, Spain, Sri Lanka, Sweden, Vanuatu, Vietnam, Australia, USA, Canada, Peru, Argentina, South Africa, New Zealand, American Samoa, Belize, Brazil, Ecuador, France, Greece, India, Netherlands, Nigeria, Philippines, St Lucia, United States, United Kingdom
-
-#chile_itq_turf <- filter(true_turf_itq, Country == "Chile")
-#unique(chile_itq_turf$SciName)
-# 67
-
-#fiji_itq_turf <- filter(only_turf_itq, Country == "Fiji")
-#unique(fiji_itq_turf$SciName)
-
-#test_duplicate <- unique(fiji_itq_turf[ , 1:8])
-
-```
-
-3
-ISCAAP
-```{r}
-
-iscaap_cat_1 <- upside_2018_updated %>%
-  select("SciName", "SpeciesCat")
-
-iscaap_cat <- unique(iscaap_cat_1 [ , 1:2])
-
-true_turf_itq_iscaap_1 <- merge(true_turf_itq, iscaap_cat, by = "SciName", all = T)
-
-true_turf_itq_iscaap <- true_turf_itq_iscaap_1 %>%
-  filter( itq != "NA" & ivq != "NA" & iq != "NA" & turf != "NA")
-
-true_turf_itq_iscaap[is.na(true_turf_itq_iscaap)] <- "NA"
-
-missing_speccat <- true_turf_itq_iscaap %>%
-  filter(SpeciesCat == "NA")
-
-#write.csv(true_turf_itq_iscaap, file = "true_turf_itq_iscaap.csv")
-
-determine_spec_cat <- as.vector(missing_speccat$SciName)
-determine_spec_cat
-
-```
-
-FishBase
-
-```{r}
-
-library("rfishbase")
-
-species <- as.vector(true_turf_itq_iscaap$SciName)
-species
-
-table_species <- species(species)
-
-growth <- popgrowth(species)
-
-#fishtest <- species_list(Genus = "Labroides")
-#fishtest
-#species(fishtest)
-#even running the practice online tutorial get this error :Error in curl::curl_fetch_memory(url, handle = handle) : Timeout was reached: Connection timed out after 10004 milliseconds
-
-#fishbase_test <- validate_names(species, fields = c("Species", ""))
-
-```
-
-FAO website with fisheries data is currently unavaliable. Updated by hand for now; read in below 
-```{r}
-species_rightsbased <- read_csv("processed_data/species_rightsbased.csv")
-```
--	used FAO 3-Alpha species codes (ASFIS) updated 2/2009
--	ones with no ISSCAPP # still are shellfish, snails, crabs, not species specific, common name, species in NA, or a family name with more than 1 #
-
-###########
-
-Part 4:
-For TURF/ITQ data, add GDP/capita for each country, also do ISCAAP categories. Combine all ITQ,IQ etc. Run logit of Prob(ITQ) = f(ISCAAP, GDP).
-```{r}
-
-species_rightsbased <- read_csv("data/species_rightsbased_binary.csv")
-
-upside_2018_updated <- readRDS("/GitHub/global_fisheries_managment/processed_data/upside_2018_updated.rds")
-
-gdp_all <- read_csv("/GitHub/global_fisheries_managment/data/gpd.csv")
-
-```
-
-```{r}
-
-gdp <- filter(gdp_all, current_gdp != "NA")
-
-join_gdp_rightsbased <- join(gdp, species_rightsbased, by = c("Country"), type = "full")
-
-gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )
-
-```
-
-```{r}
-
-#gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
-
-itq_glm <- glm(formula = i_right ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
-itq_glm
-
-#turf_glm <- glm(turf ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
-#turf_glm
-
-```
-
-Part 5:
-RAM only: F/Fmsy vs. B/Bmsy for all fisheries. Color ITQ differently.
-
-```{r}
-
-ITQ_projection <- readRDS("processed_data//not_actively_used/ITQ_projection.rds")
-
-f_b_itq <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA")
-
-#write.csv(f_b_itq, file = "f_b_itq.csv")
-f_b_irights <- read_csv("data/f_b_irights.csv")
-
-F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(-1, 22)+
-  xlim(-.3, 3)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))
-
-#F_B_graph
-ggplotly(F_B_graph)
-
-```

### 2018-12-09 draft_figures.Rmd
probability functions for itq and turfs

---
title: "Draft_Figures"
author: "Juliette Verstaen"
date: "12/9/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

suppressPackageStartupMessages({
  library(tidyverse)
  library(tidyr)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(readxl)
  library(devtools)
  library(plotly)
  library(base)
  library(rio)
  library(plyr)
})
```

##From upside data: ITQ versus non ITQ and the size of dot is the catch

Note: Corbett's ITQ data is only until 2012. Chris's upside data is now updated until 2016 with the more recent RAM data that Dan had. I ran all the figure and regressions under two "scenerios":

    1. until 2012
    2. past 2012. extracted information about which fisheries had ITQs in 2012 and applied it   to the same fisheries into the future. This doesn't take into account other fisheries that   get ITQs in place during that time, or if fisheries stop ITQs

"KOBE" plots with ITQs not updated past 2012
```{r}

ITQ_projection <- readRDS("data/ITQ_projection.rds")

f_b_itq <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

F_B_graph <- ggplot(data = f_b_itq, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 5)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))

#F_B_graph
ggplotly(F_B_graph)

```

"KOBE" plots with ITQs updated past 2012
```{r}

ITQ_projection_updated <- readRDS("data/ITQ_projection_updated.rds")

f_b_itq_updated <- ITQ_projection_updated %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

F_B_graph_updated <- ggplot(data = f_b_itq_updated, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 5)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))

#F_B_graph
ggplotly(F_B_graph_updated)
```

##From upside: the catch in ITQ versus non ITQ for most recent year

Data until 2012
```{r}
ITQ_projection <- readRDS("data/ITQ_projection.rds")

f_b_itq_countries <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

countries_itq_2012 <- f_b_itq_countries %>%
  select (Country, rightsbased, Year, IdOrig, Catch) %>%
  filter(Year == "2012")

itq_2012_rightsbasedTRUE <- filter(countries_itq_2012, rightsbased == "1")

itq_2012_rightsbasedFALSE <- filter(countries_itq_2012, rightsbased == "0")

itq_2012_rightsbasedTURF <- filter(countries_itq_2012, rightsbased == "2")

sum(itq_2012_rightsbasedTRUE$Catch, na.rm = TRUE)
#7,420,003

sum(itq_2012_rightsbasedFALSE$Catch, na.rm = TRUE)
#142,231

sum(itq_2012_rightsbasedTURF$Catch, na.rm = TRUE)
#1,301,000
```
2012 total catch:
ITQs: 7,420,003
No ITQ: 142,231
TURF:1,301,000

Data past 2012
```{r}

ITQ_projection <- readRDS("data/ITQ_projection.rds")

f_b_itq_countries <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

countries_itq_2012 <- f_b_itq_countries %>%
  select (Country, rightsbased, Year, IdOrig, Catch) %>%
  filter(Year == "2012")

ITQ_projection_2016 <- ITQ_projection %>%
  filter(Year == "2016") %>%
  select(IdOrig, Country)

itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012, by= c("IdOrig", "Country"), type= "full")

itq_2016_rightsbasedTRUE <- filter(itq_2016_updated, rightsbased == "1")

itq_2016_rightsbasedFALSE <- filter(itq_2016_updated, rightsbased == "0")

itq_2016_rightsbasedTURF <- filter(itq_2016_updated, rightsbased == "2")

sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
#27,830,933

sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
#266,328,075

sum(itq_2016_rightsbasedTURF$Catch, na.rm = TRUE)
#1505000
```

2016 total catch:
ITQs: 27,830,933
No ITQ: 266,328,075
TURF:1,505,000

##Probability of ITQ

```{r}

species_rightsbased <- read_csv("data/species_rightsbased.csv")

gdp_all <- read_csv("/GitHub/global_fisheries_managment/data/gpd.csv")

gdp <- filter(gdp_all, current_gdp != "NA")

species_rightsbased_mutate <- species_rightsbased %>%
  mutate(i_right = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0")) %>%
  mutate(TURF = case_when(
    turf == TRUE ~ "1", 
    turf = FALSE ~"0"
  ))

##why does this value have NAs in the first place? when mutate is does line 1 first and not registering the false = 0 one. but i guess it doesn't matter beacuse its either one or the other? this is not happening for i_right so thats weird

species_rightsbased_mutate$TURF[is.na(species_rightsbased_mutate$TURF)] <- "0"

gdp <- filter(gdp_all, current_gdp != "NA")

join_gdp_rightsbased <- join(gdp, species_rightsbased_mutate, by = c("Country"), type = "full")

gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )

gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
gdp_rightsbased$i_right <- factor(gdp_rightsbased$i_right)

itq_glm <- glm(formula = i_right ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
itq_glm

summary(itq_glm)

```

### this code chunk and the one above should be the same but they are not. figure out why sinc eth two data frames are pulled from the same original info
```{r}

#ISSCAAP_species <- read_csv("data/ISSCAAP_species.csv")
#ITQ_projection <- readRDS("data/ITQ_projection.rds")

#ITQ_projection_isscaap_1 <- join(ISSCAAP_species,ITQ_projection, by = c("SciName", "SpeciesCat"), type = "full" )

#ITQ_projection_isscaap <- ITQ_projection_isscaap_1 %>%
 # filter(Country != "NA")

species_rightsbased <- read_csv("data/species_rightsbased.csv")

gdp_all <- read_csv("/GitHub/global_fisheries_managment/data/gpd.csv")

gdp <- filter(gdp_all, current_gdp != "NA")

species_rightsbased <- ITQ_projection_isscaap %>%
  select("SciName", "Country", "SpeciesCat", "itq", "iq", "ivq", "turf", "Catch") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(i_right = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0")) %>%
  mutate(turf = case_when(
    turf == TRUE ~ "1", 
    turf = FALSE ~"0"
  )) %>%
  select("SciName", "Country", "SpeciesCat", "i_right", "turf", "Catch")

species_rightsbased$turf[is.na(species_rightsbased$turf)] <- "0"

join_gdp_rightsbased <- join(gdp, species_rightsbased, by = c("Country"), type = "full")

gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )

gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
gdp_rightsbased$i_right <- factor(gdp_rightsbased$i_right)

itq_glm <- glm(formula = i_right ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
itq_glm

summary(itq_glm)

```

##Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one

```{r}
species_rightsbased <- read_csv("data/species_rightsbased.csv")

gdp_all <- read_csv("/GitHub/global_fisheries_managment/data/gpd.csv")

gdp <- filter(gdp_all, current_gdp != "NA")

species_rightsbased_mutate_2 <- species_rightsbased %>%
  mutate(rightbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "0",
    turf == TRUE ~ "1"))

gdp <- filter(gdp_all, current_gdp != "NA")

join_gdp_rightsbased_2 <- join(gdp, species_rightsbased_mutate_2, by = c("Country"), type = "full")

gdp_rightsbased_2 <- filter(join_gdp_rightsbased_2, SpeciesCat != "NA" )

gdp_rightsbased_2$SpeciesCat <- factor(gdp_rightsbased_2$SpeciesCat)
gdp_rightsbased_2$rightbased <- factor(gdp_rightsbased_2$rightbased)

rightbased_glm <- glm(formula = rightbased ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased_2)
rightbased_glm

summary(rightbased_glm)

```

### 2018-12-09 lab_notebook.Rmd
probability functions for itq and turfs

@@
 
+2. From upside sorts KOBE: ITQ versus non ITQ and the size of dot is the catch
+#this is all the data we have, make the same ones with only certain years and such
+
 ```{r}
@@
 f_b_itq <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA")
+  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch") %>%
+  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
+  mutate(rightsbased = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
 
+#turf == TRUE ~ "2",
 #write.csv(f_b_itq, file = "f_b_itq.csv")
-f_b_irights <- read_csv("data/f_b_irights.csv")
+#f_b_irights <- read_csv("data/f_b_irights.csv")
+#this was when i couldn't figure out how to do the if then statement in R
+
+#F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights, size = catch ))+
 
 # get data frame that was
-F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights, size = catch ))+
+F_B_graph <- ggplot(data = f_b_itq, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
   geom_point()+
@@
   theme(legend.title=element_blank())+
-  ylim(-1, 22)+
+  ylim(-1, 5)+
   xlim(-.3, 3)+
@@
 
+1.	From upside want to know the catch in ITQ versus non ITQ for most recent year
+corbet data only goes up until 2012 
+```{r}
+
+ITQ_projection <- readRDS("data/ITQ_projection.rds")
+
+f_b_itq_countries <- ITQ_projection %>%
+  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
+  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
+
+countries_itq_2012 <- f_b_itq_countries %>%
+  select (Country, rightsbased, Year, IdOrig, Catch) %>%
+  filter(Year == "2012")
+
+ITQ_projection_2016 <- ITQ_projection %>%
+  filter(Year == "2016") %>%
+  select(IdOrig, Country)
+
+itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012, by= c("IdOrig", "Country"), type= "full")
+
+itq_2016_rightsbasedTRUE <- filter(itq_2016_updated, rightsbased == "1")
+
+itq_2016_rightsbasedFALSE <- filter(itq_2016_updated, rightsbased == "0")
+
+itq_2016_rightsbasedTURF <- filter(itq_2016_updated, rightsbased == "2")
+
+sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
+#27,830,933
+sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
+#266,328,075
+
+sum(itq_2016_rightsbasedTURF$Catch, na.rm = TRUE)
+#1505000
+
+```
+
+updating projection datapast 2012  with the 2012 itq fisheries
+```{r}
+ITQ_projection <- readRDS("data/ITQ_projection.rds")
+
+f_b_itq_countries <- ITQ_projection %>%
+  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
+  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
+
+countries_itq_2012 <- f_b_itq_countries %>%
+  select (Country, rightsbased, Year, IdOrig, Catch) %>%
+  filter(Year == "2012")
+
+ITQ_projection_past2012 <- ITQ_projection %>%
+  filter(Year > 2012)
+
+ITQ_projection_past2012UPDATED <- join(ITQ_projection_past2012, countries_itq_2012, by = c("Country", "Year", "IdOrig"), type = "full" )
+
+ITQ_projection_pre2012 <- ITQ_projection %>%
+  filter(Year <= 2012)
+
+ITQ_projection_updated <- join(ITQ_projection_past2012UPDATED,ITQ_projection_pre2012, by = c("Country", "Year", "IdOrig"), type = "full")
+
+#saveRDS(ITQ_projection_updated, "ITQ_projection_updated.rds")
+
+ITQ_projection_updated <- readRDS("data/ITQ_projection_updated.rds")
+
+f_b_itq_updated <- ITQ_projection_updated %>%
+  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch") %>%
+  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
+  mutate(rightsbased = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
+
+F_B_graph_updated <- ggplot(data = f_b_itq_updated, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
+  geom_point()+
+  labs(x = "B/Bmsy", y= "F/Fsmy") +
+  theme_minimal()+
+  theme(legend.title=element_blank())+
+  ylim(-1, 5)+
+  xlim(-.3, 3)+
+  geom_hline(aes(yintercept=1))+
+  geom_vline(aes(xintercept=1))
+
+#F_B_graph
+ggplotly(F_B_graph_updated)
+
+```
+
+###Did this chunck before figured out how to do if/then statements in r
+
 ```{r}
@@
 
-Fixing upsie data
+Fixing upside data
 - take ITQ projection an filter it down to idorig, year, BvBmsy", "FvFmsy", "itq", "iq", "ivq"
@@
 
-```{r}
+#this was from before figured out if then statement
+
+ITQ_projection <- readRDS("data/ITQ_projection.rds")
+
+itq_selected <- ITQ_projection %>%
+  select(IdOrig,Country, Year, BvBmsy, FvFmsy, itq, iq, ivq) %>%
+  filter(itq != "NA" | iq != "NA" | ivq != "NA")
+
+itq_selected$rightsbased <- 1
+
+itq_selected_2 <- select(itq_selected,Country, IdOrig, Year, rightsbased)
+
+itq_new_join <- join(itq_selected_2, countries_itq_2012, by = c(Country, IdOrig, Year), type = "full")
+
+##not using this anymore
 
@@
   filter( itq != "NA", iq != "NA", ivq != "NA")
-
-#write.csv(f_b_itq, file = "f_b_itq.csv")
-f_b_irights <- read_csv("data/f_b_irights.csv")
-
-# get data frame that was
-F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights, size = catch ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(-1, 22)+
-  xlim(-.3, 3)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))
-
-#F_B_graph
-ggplotly(F_B_graph)
-
-```

### 2018-12-10 draft_figures.Rmd
mpa graph

@@
 ```
+##5.	For MPA filter only for those that are “All” for No Take
+a.	Total area for each country
+b.	Top ten countries by area
+i.	make a bar graph and each x-axis label is a country
+
+PA_DEF: Allowed values: 1 (meets IUCN and/or CBD PA definition); 0 (does not meet IUCN and/or CBD PA definition (currently stored outside WDPA)).
+
+MARINE: Allowed values: 0 (100% Terrestrial PA), 1 (Coastal: marine and terrestrial PA), and 2 (100 % marine PA).
+
+```{r}
+
+mpa_updated <- read_csv("data/mpa_updated.csv")
+
+mpa <- mpa_updated %>%
+  select(Country, REP_M_AREA, MARINE, NO_TAKE) %>%
+  filter(MARINE == "2" | MARINE == "1") %>%
+  filter(NO_TAKE == "All") %>%
+  group_by(Country)
+
+mpa_area <- aggregate(mpa$REP_M_AREA, by=list(Country=mpa$Country), FUN=sum)
+mpa_area
+
+names(mpa_area) <-c("Country", "Area")
+
+mpa_area_10 <- top_n(mpa_area, 10, Area)
+mpa_area_10
+
+ggplot(mpa_area_10, aes(x = Country, y = Area)) +
+  geom_bar(stat = "identity")
+
+mpa_area_nojurisdiction <-filter(mpa_area, Country != "Areas Beyond National Jurisdiction")
+mpa_area_nojurisdiction_10 <- top_n(mpa_area_nojurisdiction, 10, Area)
+mpa_area_nojurisdiction_10
+
+ggplot(mpa_area_nojurisdiction_10, aes(x = Country, y = Area)) +
+  geom_bar(stat = "identity")
+
+```

### 2018-12-11 draft_figures.Rmd
"kobe" plots 2012 and 2016 total catch 2012 and 2016

@@
 
-Note: Corbett's ITQ data is only until 2012. Chris's upside data is now updated until 2016 with the more recent RAM data that Dan had. I ran all the figure and regressions under two "scenerios":
+Notes:
+- Corbett's ITQ data is only until 2012. Chris's upside data is now updated until 2016 with the more recent RAM data that Dan had. I ran all the figure and regressions under two "scenerios":
 
@@
 extracted information about which fisheries had ITQs in 2012 and applied it to the same fisheries into the future.
-This doesn't take into account other fisheries that   get ITQs in place during that time, or if fisheries stop ITQs
+This doesn't take into account other fisheries implement ITQs past 2012, or if fisheries stop ITQs.
+Only countries with ITQs in 2012 are : Australia, USA, Canda, Japan, Peru, Argentina, South Africa, New Zealand
+
+- for all ITQ related analyzes, limited to fisheries that Corbette had data on.
+I remove the fisheries that have no information on presence or absence of ITQs.
+I am unsure if this is biasing the data; should we assume that the fisheries with no information on ITQs have no ITQs or not?
+This seems like it woud be biased as well.
+    - Corbette's ITQ data includes 375 different fisheries years 1950-2012 for a total of ~15,000 lines of data
 
 "KOBE" plots with ITQs not updated past 2012
+All fisheries 1950-2012 
 ```{r}
@@
 
+f_b_itq$rightsbased[f_b_itq$rightsbased == "0"]<- "No ITQ"
+f_b_itq$rightsbased[f_b_itq$rightsbased == "1"]<- "ITQ"
+
 F_B_graph <- ggplot(data = f_b_itq, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
@@
   geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))
+  geom_vline(aes(xintercept=1))+
+  ggtitle("Fisheries 1950-2012")
 
@@
 
+f_b_itq_updated$rightsbased[f_b_itq_updated$rightsbased == "0"]<- "No ITQ"
+f_b_itq_updated$rightsbased[f_b_itq_updated$rightsbased == "1"]<- "ITQ"
+
 F_B_graph_updated <- ggplot(data = f_b_itq_updated, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
@@
   geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))
+  geom_vline(aes(xintercept=1))+
+  ggtitle("Fisheries 1950-2016")
 
@@
 
-Data until 2012
+###Total Catch ITQ, No ITQ, TURF in 2012
 ```{r}
@@
   select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
+  filter( itq != "NA" & iq != "NA" & ivq != "NA" & turf != "NA") %>%
   mutate(rightsbased = case_when(
@@
 ITQs: 7,420,003
-No ITQ: 142,231
-TURF:1,301,000
+No ITQ: 142,231 (all USA)
+TURF:1,301,000 (all Japan)
+**note: what units is the catch in the upside/rams data?**
 
-Data past 2012
+###Total Catch ITQ, No ITQ, TURF in 2016
 ```{r}
@@
 
-countries_itq_2012 <- f_b_itq_countries %>%
-  select (Country, rightsbased, Year, IdOrig, Catch) %>%
-  filter(Year == "2012")
+countries_itq_2012_2 <- f_b_itq_countries %>%
+  select (Country, rightsbased, Year, IdOrig) %>%
+  filter(Year == "2012")  %>%
+  select(Country, rightsbased, IdOrig)
 
@@
   filter(Year == "2016") %>%
-  select(IdOrig, Country)
+  select(IdOrig, Country, Year, Catch)
 
-itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012, by= c("IdOrig", "Country"), type= "full")
+itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012_2, by= c("IdOrig", "Country"), type= "full")
 
@@
 sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
-#27,830,933
+#26,293,606
 
 sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
-#266,328,075
+#1,154,957
 
 sum(itq_2016_rightsbasedTURF$Catch, na.rm = TRUE)
-#1505000
+#382,370.4
 ```
@@
 ITQs: 27,830,933
-No ITQ: 266,328,075
-TURF:1,505,000
+No ITQ: 266,328,075 (all in the USA)
+TURF:1,505,000 (all in Japan)
+
+**note: This analyze does not include TURF information from DiscoverTurf GP because that data is not fishery specific enough to merge with the upside/Corbette data**
 

### 2018-12-11 lab_notebook.Rmd
"kobe" plots 2012 and 2016 total catch 2012 and 2016

@@
 ```{r}
-species_rightsbased <- read_csv("processed_data/species_rightsbased.csv")
+species_rightsbased <- read_csv("data/species_rightsbased.csv")
+
+ISSCAAP_species <- select(species_rightsbased, SciName, SpeciesCat)
+#write.csv(ISSCAAP_species, file ="ISSCAAP_species.csv")
 ```
@@
 
-species_rightsbased <- read_csv("data/species_rightsbased_binary.csv")
+species_rightsbased_binary <- read_csv("data/species_rightsbased_binary.csv")
 
@@
 
-join_gdp_rightsbased <- join(gdp, species_rightsbased, by = c("Country"), type = "full")
+join_gdp_rightsbased <- join(gdp, species_rightsbased_binary, by = c("Country"), type = "full")
 
@@
 
+###Need to update the ITQ_projection rds file and the ITQ_projection_updated rds file (1st file is without applying ITQ info past 2012 and the second is)
+
+##ADD THIS INTO THE SCRIPT FOR UPDATING UPSIDE DATA
+```{r}
+ISSCAAP_species <- read_csv("data/ISSCAAP_species.csv")
+ITQ_projection <- readRDS("data/ITQ_projection.rds")
+
+ITQ_projection_isscaap_1 <- join(ISSCAAP_species,ITQ_projection, by = c("SciName", "SpeciesCat"), type = "full" )
+
+ITQ_projection_isscaap <- ITQ_projection_isscaap_1 %>%
+  filter(Country != "NA")
+
+```
+
 In the updated ITQ projection data there are lines of data that have 2012 with NA instead of TRUE/FALSE for itq.

### 2018-12-11 scripts/itq_turf_data.R

@@ -86,4 +86,4 @@ true_turf_itq_iscaap[is.na(true_turf_itq_iscaap)] <- "NA"
 
 
 ####FAO website has been down, can't access the species list with FAO numbers associated. did it by hanf for now: read in below csv file for updated with FAO numbers
-species_rightsbased <- read_csv("processed_data/species_rightsbased.csv")
+species_rightsbased <- read_csv("data/species_rightsbased.csv")

### 2018-12-11 scripts/updating_projection.R

@@ -86,6 +86,4 @@ upside_2018_updated <- ITQ_projection %>%
 
 
 
-
-
               

### 2018-12-12 scripts/itq_turf_data.R
commmit 1.5/2

@@ -1,5 +1,8 @@
 ################################################################
 ##Creating dataframe with countries, species, and itq/turf info##
+
+###has all countries that have ever had ITQ and/or TURFs and the ISSCAAP category code associated with the scientific name of the species##
+
 ################################################################
 
 #Load Packages
@@ -19,7 +22,7 @@ suppressPackageStartupMessages({
 
 #load data
 
-ITQ_projection <- readRDS("processed_data/ITQ_projection.rds")
+ITQ_projection <- readRDS("data/ITQ_projection.rds")
 
 # create dataframe with 
 itq <- ITQ_projection %>%
@@ -31,10 +34,7 @@ edf_turf <- read_excel("data/EDF_TURF_data.xlsx")
 #load in DiscoverTURFs data
 d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx")
 
-
 edf_turf_simple <- select(edf_turf, "country", "start_date", "SciName", "turf")
-#create new column that says "turf" and TRUE or FALSE
-
 
 colnames(edf_turf_simple) <- c("Country", "programstart", "SciName", "turf")
 
@@ -44,15 +44,10 @@ edf_projection_1 <- join(edf_turf_simple, itq, by = c("Country", "programstart",
 #combine edf/upside with discover turfs
 all_turf_1 <- join(edf_projection_1, d_turfs, by = c("Country", "SciName", "turf"), type = "full")
 
-#change "blank" NAs to real NAs
-#all_turf_1[is.na(all_turf_1)] <- "NA"
-
 #rearrange columns
 all_turf_itq <- all_turf_1[, c(1,3,2,5,6,7,8,4)]
 
-#turning NAs from no ITQ data to FALSE
-#all_turf_2[all_turf_2 == 0] <- NA
-
+#make all NAs into False with regards to ITQs and TURFs
 all_turf_itq$iq[is.na(all_turf_itq$iq)] <- FALSE
 
 all_turf_itq$itq[is.na(all_turf_itq$itq)] <- FALSE
@@ -61,29 +56,25 @@ all_turf_itq$ivq[is.na(all_turf_itq$ivq)] <- FALSE
 
 all_turf_itq$itq_now[is.na(all_turf_itq$itq_now)] <- 0
 
+
 #filter out all countries that don't have itqs or turfs
-true_turf_itq_1 <- all_turf_itq %>%
[…]

### 2018-12-12 scripts/updating_projection.R

@@ -39,9 +39,8 @@ ram <- timeseries_values_views %>%
 colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
 
 
-
 #Update Projection with RAM
-projection_updated <- join(projection_data, ram, by = c("CommName", "Year"), type = "full")
+projection_updated <- join(ram, projection_data, by = c("CommName", "Year"), type = "full")
 
 #Merge Projection and ITQ
 #seperate out IdOrig column for Projection Data
@@ -69,6 +68,9 @@ ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf
 ITQ_projection_simple <- ITQ_projection %>%
   select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi", "yearitq", "itq_now", "turf", "programstart")
 
+
+#saveRDS(ITQ_projection, "ITQ_projection.rds")
+
 #create RDS from datafram
 #saveRDS(ITQ_projection_simple, "projection_updated.rds")
 
@@ -79,7 +81,7 @@ upside_2018_updated <- ITQ_projection %>%
   select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi")
 
 #create RDS from dataframe
-#saveRDS(upside_2018_updated, "upside_2018_updated")
+saveRDS(upside_2018_updated, "upside_2018_updated.rds")
 #write.csv(upside_2018_updated, file = "upside_2018_updated")
 
 

### 2018-12-18 draft_figures_12.18.18.Rmd
new draft figures doc and fixed most recent year info for each fishery (commit 1/2)

---
title: "draft_figures_12.18.18"
author: "Juliette Verstaen"
date: "12/18/2018"
output: pdf_document
toc: true
toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE }

suppressPackageStartupMessages({
  library(tidyverse)
  library(tidyr)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(readxl)
  library(devtools)
  library(plotly)
  library(base)
  library(rio)
  library(plyr)
})
```

##KOBE Plots with only most recent year of fisheries
###RAM only
No data: ITQ = FALSE

```{r}
fisheries_recent <- read_csv("data/fisheries_recent.csv")

fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
```

```{r}

fisheries_KOBE_ram <- fisheries_recent %>%
  filter(Dbase == "RAM") %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "0"]<- "No ITQ"
fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "1"]<- "ITQ"

 ggplot(data = fisheries_KOBE_ram, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(0, 2.5)+
  xlim(0, 2.5)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  ggtitle("KOBE Plot: RAM only Fisheries")

```

##KOBE Plots with only most recent year of fisheries
###All Data Sources
No data: ITQ = FALSE
```{r}

fisheries_KOBE <- fisheries_recent %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "0"]<- "No ITQ"
fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "1"]<- "ITQ"

ggplot(data = fisheries_KOBE, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(0, 2.5)+
  xlim(0, 2.5)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  ggtitle("KOBE Plot:  All Fisheries")

```

### 2018-12-18 lab_notebook.Rmd
commmit 2/2

@@
   library(plyr)
+  library(data.table)
 })
@@
   filter( itq != "NA", iq != "NA", ivq != "NA")
+
+ISSCAAP Codes and the non-species specific codes
+```{r}
+
+meta_isscaap_codes_1 <- join(isscaap_codes, ISSCAAP_species, by = c("SciName", "SpeciesCat"), type = "full")
+
+meta_isscaap_codes <- unique( meta_isscaap_codes_1[ , 1:2 ] )
+write_csv(meta_isscaap_codes, "meta_isscaap_codes.csv")
+```
+
+12/18/2018
+Using the newly updated upside/ITQ and filtering out only the most recent date for each fishery
+- make a df of these that have ITQs and those that don't -> apply to OG upside/ITQ data so that more recent years can have ITQ data
+- take this new df and filter out the most recent years with ITQs and KOBE plot. also do catches
+
+```{r}
+
+ITQ_projection <- readRDS("data/ITQ_projection.rds")
+
+upside_2016 <- ITQ_projection %>%
+  filter(Year <= "2016") %>%
+  unite(id_country, IdOrig, Country, sep = "-")
+
+upside_recent <- setDT(upside_2016)[,.SD[which.max(Year)],keyby=id_country]
+
+upside_allfisheriesITQ <- upside_recent %>%
+  select (id_country, itq, iq, ivq, Year, turf) %>%
+  filter(itq != "NA" & iq != "NA" & ivq != "NA" )
+
+```
+
+#closer look at corbett's data
+```{r}
+Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
+
+corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
+
+corbette_fisheries <- corbette_recent %>%
+  select(assess_id_short, year, speciescat, iq, itq, ivq, coop, turf)%>%
+  filter(itq != "NA" & iq != "NA" & ivq != "NA" )
+
+fisheries_with_turfs <- corbette_fisheries %>%
+  filter(turf != "FALSE")
+
+fisheries_with_itq <- corbette_fisheries %>%
+   filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" )
+
+```
+
+reupdating upside data with new ITQ list
+```{r}
+#Load Data
+#Upside data
+projection_data <- readRDS("data/projection_data.rds")
+
+#RAMS
+load("data/DBdata-model_fits_included.RData")
+
+#RAM Data Tiddying
+ram <- timeseries_values_views %>%
+  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
+  add_column("RAM")
+
+colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
+
+#Update Projection with RAM
+projection_updated <- join(ram, projection_data, by = c("CommName", "Year"), type = "full")
+
+separate_projection <- projection_updated%>% 
+  separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
+
+unite_projection <- separate_projection %>% 
+  unite(assess_id_short, agency, stock, sep = "-")
+
+colnames(fisheries_with_itq) <- c("assess_id_short", "Year","SpeciesCat" , "iq", "itq", "ivq", "coop", "turf")
+
+fishery_itq_simple <- fisheries_with_itq %>%
+  select(assess_id_short,"iq", "itq", "ivq", "turf" )
+
+ITQ_projection_merge <- merge(unite_projection, fisheries_with_itq, by = c("assess_id_short"), all = TRUE)
+
+recent_pre2016 <- ITQ_projection_merge %>%
+  filter(Year.x <= "2016")
+
+fisheries_recent_1 <- setDT(recent_pre2016)[,.SD[which.max(Year.x)],keyby=assess_id_short]
+
+fisheries_recent <- fisheries_recent_1 %>%
+  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq, turf)
+
+#fisheries_recent <- write.csv(fisheries_recent, file = "fisheries_recent.csv")
+
+```
+
+##KOBE Plots with only most recent year of fisheries
+RAM only
+No data: ITQ = FALSE
+
+```{r}
+
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
+fisheries_KOBE_ram <- fisheries_recent %>%
+  filter(Dbase == "RAM") %>%
+  mutate(rightsbased = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
+
+fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "0"]<- "No ITQ"
+fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "1"]<- "ITQ"
+
+F_B_graph_RAM <- ggplot(data = fisheries_KOBE_ram, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
+  geom_point()+
+  labs(x = "B/Bmsy", y= "F/Fsmy") +
+  theme_minimal()+
+  theme(legend.title=element_blank())+
+  ylim(0, 2.5)+
+  xlim(0, 2.5)+
+  geom_hline(aes(yintercept=1))+
+  geom_vline(aes(xintercept=1))+
+  ggtitle("KOBE Plot: RAM only Fisheries")
+
+#F_B_graph
+ggplotly(F_B_graph)
+
+```
+
+##KOBE Plots with only most recent year of fisheries
+RAM only
+No data: ITQ = FALSE
+```{r}
+
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
+fisheries_KOBE <- fisheries_recent %>%
+  mutate(rightsbased = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
+
+fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "0"]<- "No ITQ"
+fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "1"]<- "ITQ"
+
+F_B_graph <- ggplot(data = fisheries_KOBE, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
+  geom_point()+
+  labs(x = "B/Bmsy", y= "F/Fsmy") +
+  theme_minimal()+
+  theme(legend.title=element_blank())+
+  ylim(0, 2.5)+
+  xlim(0, 2.5)+
+  geom_hline(aes(yintercept=1))+
+  geom_vline(aes(xintercept=1))+
+  ggtitle("KOBE Plot:  All Fisheries")
+
+#F_B_graph
+ggplotly(F_B_graph)
+
+```

### 2018-12-18 draft_figures_12.18.18.Rmd
estimates of total catch for turf, itq, no itq

@@
 ```
+
+##Total Catches in most recent year of ITQ, no ITQ, and Turfs
+```{r}
+
+fisheries_rightsbased <- fisheries_recent %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0", 
+    ))
+
+turfs <- filter(fisheries_rightsbased, rightsbased == "2")
+itq <- filter(fisheries_rightsbased, rightsbased == "1")
+no_itq <- filter(fisheries_rightsbased, rightsbased == "0")
+
+sum(turfs$Catch, na.rm = TRUE)
+#20,217,168
+
+sum(itq$Catch, na.rm = TRUE)
+#1,154,957
+
+sum(no_itq$Catch, na.rm = TRUE)
+#382,370.4
+```
+turf = 0
+itq = 4,056,613
+no itq = 66,156,579
+
+## adding turf information to upside projection
+```{r}
+
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf)
+
+fisheries_recent_generousturf_1 <- select(fisheries_recent, Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
+
+fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
+
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    ))
+
+turfs <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
+itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "1")
+no_itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "0")
+
+sum(turfs$Catch, na.rm = TRUE)
+
+sum(itq$Catch, na.rm = TRUE)
+
+sum(no_itq$Catch, na.rm = TRUE)
+
+69025951/78938573
+
+```
+
+Generous Turf Catch Estimates:
+
+turf = 1,357,098 -> 1.72% global catch
+itq= 8,555,524 -> 10.8% global catch
+no itq =  69,025,951 -> 87.44% global catch
+
+Total: 78,938,573

### 2018-12-20 lab_notebook.Rmd
new script with updated projection data and updated ITQ/Turf implementation in most recent year 2016

@@
 reupdating upside data with new ITQ list
+
+###JULIETTE: check why the fisheries recent only has FALSE for turfs and no TRUEs
+
 ```{r}
@@
 fishery_itq_simple <- fisheries_with_itq %>%
-  select(assess_id_short,"iq", "itq", "ivq", "turf" )
+  select(assess_id_short,iq, itq, ivq, turf )
 
@@
 ```
+
+## adding turf information to upside projection (use fisheries recent?)
+```{r}
+
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf)
+
+fisheries_recent_generousturf_1 <- select(fisheries_recent, Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
+
+fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
+
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    ))
+
+turfs <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
+itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "1")
+no_itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "0")
+
+sum(turfs$Catch, na.rm = TRUE)
+
+sum(itq$Catch, na.rm = TRUE)
+
+sum(no_itq$Catch, na.rm = TRUE)
+
+```
+
+turf only = 413 rows
+fisheries recent = 5294
+
+5643 actual rows
+5707 when manually added added
+- this means 64 species were matched with existing species in database
+- when separated out all by species it was worse
+
+- separate remaining by genus?
+
+12/20/2018
+new UN GDP data, 2016 only
+Scaled GDPs
+Rerun Regressions
+###itq or turf: probablity of itq = f(ISSCAPP and GDP)
+*regression converges*
+```{r}
+
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf, SpeciesCat) %>%
+  filter(SpeciesCat != 91) %>%
+  filter(SpeciesCat != 92)
+
+fisheries_recent_generousturf_1 <- fisheries_recent %>%
+  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)%>%
+  filter(SpeciesCat.x != 91) %>%
+  filter(SpeciesCat.x != 92)
+
+fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
+
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE | iq == FALSE | ivq == FALSE ~ "0"
+    ))
+
+gdp_all <- read_excel("data/un_gdp_2016.xls")
+
+gdp <- gdp_all %>%
+  select(Country, gdp_center) %>%
+  filter( gdp_center != "NA")
+
+join_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))
+
+gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )
+
+gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
+gdp_rightsbased$rightsbased <- as.numeric(gdp_rightsbased$rightsbased)
+
+itq_glm <- glm(formula = rightsbased ~ gdp_center + SpeciesCat, family = "binomial", data = gdp_rightsbased)
+itq_glm
+
+summary(itq_glm)
+
+```
+
+Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
+
+```{r}
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf, SpeciesCat) %>%
+  filter(SpeciesCat != 91) %>%
+  filter(SpeciesCat != 92)
+
+fisheries_recent_generousturf_1 <- fisheries_recent %>%
+  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)%>%
+  filter(SpeciesCat.x != 91) %>%
+  filter(SpeciesCat.x != 92)
+
+fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
+
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "1",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "0"
+    ))
+
+gdp_all <- read_excel("data/un_gdp_2016.xls")
+
+gdp <- gdp_all %>%
+  select(Country, gdp_center) %>%
+  filter( gdp_center != "NA")
+
+join_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))
+
+gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )
+
+gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
+gdp_rightsbased$rightsbased <- as.numeric(gdp_rightsbased$rightsbased)
+
+itq_turf_glm <- glm(formula = rightsbased ~ gdp_center + SpeciesCat, family = "binomial", data = gdp_rightsbased)
+itq_glm
+
+summary(itq_turf_glm)
+
+```

### 2018-12-20 2016_projection_updated.R

@@ -1,0 +1,81 @@
+
+#Loading packages
+
+suppressPackageStartupMessages({
+  library(tidyverse)
+  library(tidyr)
+  library(here)
+  library(ggplot2)
+  library(dplyr)
+  library(readxl)
+  library(devtools)
+  library(plotly)
+  library(base)
+  library(rio)
+  library(plyr)
+  library(data.table)
+})
+
+Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
+
+#new dataframw with just most recent year of data for each fishery
+corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
+
+#filter out the fisheries with no data on itqs or turfs
+corbette_fisheries <- corbette_recent %>%
+  select(assess_id_short, year, speciescat, iq, itq, ivq, coop, turf)%>%
+  filter(itq != "NA" & iq != "NA" & ivq != "NA")%>%
+  filter(turf != "NA" ) 
+
+
+#new data frame with just data on fisheries with itqs
+fisheries_with_itq <- corbette_fisheries %>%
+  filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" | turf == "TRUE" )
+#Load Data
+#Upside data
+projection_data <- readRDS("data/projection_data.rds")
+
+#RAMS
+load("data/DBdata-model_fits_included.RData")
+
+
+#RAM Data Tiddying
+ram <- timeseries_values_views %>%
+  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
+  add_column("RAM")
+
+colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
+
+#Update Projection with RAM
+projection_updated <- join(ram, projection_data, by = c("CommName", "Year"), type = "full")
+##note: RAM data has some fisheries not in the projection data, thus adding new fisheries to the upside projection data
+
+#separate and unit functions to create a shorter version of the stock assessment ID to merge with corbette ITQ/TURF data later
+separate_projection <- projection_updated%>% 
+  separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
+
+unite_projection <- separate_projection %>% 
+  unite(assess_id_short, agency, stock, sep = "-")
+
[…]

### 2018-12-21 draft_figures_12.18.18.Rmd
working on regressions

--- 2018-12-18 draft_figures_12.18.18.Rmd
@@
 ```{r}
+
+#read in data: this is updated projection data (updated using RAMs) and Corbett's ITQ/Turf data applied to each fishery. only data for most recent year for each fishery is represented.
+
 fisheries_recent <- read_csv("data/fisheries_recent.csv")
 
+#assuming that when no data is avaliable on the fishery inregardes to ITQ or Turfs that means there are none
 fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
@@
 fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
 ```
@@
 
+#only looking at fisheries data that come from RAMS database
+# creating new column called "rightsbased" where 1 = ITQ and 0 = No ITQ
 fisheries_KOBE_ram <- fisheries_recent %>%
@@
 
+#graphing 
 fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "0"]<- "No ITQ"
@@
 
-ggplot(data = fisheries_KOBE, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
+#graphing 
+F_B_graph <- ggplot(data = fisheries_KOBE, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
   geom_point()+
@@
 ```
+
+LOOK AT THIS TOMORROW. ITQ AND NO ITQ CATCH PROJECTIONS SHOULD BE THE SAME, USING SAME DATA, BUT THEY ARE NOT. WTF?
+
+##Total Catches in most recent year of ITQ, no ITQ, and Turfs
+```{r}
+
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+#assuming that when no data is present for itqs/turf that means there are none
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+
+fisheries_rightsbased <- fisheries_recent %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1"
+    ))
+
+turfs <- filter(fisheries_rightsbased, rightsbased == "2")
+itq <- filter(fisheries_rightsbased, rightsbased == "1")
+no_itq <- filter(fisheries_rightsbased, rightsbased == "0")
+
+sum(turfs$Catch, na.rm = TRUE)
+#174065.5
+
+sum(itq$Catch, na.rm = TRUE)
+#3874741
+
+sum(no_itq$Catch, na.rm = TRUE)
+#66155763
+
+```
+
+turf = 174,065.5 = 0.248% of total catch
+itq = 3,874,741 = 5.5% of total catch
+no itq = 66,155,763 = 94.23% of total catch
+Total = 70,204,569.5
+
+## Total Catch: A more generous estimation of Turf catch
+```{r}
+
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+#load in data for turf/itq only projection
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf)
+
+fisheries_recent_generousturf_1 <- select(fisheries_recent, Country, assess_id_short, Year.x,SciName, Catch, itq, ivq, iq)
+
+#merge the most recent data on each fishery with turf data
+fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1,turf_only, by = c("Country", "SciName") , all.x = "TRUE")
+
+#assuming that when no data is present for itqs/turf that means there are none
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1"
+    ))
+
+#create dfs for turf, itq, and no itq fisheries to calculate the sum of each
+#NOTE to rememeber: the data from these fisheries are the most recent numbers we have. they are not all in the same year 
+turfs_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
+itq_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "1")
+no_itq_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "0")
+
+sum(turfs_generous$Catch, na.rm = TRUE)
+#1530353
+
+sum(itq_generous$Catch, na.rm = TRUE)
+#8374634
+
+sum(no_itq_generous$Catch, na.rm = TRUE)
+#69025946
+
+```
+
+Generous Turf Catch Estimates:
+
+turf = 1,530,353 -> 1.93% global catch
+itq= 8,374,634 -> 10.6% global catch
+no itq =  69,025,946 -> 87.46% global catch
+
+Total: 78,930,933
+
+*note: 5643 actual rows
+5707 when manually added added
+- this means 64 species were matched with existing species in database
+- when separated out all by species it was worse
+- separate remaining by genus?
+
+##Logit regressions
+
+new UN GDP data, 2016 only
+Scaled GDPs
+Rerun Regressions
+###itq or turf: probablity of itq = f(ISSCAPP and GDP)
+
+```{r}
+
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf, SpeciesCat)
+
+fisheries_recent_generousturf_1 <- fisheries_recent %>%
+  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
+
+fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
+
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE | iq == FALSE | ivq == FALSE ~ "0"
+    ))
+
+gdp_all <- read_excel("data/un_gdp_2016.xls")
+
+gdp <- gdp_all %>%
+  select(Country, gdp_center) %>%
+  filter( gdp_center != "NA")
+
+merge_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))
+
+gdp_rightsbased <- filter(merge_gdp_rightsbased, SpeciesCat != "NA" )
+
+gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
+gdp_rightsbased$rightsbased <- as.numeric(gdp_rightsbased$rightsbased)
+
+itq_glm <- glm(formula = rightsbased ~ gdp_center + SpeciesCat, family = "binomial", data = gdp_rightsbased)
+itq_glm
+
+summary(itq_glm)
+```
+
+Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
+```{r}
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf, SpeciesCat)
+
+fisheries_recent_generousturf_1 <- fisheries_recent %>%
+  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
+
+fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
+
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "1",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "0"
+    ))
+
+gdp_all <- read_excel("data/un_gdp_2016.xls")
+
+gdp <- gdp_all %>%
+  select(Country, gdp_center) %>%
+  filter( gdp_center != "NA")
+
+join_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))
+
+gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )
+
+gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
+gdp_rightsbased$rightsbased <- as.numeric(gdp_rightsbased$rightsbased)
+
+itq_turf_glm <- glm(formula = rightsbased ~ gdp_center + SpeciesCat, family = "binomial", data = gdp_rightsbased)
+itq_glm
+
+summary(itq_turf_glm)
+
+```
+
+####Bar Chart: Coefficient Species Category

### 2018-12-21 2016_projection_updated.R

@@ -1,81 +1,0 @@
-
-#Loading packages
-
-suppressPackageStartupMessages({
-  library(tidyverse)
-  library(tidyr)
-  library(here)
-  library(ggplot2)
-  library(dplyr)
-  library(readxl)
-  library(devtools)
-  library(plotly)
-  library(base)
-  library(rio)
-  library(plyr)
-  library(data.table)
-})
-
-Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
-
-#new dataframw with just most recent year of data for each fishery
-corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
-
-#filter out the fisheries with no data on itqs or turfs
-corbette_fisheries <- corbette_recent %>%
-  select(assess_id_short, year, speciescat, iq, itq, ivq, coop, turf)%>%
-  filter(itq != "NA" & iq != "NA" & ivq != "NA")%>%
-  filter(turf != "NA" ) 
-
-
-#new data frame with just data on fisheries with itqs
-fisheries_with_itq <- corbette_fisheries %>%
-  filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" | turf == "TRUE" )
-#Load Data
-#Upside data
-projection_data <- readRDS("data/projection_data.rds")
-
-#RAMS
-load("data/DBdata-model_fits_included.RData")
-
-
-#RAM Data Tiddying
-ram <- timeseries_values_views %>%
-  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
-  add_column("RAM")
-
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
-
-#Update Projection with RAM
-projection_updated <- join(ram, projection_data, by = c("CommName", "Year"), type = "full")
-##note: RAM data has some fisheries not in the projection data, thus adding new fisheries to the upside projection data
-
-#separate and unit functions to create a shorter version of the stock assessment ID to merge with corbette ITQ/TURF data later
-separate_projection <- projection_updated%>% 
-  separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
-
-unite_projection <- separate_projection %>% 
-  unite(assess_id_short, agency, stock, sep = "-")
-
[…]

### 2018-12-21 draft_figures_12.18.18.Rmd
diagnostics

@@
 
+## run diagnostics
+
+##Diagnostics
+
+```{r}
+
+##run above chunk to get gdp_rightsbased df not the old csv file that is now archived in data folder
+
+diagnostics <- gdp_rightsbased %>%
+  mutate(management = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    turf == TRUE ~ "2",
+    itq == FALSE | iq == FALSE | ivq == FALSE | turf == FALSE ~ "0"
+    )) %>%
+  select(Country, gdp_center, SpeciesCat, management)
+
+#diagnostics wont run with non-numeric?
+diagnostics$SpeciesCat <- as.numeric(diagnostics$SpeciesCat)
+diagnostics$management <- as.numeric(diagnostics$management)
+
+#2= gdp; 4= turf; 5 = SpeciesCat; 23 = itq; 24= ivq; 25 = iq; 26= binary rights based
+pairs(diagnostics[2:4])
+
+#pearson's r correlations
+cor(diagnostics[2:4])
+
+#run chi square?
+
+```
+
 ####Bar Chart: Coefficient Species Category

### 2018-12-21 lab_notebook.Rmd
diagnostics

@@
 
-#closer look at corbett's data
-```{r}
+#Pulling out information about ITQs/TURFs in Corbette Data to apply to upside data
+```{r}
+
 Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
 
+#new dataframw with just most recent year of data for each fishery
 corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
 
+#filter out the fisheries with no data on itqs or turfs
 corbette_fisheries <- corbette_recent %>%
   select(assess_id_short, year, speciescat, iq, itq, ivq, coop, turf)%>%
-  filter(itq != "NA" & iq != "NA" & ivq != "NA" )
-
-fisheries_with_turfs <- corbette_fisheries %>%
-  filter(turf != "FALSE")
-
+  filter(itq != "NA" & iq != "NA" & ivq != "NA")%>%
+  filter(turf != "NA" )
+
+#new data frame with just data on fisheries with itqs
 fisheries_with_itq <- corbette_fisheries %>%
-   filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" )
+   filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" | turf == "TRUE" )
 
@@
 reupdating upside data with new ITQ list
-
-###JULIETTE: check why the fisheries recent only has FALSE for turfs and no TRUEs
 
@@
 projection_updated <- join(ram, projection_data, by = c("CommName", "Year"), type = "full")
-
+##note: RAM data has some fisheries not in the projection data, thus adding new fisheries to the upside projection data
+
+#separate and unit functions to create a shorter version of the stock assessment ID to merge with corbette ITQ/TURF data later
 separate_projection <- projection_updated%>% 
@@
 
+#merge corbette's data on ITQ/Turf implemented or not for each fishery
 fishery_itq_simple <- fisheries_with_itq %>%
@@
 
+#filter out data post 2016 because we know that those are projected/modeled data not recorded
 recent_pre2016 <- ITQ_projection_merge %>%
@@
 
+#keep only info on most recent year for each fishery  
 fisheries_recent_1 <- setDT(recent_pre2016)[,.SD[which.max(Year.x)],keyby=assess_id_short]
 
+#select the columns we are interested in
 fisheries_recent <- fisheries_recent_1 %>%
@@
 
+#write dataframe to csv file
 #fisheries_recent <- write.csv(fisheries_recent, file = "fisheries_recent.csv")
@@
 
+#read in data: this is updated projection data (updated using RAMs) and Corbett's ITQ/Turf data applied to each fishery. only data for most recent year for each fishery is represented.
+
 fisheries_recent <- read_csv("data/fisheries_recent.csv")
 
+#assuming that when no data is avaliable on the fishery inregardes to ITQ or Turfs that means there are none
 fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
@@
 
+#graphing logistics
 fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "0"]<- "No ITQ"
@@
 #F_B_graph
-ggplotly(F_B_graph)
+ggplotly(F_B_graph_RAM)
 
@@
 
+#read in data: this is updated projection data (updated using RAMs) and Corbett's ITQ/Turf data applied to each fishery. only data for most recent year for each fishery is represented.
 fisheries_recent <- read_csv("data/fisheries_recent.csv")
 
+#assuming that when no data is avaliable on the fishery inregardes to ITQ or Turfs that means there are none
 fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
@@
 
+#graphing logistics
 F_B_graph <- ggplot(data = fisheries_KOBE, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
@@
 
-## adding turf information to upside projection (use fisheries recent?)
-```{r}
-
+## adding turf information to upside projection(ie: fisheries_recent)
+```{r}
+
+#load in data for turf/itq only projection
 turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
@@
 
-fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
-
+#merge the most recent data on each fishery with turf data
+fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turf_only, by = c("Country", "SciName")) #, all = "TRUE")
+
+#assuming that when no data is present for itqs/turf that means there are none
 fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
@@
     itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1"
     ))
 
+#create dfs for turf, itq, and no itq fisheries to calculate the sum of each
+#NOTE to rememeber: the data from these fisheries are the most recent numbers we have. they are not all in the same year 
 turfs <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
@@
 turf_only <- turf_itq_isscaap %>%
-  select(SciName, Country, turf, SpeciesCat) %>%
-  filter(SpeciesCat != 91) %>%
-  filter(SpeciesCat != 92)
+  select(SciName, Country, turf, SpeciesCat)
 
 fisheries_recent_generousturf_1 <- fisheries_recent %>%
-  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)%>%
-  filter(SpeciesCat.x != 91) %>%
-  filter(SpeciesCat.x != 92)
+  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
 
@@
 ```
+
+##Diagnostics
+
+```{r}
+
+##run above chunk to get gdp_rightsbased df not the old csv file that is now archived in data folder
+
+diagnostics <- gdp_rightsbased %>%
+  mutate(management = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    turf == TRUE ~ "2",
+    itq == FALSE | iq == FALSE | ivq == FALSE | turf == FALSE ~ "0"
+    )) %>%
+  select(Country, gdp_center, SpeciesCat, management)
+
+#diagnostics wont run with non-numeric?
+diagnostics$SpeciesCat <- as.numeric(diagnostics$SpeciesCat)
+diagnostics$management <- as.numeric(diagnostics$management)
+
+#2= gdp; 4= turf; 5 = SpeciesCat; 23 = itq; 24= ivq; 25 = iq; 26= binary rights based
+pairs(diagnostics[2:4])
+
+#pearson's r correlations
+cor(diagnostics[2:4])
+
+#run chi square?
+
+```
+## MPA stuff

### 2018-12-23 draft_figures_12.18.18.Rmd
regressions with larger categories and new MPA bar graphs with different data

--- 2018-12-21 draft_figures_12.18.18.Rmd
@@
 
+##Larger Categories for ISSCAAP Codes
+11,13 = freshwater fish = 1
+22-24 = diadromous fishes = 2
+31-35, 37 = marine fishes = 3
+42-45,47 = crustaceans = 4
+52-58 = molluscs = 5
+74,76,77 = miscellaneous aquatic animals = 7
+
+```{r}
+
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf, SpeciesCat)
+
+fisheries_recent_generousturf_1 <- fisheries_recent %>%
+  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
+
+colnames(fisheries_recent_generousturf_1) <- c("Country", "assess_id_short", "Year", "CommName", "Biomass", "Catch", "BvBmsy", "FvFmsy", "Dbase", "SciName", "IdLevel", "SpeciesCat", "Profits", "MSY", "Price", "g", "k", "c", "phi", "itq", "ivq", "iq")
+
+fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName", "SpeciesCat"), all = "TRUE")
+
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_regression_1 <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE | iq == FALSE | ivq == FALSE ~ "0"
+    )) %>%
+  mutate(MainCat = case_when(
+    SpeciesCat == 11 | SpeciesCat == 13 ~ "1",
+    SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",
+    SpeciesCat == 31 | SpeciesCat == 32 | SpeciesCat == 33 | SpeciesCat == 34 | SpeciesCat     == 35 | SpeciesCat == 37 ~ "3",
+    SpeciesCat == 42 | SpeciesCat == 43 | SpeciesCat == 44 | SpeciesCat == 45 | SpeciesCat      == 47 ~ "4",
+    SpeciesCat == 52 | SpeciesCat == 53 | SpeciesCat ==54 |  SpeciesCat == 55 | SpeciesCat     == 56 | SpeciesCat == 57 | SpeciesCat == 58 ~ "5",
+    SpeciesCat == 74 | SpeciesCat == 76 | SpeciesCat == 77 ~ "7"
+  )) %>%
+  select(Country, SciName, MainCat, rightsbased) %>%
+  filter(MainCat != "NA")
+
+gdp_all <- read_excel("data/un_gdp_2016.xls")
+
+gdp <- gdp_all %>%
+  select(Country, gdp_center) %>%
+  filter( gdp_center != "NA")
+
+merge_gdp_mc_rb <- merge(gdp, fisheries_recent_regression_1, by = c("Country"))
+
+gdp_mc_rb <- filter(merge_gdp_mc_rb, MainCat != "NA" )
+
+gdp_mc_rb$MainCat <- factor(gdp_mc_rb$MainCat)
+gdp_mc_rb$rightsbased <- as.numeric(gdp_mc_rb$rightsbased)
+
+itq_glm_mc <- glm(formula = rightsbased ~ gdp_center + MainCat, family = "binomial", data = gdp_mc_rb)
+
+itq_glm_mc
+
+summary(itq_glm_mc)
+
+```
+
 Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
@@
 
-####Bar Chart: Coefficient Species Category
+##Larger Categories for ISSCAAP Codes
+11,13 = freshwater fish = 1
+22-24 = diadromous fishes = 2
+31-35, 37 = marine fishes = 3
+42-45,47 = crustaceans = 4
+52-58 = molluscs = 5
+74,76,77 = miscellaneous aquatic animals = 7
+
+```{r}
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf, SpeciesCat)
+
+fisheries_recent_generousturf_1 <- fisheries_recent %>%
+  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
+
+fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
+
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_turf_i_mc <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "1",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "0"
+    ))%>%
+  mutate(MainCat = case_when(
+    SpeciesCat == 11 | SpeciesCat == 13 ~ "1",
+    SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",
+    SpeciesCat == 31 | SpeciesCat == 32 | SpeciesCat == 33 | SpeciesCat == 34 | SpeciesCat     == 35 | SpeciesCat == 37 ~ "3",
+    SpeciesCat == 42 | SpeciesCat == 43 | SpeciesCat == 44 | SpeciesCat == 45 | SpeciesCat      == 47 ~ "4",
+    SpeciesCat == 52 | SpeciesCat == 53 | SpeciesCat ==54 |  SpeciesCat == 55 | SpeciesCat     == 56 | SpeciesCat == 57 | SpeciesCat == 58 ~ "5",
+    SpeciesCat == 74 | SpeciesCat == 76 | SpeciesCat == 77 ~ "7"
+  )) %>%
+  select(Country, SciName, MainCat, rightsbased) %>%
+  filter(MainCat != "NA")
+
+gdp_all <- read_excel("data/un_gdp_2016.xls")
+
+gdp <- gdp_all %>%
+  select(Country, gdp_center) %>%
+  filter( gdp_center != "NA")
+
+join_gdp_turf_i_mc <- merge(gdp, fisheries_recent_turf_i_mc, by = c("Country"))
+
+gdp_turf_i_mc <- filter(join_gdp_turf_i_mc, MainCat != "NA" )
+
+gdp_turf_i_mc$MainCat <- factor(gdp_turf_i_mc$MainCat)
+gdp_turf_i_mc$rightsbased <- as.numeric(gdp_turf_i_mc$rightsbased)
+
+turf_itq_mc_glm <- glm(formula = rightsbased ~ gdp_center + MainCat, family = "binomial", data = gdp_turf_i_mc)
+turf_itq_mc_glm
+
+summary(turf_itq_mc_glm)
+```
+
+###MPA New Costello Data
+These MPAs are at least partitally no-take but some of the percentages are very low
+
+```{r}
+
+mpa_costello_data <- read_excel("data/mpa_costello_data.xlsx")
+
+##Choose only MPAs that have some no take
+mpa_no_take <- mpa_costello_data %>%
+  filter(no_take == "1")
+
+mpa_no_take_10 <- top_n(mpa_no_take, 10, mpa_area)
+mpa_no_take_10
+
+##all countries
+mpa_no_take_10$Country <- factor(mpa_no_take_10$Country, levels = mpa_no_take_10$Country[order(mpa_no_take_10$mpa_area)])
+
+ggplot(mpa_no_take_10, aes(x = Country, y = mpa_area)) +
+  geom_bar(stat = "identity")+
+  ggtitle("Top 10 Countries with No Take MPAs")+
+  coord_flip()+
+  theme_bw()+
+  ylab("Area km2")
+
+```
+
+These are the countries with the highest area of no-take
+```{r}
+mpa_costello_data <- read_excel("data/mpa_costello_data.xlsx")
+
+##Choose only MPAs that have some no take
+mpa_no_take <- mpa_costello_data %>%
+  filter(no_take == "1")
+
+mpa_no_take_area_10 <- top_n(mpa_no_take, 10, no_take_area)
+mpa_no_take_area_10
+
+##all countries
+mpa_no_take_area_10$Country <- factor(mpa_no_take_area_10$Country, levels = mpa_no_take_area_10$Country[order(mpa_no_take_area_10$no_take_area)])
+
+ggplot(mpa_no_take_area_10, aes(x = Country, y = no_take_area)) +
+  geom_bar(stat = "identity")+
+  ggtitle("Top 10 Countries with Largest No Take Areas")+
+  coord_flip()+
+  theme_bw()+
+  ylab("Area km2")
+
+```

### 2018-12-23 draft_figures_12.23.18.Rmd
catch calcuations fixed, and new mpa graphs

--- 2018-12-23 draft_figures_12.18.18.Rmd
@@
 ---
-title: "draft_figures_12.18.18"
+title: "Draft Figures: 12.23.18"
 author: "Juliette Verstaen"
@@
   library(plyr)
+  library(knitr)
 })
@@
 
-```{r}
+```{r message=FALSE}
 
@@
 
-LOOK AT THIS TOMORROW. ITQ AND NO ITQ CATCH PROJECTIONS SHOULD BE THE SAME, USING SAME DATA, BUT THEY ARE NOT. WTF?
-
-##Total Catches in most recent year of ITQ, no ITQ, and Turfs
+##Total Catch: Most recent year for each fishery 
 ```{r}
@@
 
-fisheries_rightsbased <- fisheries_recent %>%
+fisheries_turf_itqs <- fisheries_recent %>%
   mutate(rightsbased = case_when(
     turf == TRUE ~ "2",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1"
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"
     ))
 
-turfs <- filter(fisheries_rightsbased, rightsbased == "2")
-itq <- filter(fisheries_rightsbased, rightsbased == "1")
-no_itq <- filter(fisheries_rightsbased, rightsbased == "0")
+turfs_catch <- filter(fisheries_turf_itqs, rightsbased == "2")
+itq_catch <- filter(fisheries_turf_itqs, rightsbased == "1")
+no_itq_catch <- filter(fisheries_turf_itqs, rightsbased == "0")
 
-sum(turfs$Catch, na.rm = TRUE)
-#174065.5
+sum(turfs_catch$Catch, na.rm = TRUE)
 
-sum(itq$Catch, na.rm = TRUE)
-#3874741
+sum(itq_catch$Catch, na.rm = TRUE)
 
-sum(no_itq$Catch, na.rm = TRUE)
-#66155763
+sum(no_itq_catch$Catch, na.rm = TRUE)
 
@@
 ## Total Catch: A more generous estimation of Turf catch
-```{r}
 
+```{r message =FALSE}
+
+#load data with info only on most recent year for each fishery (includes upside, updated with RAMs, corbette itq/turf data)
 fisheries_recent <- read_csv("data/fisheries_recent.csv")
 
-#load in data for turf/itq only projection
-turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+#turf data from edf and discover turfs
+turfs_edf_dt <- read_csv("data/turfs_edf_dt.csv")
+```
 
-turf_only <- turf_itq_isscaap %>%
-  select(SciName, Country, turf)
+```{r}
 
@@
 #merge the most recent data on each fishery with turf data
-fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1,turf_only, by = c("Country", "SciName") , all.x = "TRUE")
+fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turfs_edf_dt, by = c("Country", "SciName") , all.x = "TRUE")
 
@@
 #NOTE to rememeber: the data from these fisheries are the most recent numbers we have. they are not all in the same year
+
 turfs_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
@@
 sum(turfs_generous$Catch, na.rm = TRUE)
-#1530353
 
 sum(itq_generous$Catch, na.rm = TRUE)
-#8374634
 
 sum(no_itq_generous$Catch, na.rm = TRUE)
-#69025946
 
@@
 
-turf = 1,530,353 -> 1.93% global catch
-itq= 8,374,634 -> 10.6% global catch
-no itq =  69,025,946 -> 87.46% global catch
+turf = 1,643,571 -> 2.3% global catch
+itq= 3,874,741 -> 5.5% global catch
+no itq =  64,815,841 -> 92.1% global catch
 
-Total: 78,930,933
-
-*note: 5643 actual rows
-5707 when manually added added
-- this means 64 species were matched with existing species in database
-- when separated out all by species it was worse
-- separate remaining by genus?
+Total: 70,334,153
 
@@
 
-new UN GDP data, 2016 only
-Scaled GDPs
-Rerun Regressions
-###itq or turf: probablity of itq = f(ISSCAPP and GDP)
+- new UN GDP data, 2016 only
+- Scaled GDPs
+
+###Probablity of itq = f(ISSCAPP and GDP)
 
 ```{r}
-
-fisheries_recent <- read_csv("data/fisheries_recent.csv")
 
@@
 
-turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
-
-turf_only <- turf_itq_isscaap %>%
-  select(SciName, Country, turf, SpeciesCat)
-
 fisheries_recent_generousturf_1 <- fisheries_recent %>%
@@
 
-fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
+colnames(fisheries_recent_generousturf_1) <- c("Country", "assess_id_short", "Year", "CommName", "Biomass", "Catch", "BvBmsy", "FvFmsy", "Dbase", "SciName", "IdLevel", "SpeciesCat", "Profits", "MSY", "Price", "g", "k", "c", "phi", "itq", "ivq", "iq")
+fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turfs_edf_dt, by = c("Country", "SciName") , all.x = "TRUE")
 
@@
 
-##Larger Categories for ISSCAAP Codes
+**The intercepts for the species categories are not coming up as significant at all. Recategorized fish according to the next level up for the ISSCAAP codes. Reclassifications are below: **
+
+Larger Categories for ISSCAAP Codes
 11,13 = freshwater fish = 1
@@
 
+###Rerun Logits with higher up species categories
 ```{r}
@@
 
-turf_only <- turf_itq_isscaap %>%
-  select(SciName, Country, turf, SpeciesCat)
-
 fisheries_recent_generousturf_1 <- fisheries_recent %>%
@@
 
-fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName", "SpeciesCat"), all = "TRUE")
+fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turfs_edf_dt, by = c("Country", "SciName") , all.x = "TRUE")
 
@@
 ```
+Larger categories do not seem to make a difference
 
-Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
+###Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
 ```{r}
+
 fisheries_recent <- read_csv("data/fisheries_recent.csv")
@@
 
-fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
+colnames(fisheries_recent_generousturf_1) <- c("Country", "assess_id_short", "Year", "CommName", "Biomass", "Catch", "BvBmsy", "FvFmsy", "Dbase", "SciName", "IdLevel", "SpeciesCat", "Profits", "MSY", "Price", "g", "k", "c", "phi", "itq", "ivq", "iq")
+
+fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turfs_edf_dt, by = c("Country", "SciName") , all.x = "TRUE")
 
@@
 74,76,77 = miscellaneous aquatic animals = 7
+
+###Rerun Logits with higher up species categories
 
@@
 
-###MPA New Costello Data
+##MPA New Costello Data
+
 These MPAs are at least partitally no-take but some of the percentages are very low
@@
 ```
+
+##Estimates of lost global economic value from lack of managemnet
+
+**1. Costello et al 2016 **
+2050
+
+-	RBFM policy applied to just stocks of conservation concern = $31 billion in fisheries profit
+
+-	RBFM policy applied to all stocks = $53 billion in fisheries profit
+
+**2. Original Sunken Billions (2009)**
+
+- “current annual net benefits from marine capture fisheries are tens of billions of U.S. dollars less than the potential benefits”
+```{r}
+include_graphics("sunkenbillionstable.png")
+```
+
+**3. Updated Sunken Billions (2012)**
+
+-	economic losses of about $83 billion

### 2019-01-03 lab_notebook.Rmd
labnotebook

@@
 ## MPA stuff
+
+##12/23/2018
+
+##KOBE Plots with only most recent year of fisheries
+###RAM only
+No data: ITQ = FALSE
+
+```{r}
+
+#read in data: this is updated projection data (updated using RAMs) and Corbett's ITQ/Turf data applied to each fishery. only data for most recent year for each fishery is represented.
+
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+#assuming that when no data is avaliable on the fishery inregardes to ITQ or Turfs that means there are none
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
+```
+
+```{r}
+
+#only looking at fisheries data that come from RAMS database
+# creating new column called "rightsbased" where 1 = ITQ and 0 = No ITQ
+fisheries_KOBE_ram <- fisheries_recent %>%
+  filter(Dbase == "RAM") %>%
+  mutate(rightsbased = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
+
+#graphing 
+fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "0"]<- "No ITQ"
+fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "1"]<- "ITQ"
+
+ggplot(data = fisheries_KOBE_ram, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
+  geom_point()+
+  labs(x = "B/Bmsy", y= "F/Fsmy") +
+  theme_minimal()+
+  theme(legend.title=element_blank())+
+  ylim(0, 2.5)+
+  xlim(0, 2.5)+
+  geom_hline(aes(yintercept=1))+
+  geom_vline(aes(xintercept=1))+
+  ggtitle("KOBE Plot: RAM only Fisheries")
+
+```
+
+##KOBE Plots with only most recent year of fisheries
+###All Data Sources
+No data: ITQ = FALSE
+```{r}
+
+fisheries_KOBE <- fisheries_recent %>%
+  mutate(rightsbased = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
+
+fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "0"]<- "No ITQ"
+fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "1"]<- "ITQ"
+
+#graphing 
+F_B_graph <- ggplot(data = fisheries_KOBE, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
+  geom_point()+
+  labs(x = "B/Bmsy", y= "F/Fsmy") +
+  theme_minimal()+
+  theme(legend.title=element_blank())+
+  ylim(0, 2.5)+
+  xlim(0, 2.5)+
+  geom_hline(aes(yintercept=1))+
+  geom_vline(aes(xintercept=1))+
+  ggtitle("KOBE Plot:  All Fisheries")
+
+```
+
+LOOK AT THIS TOMORROW. ITQ AND NO ITQ CATCH PROJECTIONS SHOULD BE THE SAME, USING SAME DATA, BUT THEY ARE NOT. WTF?
+
+##Total Catches in most recent year of ITQ, no ITQ, and Turfs
+```{r}
+
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+#assuming that when no data is present for itqs/turf that means there are none
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+
+fisheries_rightsbased <- fisheries_recent %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1"
+    ))
+
+turfs <- filter(fisheries_rightsbased, rightsbased == "2")
+itq <- filter(fisheries_rightsbased, rightsbased == "1")
+no_itq <- filter(fisheries_rightsbased, rightsbased == "0")
+
+sum(turfs$Catch, na.rm = TRUE)
+#174065.5
+
+sum(itq$Catch, na.rm = TRUE)
+#3874741
+
+sum(no_itq$Catch, na.rm = TRUE)
+#66155763
+
+```
+
+turf = 174,065.5 = 0.248% of total catch
+itq = 3,874,741 = 5.5% of total catch
+no itq = 66,155,763 = 94.23% of total catch
+Total = 70,204,569.5
+
+## Total Catch: A more generous estimation of Turf catch
+```{r}
+
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+#load in data for turf/itq only projection
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf)
+
+fisheries_recent_generousturf_1 <- select(fisheries_recent, Country, assess_id_short, Year.x,SciName, Catch, itq, ivq, iq)
+
+#merge the most recent data on each fishery with turf data
+fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1,turf_only, by = c("Country", "SciName") , all.x = "TRUE")
+
+#assuming that when no data is present for itqs/turf that means there are none
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1"
+    ))
+
+#create dfs for turf, itq, and no itq fisheries to calculate the sum of each
+#NOTE to rememeber: the data from these fisheries are the most recent numbers we have. they are not all in the same year 
+turfs_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
+itq_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "1")
+no_itq_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "0")
+
+sum(turfs_generous$Catch, na.rm = TRUE)
+#1530353
+
+sum(itq_generous$Catch, na.rm = TRUE)
+#8374634
+
+sum(no_itq_generous$Catch, na.rm = TRUE)
+#69025946
+
+```
+
+Generous Turf Catch Estimates:
+
+turf = 1,530,353 -> 1.93% global catch
+itq= 8,374,634 -> 10.6% global catch
+no itq =  69,025,946 -> 87.46% global catch
+
+Total: 78,930,933
+
+*note: 5643 actual rows
+5707 when manually added added
+- this means 64 species were matched with existing species in database
+- when separated out all by species it was worse
+- separate remaining by genus?
+
+##Logit regressions
+
+new UN GDP data, 2016 only
+Scaled GDPs
+Rerun Regressions
+###itq or turf: probablity of itq = f(ISSCAPP and GDP)
+
+```{r}
+
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf, SpeciesCat)
+
+fisheries_recent_generousturf_1 <- fisheries_recent %>%
+  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
+
+fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
+
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE | iq == FALSE | ivq == FALSE ~ "0"
+    ))
+
+gdp_all <- read_excel("data/un_gdp_2016.xls")
+
+gdp <- gdp_all %>%
+  select(Country, gdp_center) %>%
+  filter( gdp_center != "NA")
+
+merge_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))
+
+gdp_rightsbased <- filter(merge_gdp_rightsbased, SpeciesCat != "NA" )
+
+gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
+gdp_rightsbased$rightsbased <- as.numeric(gdp_rightsbased$rightsbased)
+
+itq_glm <- glm(formula = rightsbased ~ gdp_center + SpeciesCat, family = "binomial", data = gdp_rightsbased)
+itq_glm
+
+summary(itq_glm)
+```
+
+##Larger Categories for ISSCAAP Codes
+11,13 = freshwater fish = 1
+22-24 = diadromous fishes = 2
+31-35, 37 = marine fishes = 3
+42-45,47 = crustaceans = 4
+52-58 = molluscs = 5
+74,76,77 = miscellaneous aquatic animals = 7
+
+```{r}
+
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf, SpeciesCat)
+
+fisheries_recent_generousturf_1 <- fisheries_recent %>%
+  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
+
+colnames(fisheries_recent_generousturf_1) <- c("Country", "assess_id_short", "Year", "CommName", "Biomass", "Catch", "BvBmsy", "FvFmsy", "Dbase", "SciName", "IdLevel", "SpeciesCat", "Profits", "MSY", "Price", "g", "k", "c", "phi", "itq", "ivq", "iq")
+
+fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName", "SpeciesCat"), all = "TRUE")
+
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_regression_1 <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE | iq == FALSE | ivq == FALSE ~ "0"
+    )) %>%
+  mutate(MainCat = case_when(
+    SpeciesCat == 11 | SpeciesCat == 13 ~ "1",
+    SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",
+    SpeciesCat == 31 | SpeciesCat == 32 | SpeciesCat == 33 | SpeciesCat == 34 | SpeciesCat     == 35 | SpeciesCat == 37 ~ "3",
+    SpeciesCat == 42 | SpeciesCat == 43 | SpeciesCat == 44 | SpeciesCat == 45 | SpeciesCat      == 47 ~ "4",
+    SpeciesCat == 52 | SpeciesCat == 53 | SpeciesCat ==54 |  SpeciesCat == 55 | SpeciesCat     == 56 | SpeciesCat == 57 | SpeciesCat == 58 ~ "5",
+    SpeciesCat == 74 | SpeciesCat == 76 | SpeciesCat == 77 ~ "7"
+  )) %>%
+  select(Country, SciName, MainCat, rightsbased) %>%
+  filter(MainCat != "NA")
+
+gdp_all <- read_excel("data/un_gdp_2016.xls")
+
+gdp <- gdp_all %>%
+  select(Country, gdp_center) %>%
+  filter( gdp_center != "NA")
+
+merge_gdp_mc_rb <- merge(gdp, fisheries_recent_regression_1, by = c("Country"))
+
+gdp_mc_rb <- filter(merge_gdp_mc_rb, MainCat != "NA" )
+
+gdp_mc_rb$MainCat <- factor(gdp_mc_rb$MainCat)
+gdp_mc_rb$rightsbased <- as.numeric(gdp_mc_rb$rightsbased)
+
+itq_glm_mc <- glm(formula = rightsbased ~ gdp_center + MainCat, family = "binomial", data = gdp_mc_rb)
+
+itq_glm_mc
+
+summary(itq_glm_mc)
+
+```
+
+Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
+```{r}
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf, SpeciesCat)
+
+fisheries_recent_generousturf_1 <- fisheries_recent %>%
+  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
+
+fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
+
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "1",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "0"
+    ))
+
+gdp_all <- read_excel("data/un_gdp_2016.xls")
+
+gdp <- gdp_all %>%
+  select(Country, gdp_center) %>%
+  filter( gdp_center != "NA")
+
+join_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))
+
+gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )
+
+gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
+gdp_rightsbased$rightsbased <- as.numeric(gdp_rightsbased$rightsbased)
+
+itq_turf_glm <- glm(formula = rightsbased ~ gdp_center + SpeciesCat, family = "binomial", data = gdp_rightsbased)
+itq_glm
+
+summary(itq_turf_glm)
+
+```
+
+###Larger ISSCAAP Cat
+```{r}
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+
+turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
+
+turf_only <- turf_itq_isscaap %>%
+  select(SciName, Country, turf, SpeciesCat)
+
+fisheries_recent_generousturf_1 <- fisheries_recent %>%
+  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
+
+fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
+
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_turf_i_mc <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "1",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "0"
+    ))%>%
+  mutate(MainCat = case_when(
+    SpeciesCat == 11 | SpeciesCat == 13 ~ "1",
+    SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",
+    SpeciesCat == 31 | SpeciesCat == 32 | SpeciesCat == 33 | SpeciesCat == 34 | SpeciesCat     == 35 | SpeciesCat == 37 ~ "3",
+    SpeciesCat == 42 | SpeciesCat == 43 | SpeciesCat == 44 | SpeciesCat == 45 | SpeciesCat      == 47 ~ "4",
+    SpeciesCat == 52 | SpeciesCat == 53 | SpeciesCat ==54 |  SpeciesCat == 55 | SpeciesCat     == 56 | SpeciesCat == 57 | SpeciesCat == 58 ~ "5",
+    SpeciesCat == 74 | SpeciesCat == 76 | SpeciesCat == 77 ~ "7"
+  )) %>%
+  select(Country, SciName, MainCat, rightsbased) %>%
+  filter(MainCat != "NA")
+
+gdp_all <- read_excel("data/un_gdp_2016.xls")
+
+gdp <- gdp_all %>%
+  select(Country, gdp_center) %>%
+  filter( gdp_center != "NA")
+
+join_gdp_turf_i_mc <- merge(gdp, fisheries_recent_turf_i_mc, by = c("Country"))
+
+gdp_turf_i_mc <- filter(join_gdp_turf_i_mc, MainCat != "NA" )
+
+gdp_turf_i_mc$MainCat <- factor(gdp_turf_i_mc$MainCat)
+gdp_turf_i_mc$rightsbased <- as.numeric(gdp_turf_i_mc$rightsbased)
+
+turf_itq_mc_glm <- glm(formula = rightsbased ~ gdp_center + MainCat, family = "binomial", data = gdp_turf_i_mc)
+turf_itq_mc_glm
+
+summary(turf_itq_mc_glm)
+```
+
+##Diagnostics
+
+```{r}
+
+##run above chunk to get gdp_rightsbased df not the old csv file that is now archived in data folder
+
+diagnostics <- gdp_rightsbased %>%
+  mutate(management = case_when(
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    turf == TRUE ~ "2",
+    itq == FALSE | iq == FALSE | ivq == FALSE | turf == FALSE ~ "0"
+    )) %>%
+  select(Country, gdp_center, SpeciesCat, management)
+
+#diagnostics wont run with non-numeric?
+diagnostics$SpeciesCat <- as.numeric(diagnostics$SpeciesCat)
+diagnostics$management <- as.numeric(diagnostics$management)
+
+#2= gdp; 4= turf; 5 = SpeciesCat; 23 = itq; 24= ivq; 25 = iq; 26= binary rights based
+pairs(diagnostics[2:4])
+
+#pearson's r correlations
+cor(diagnostics[2:4])
+
+#run chi square?
+
+```
+
+####Bar Chart: Coefficient Species Category
+
+###MPA New Costello Data
+These MPAs are at least partitally no-take but some of the percentages are very low
+
+```{r}
+
+mpa_costello_data <- read_excel("data/mpa_costello_data.xlsx")
+
+##Choose only MPAs that have some no take
+mpa_no_take <- mpa_costello_data %>%
+  filter(no_take == "1")
+
+mpa_no_take_10 <- top_n(mpa_no_take, 10, mpa_area)
+mpa_no_take_10
+
+##all countries
+mpa_no_take_10$Country <- factor(mpa_no_take_10$Country, levels = mpa_no_take_10$Country[order(mpa_no_take_10$mpa_area)])
+
+ggplot(mpa_no_take_10, aes(x = Country, y = mpa_area)) +
+  geom_bar(stat = "identity")+
+  ggtitle("Top 10 Countries with No Take MPAs")+
+  coord_flip()+
+  theme_bw()+
+  ylab("Area km2")
+
+```
+
+These are the countries with the highest area of no-take
+```{r}
+mpa_costello_data <- read_excel("data/mpa_costello_data.xlsx")
+
+##Choose only MPAs that have some no take
+mpa_no_take <- mpa_costello_data %>%
+  filter(no_take == "1")
+
+mpa_no_take_area_10 <- top_n(mpa_no_take, 10, no_take_area)
+mpa_no_take_area_10
+
+##all countries
+mpa_no_take_area_10$Country <- factor(mpa_no_take_area_10$Country, levels = mpa_no_take_area_10$Country[order(mpa_no_take_area_10$no_take_area)])
+
+ggplot(mpa_no_take_area_10, aes(x = Country, y = no_take_area)) +
+  geom_bar(stat = "identity")+
+  ggtitle("Top 10 Countries with Largest No Take Areas")+
+  coord_flip()+
+  theme_bw()+
+  ylab("Area km2")
+
+```
+
+```{r}
+#load in DiscoverTURFs data
+d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx")
+edf_turf <- read_excel("data/EDF_TURF_data.xlsx")
+edf_turf_simple <- select(edf_turf, "country", "start_date", "SciName", "turf")
+
+colnames(edf_turf_simple) <- c("Country", "programstart", "SciName", "turf")
+
+turfs_edf_dt <- join(edf_turf_simple, d_turfs, by = c("Country", "SciName"), type = "full")
+
+#write.csv(turfs_edf_dt, file = "turfs_edf_dt.csv")
+
+```

### 2019-01-04 draft_figures_12.23.18.Rmd
updated 2016_projection_updated to only include data instead of projections

@@
 
+a = fisheries_recent %>% 
+  filter(Dbase == "RAM") %>% 
+  ggplot(aes(BvBmsy, FvFmsy, color =Dbase )) + 
+  geom_point() + 
+  coord_cartesian(xlim = c(0,4), ylim = c(0,4))
+
+timeseries_values_views %>% 
+  filter(year == 2016) %>% 
+  select(BdivBmsypref,UdivUmsypref) %>% 
+  na.omit() %>% 
+  nrow()
+  ggplot(aes(BdivBmsypref,UdivUmsypref)) + 
+  geom_point()
+
+  a
 ```
@@
 
-ggplot(data = fisheries_KOBE_ram, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(0, 2.5)+
-  xlim(0, 2.5)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))+
-  ggtitle("KOBE Plot: RAM only Fisheries")
-
+s
 ```

### 2019-01-04 scripts/2016_projection_updated.R

@@ -1,7 +1,5 @@
 
 #Loading packages
-
-suppressPackageStartupMessages({
   library(tidyverse)
   library(tidyr)
   library(here)
@@ -10,16 +8,20 @@ suppressPackageStartupMessages({
   library(readxl)
   library(devtools)
   library(plotly)
-  library(base)
   library(rio)
-  library(plyr)
   library(data.table)
-})
 
 Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
 
 #new dataframw with just most recent year of data for each fishery
-corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
+corbette_recent <- Countries_ITQ %>% 
+  group_by(assess_id_short) %>% 
+  filter(year == max(year))
+  
+  # setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
+
+
+# corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
 
 #filter out the fisheries with no data on itqs or turfs
 corbette_fisheries <- corbette_recent %>%
@@ -33,9 +35,14 @@ fisheries_with_itq <- corbette_fisheries %>%
   filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" | turf == "TRUE" )
 #Load Data
 #Upside data
-projection_data <- readRDS("data/projection_data.rds")
+projection_data <- readRDS("data/projection_data.rds") %>% 
+  filter(Scenario == "Historic") %>% 
+  group_by(IdOrig) %>% 
+  dplyr::mutate(max_year = max(Year)) %>% 
+  filter(max_year == 2012)
 
-#RAMS
+
+#RAM
 load("data/DBdata-model_fits_included.RData")
 
 
@@ -47,12 +54,27 @@ ram <- timeseries_values_views %>%
 colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
 
 #Update Projection with RAM
-projection_updated <- join(ram, projection_data, by = c("CommName", "Year"), type = "full")
+
+ram_data <- ram %>% 
+  left_join(projection_data %>% filter(Dbase == "RAM") %>% select(-BvBmsy,-FvFmsy,-Catch,-Biomass), by = c("CommName","Year")) %>% 
+select(colnames(projection_data))
+
[…]

### 2019-01-05 draft_figures_12.23.18.Rmd
reviewing Dan changes; median estimate graphs; new global catch percentages estiamtes

@@
   library(rio)
-  library(plyr)
   library(knitr)
+  library(doBy)
 })
@@
 
-timeseries_values_views %>% 
-  filter(year == 2016) %>% 
-  select(BdivBmsypref,UdivUmsypref) %>% 
-  na.omit() %>% 
-  nrow()
-  ggplot(aes(BdivBmsypref,UdivUmsypref)) + 
-  geom_point()
+b = fisheries_recent %>% 
+  ggplot(aes(BvBmsy, FvFmsy, color =Dbase )) + 
+  geom_point() + 
+  coord_cartesian(xlim = c(0,4), ylim = c(0,4))
+
+#timeseries_values_views%>% 
+#  filter(year == 2016) %>% 
+#  select(BdivBmsypref,UdivUmsypref) %>% 
+#  na.omit() %>% 
+#  nrow()  
+#  ggplot(aes(BdivBmsypref,UdivUmsypref)) + 
+#  geom_point()
 
 a
+
+b
+
+#median F and B values
+dbase_median <- fisheries_recent %>% 
+  select(BvBmsy,FvFmsy, Dbase) %>%
+    group_by(Dbase) %>%
+    na.omit() %>%
+    summarise_each(funs(median)) %>% 
+    ggplot()+
+    geom_point(aes(x=BvBmsy, y=FvFmsy, colour=Dbase))
+
+fisheries_median <-fisheries_recent %>% 
+  select(BvBmsy,FvFmsy) %>%
+    na.omit() %>%
+    summarise_each(funs(median)) %>% 
+    ggplot()+
+    geom_point(aes(x=BvBmsy, y=FvFmsy))
+
 ```
@@
 
-s
+F_B_graph_ram <- ggplot(data = fisheries_KOBE_ram, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
+  geom_point()+
+  labs(x = "B/Bmsy", y= "F/Fsmy") +
+  theme_minimal()+
+  theme(legend.title=element_blank())+
+  ylim(0, 2.5)+
+  xlim(0, 2.5)+
+  geom_hline(aes(yintercept=1))+
+  geom_vline(aes(xintercept=1))+
+  ggtitle("KOBE Plot:  RAM Fisheries")
+
+F_B_graph_ram
+
 ```
@@
   ggtitle("KOBE Plot:  All Fisheries")
+
+F_B_graph
+
+itq_median <- fisheries_KOBE %>% 
+  select(BvBmsy,FvFmsy, rightsbased) %>%
+  group_by(rightsbased) %>%
+    na.omit() %>%
+    summarise_each(funs(median)) %>% 
+    ggplot()+
+    geom_point(aes(x=BvBmsy, y=FvFmsy, colour = rightsbased))+
+  ggtitle("Medians for ITQ and non ITQ fisheries")
+itq_median
 
@@
 
-turf = 174,065.5 = 0.248% of total catch
-itq = 3,874,741 = 5.5% of total catch
-no itq = 66,155,763 = 94.23% of total catch
-Total = 70,204,569.5
+turf = 234000 = 0.29% of total catch
+itq = 4093520 = 5.1% of total catch
+
+Global Catch Estimate = 80 million
 
@@
 
-fisheries_recent_generousturf_1 <- select(fisheries_recent, Country, assess_id_short, Year.x,SciName, Catch, itq, ivq, iq)
+fisheries_recent_generousturf_1 <- select(fisheries_recent, Country, assess_id_short, Year,SciName, Catch, itq, ivq, iq)
 
@@
 
-turf = 1,643,571 -> 2.3% global catch
-itq= 3,874,741 -> 5.5% global catch
-no itq =  64,815,841 -> 92.1% global catch
+turf = 1246549 -> 1.5% global catch
+itq= 4093520 -> 5.1% global catch
 
-Total: 70,334,153
+Global Estimate = 80,000,000
 
@@
 fisheries_recent_generousturf_1 <- fisheries_recent %>%
-  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
+  select(Country, assess_id_short, Year, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
 
@@
 Larger Categories for ISSCAAP Codes
-11,13 = freshwater fish = 1
 22-24 = diadromous fishes = 2
@@
   mutate(MainCat = case_when(
-    SpeciesCat == 11 | SpeciesCat == 13 ~ "1",
     SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",

### 2019-01-05 lab_notebook.Rmd
reviewing Dan changes; median estimate graphs; new global catch percentages estiamtes

@@
 LOOK AT THIS TOMORROW. ITQ AND NO ITQ CATCH PROJECTIONS SHOULD BE THE SAME, USING SAME DATA, BUT THEY ARE NOT. WTF?
+- solved
 
@@
 ```
+
+#######################
+#######################
+1/2/2019
+
+Chris:
+1) The Kobe plot has a strange upward sloping line and a strange downward sloping line.  I wonder if you might be using the wrong FvFmsy or BvBmsy fields from RAM?  Dan - could you look at her code?
+
+2) The % of catch from ITQ (which you get as 5%) seems very low.  I think it should be around 25%.  Please re-check it.  Peruvian anchoveta alone should be around 9%.
+
+Dan:
+Almost looks like it’s plotting a control rule?
+Ohhhh you know what it might be?
+For the projections in te upside For the ITQ stocks it applies the MEY control rule to EQ, which would result in shutting down fishing for the low b values.
+There is some nuance in making sure that you’re getting status estimates not projections.
+Looked at the code, Juliette where is the .csv with the recent status estimates coming from?
+I don’t see any code to generate it in the repo.
+I’ll take a closer look tonight or tomorrow.
+But I’d bet that you’re pulling projections with a control rule applies instead of assessments
+
+##Total Catch: Most recent year for each fishery 
+```{r}
+
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+#assuming that when no data is present for itqs/turf that means there are none
+fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
+fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
+fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
+fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
+
+fisheries_turf_itqs_1 <-unique( fisheries_recent[ , 1:23 ] )
+
+fisheries_turf_itqs <- fisheries_turf_itqs_1 %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"
+    ))
+
+turfs_catch <- filter(fisheries_turf_itqs, rightsbased == "2")
+itq_catch <- filter(fisheries_turf_itqs, rightsbased == "1")
+no_itq_catch <- filter(fisheries_turf_itqs, rightsbased == "0")
+
+sum(turfs_catch$Catch, na.rm = TRUE)
+
+sum(itq_catch$Catch, na.rm = TRUE)
+
+sum(no_itq_catch$Catch, na.rm = TRUE)
+
+```
+
+turf = 174,065.5 = 0.248% of total catch
+itq = 3,874,741 = 5.5% of total catch
+no itq = 66,155,763 = 94.23% of total catch
+Total = 70,204,569.5
+
+## Total Catch: A more generous estimation of Turf catch
+
+```{r message =FALSE}
+
+#load data with info only on most recent year for each fishery (includes upside, updated with RAMs, corbette itq/turf data)
+fisheries_recent <- read_csv("data/fisheries_recent.csv")
+
+#turf data from edf and discover turfs
+turfs_edf_dt <- read_csv("data/turfs_edf_dt.csv")
+```
+
+```{r}
+
+fisheries_recent_generousturf_1 <- select(fisheries_recent, Country, assess_id_short, Year.x,SciName, Catch, itq, ivq, iq)
+
+#merge the most recent data on each fishery with turf data
+fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turfs_edf_dt, by = c("Country", "SciName") , all.x = "TRUE")
+
+#assuming that when no data is present for itqs/turf that means there are none
+fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
+fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
+fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
+fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
+
+fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1"
+    ))
+
+#create dfs for turf, itq, and no itq fisheries to calculate the sum of each
+#NOTE to rememeber: the data from these fisheries are the most recent numbers we have. they are not all in the same year
+
+turfs_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
+itq_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "1")
+no_itq_generous <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "0")
+
+sum(turfs_generous$Catch, na.rm = TRUE)
+
+sum(itq_generous$Catch, na.rm = TRUE)
+
+sum(no_itq_generous$Catch, na.rm = TRUE)
+
+```
+
+Generous Turf Catch Estimates:
+
+turf = 1,643,571 -> 2.3% global catch
+itq= 3,874,741 -> 5.5% global catch
+no itq =  64,815,841 -> 92.1% global catch
+
+Total: 70,334,153

### 2019-01-05 scripts/2016_projection_updated.R

@@ -13,7 +13,7 @@
 
 Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
 
-#new dataframw with just most recent year of data for each fishery
+#new dataframe with just most recent year of data for each fishery
 corbette_recent <- Countries_ITQ %>% 
   group_by(assess_id_short) %>% 
   filter(year == max(year))

### 2019-01-07 Past_draft_figs/11.06.2018.Meeting.Rmd
estimates catch from average 5 years and 10 years

--- 2018-12-21 lab_notebook.Rmd
@@
 ---
-title: "lab_notebook"
+title: "December 6th Check in Meeting Costello"
 author: "Juliette Verstaen"
-date: "November 2, 2018"
+date: "12/4/2018"
 output: html_document
@@
 
-#Loading packages
-```{r}
+#Generalized Linear Model
+```{r, echo = FALSE, message = FALSE}
 
@@
   library(plyr)
-  library(data.table)
 })
@@
 
-#converting projection csv into rds
-no longer need the code because have already used it to create the files
-```{r}
+```{r, echo = FALSE, message = FALSE}
 
-#Upside data
-#projection_data_csv <- read_csv("data/ProjectionData.csv")
-
-#saveRDS(projection_data_csv, "projection_data.rds")
-
-#WDPA_Nov2018.csv <- read_csv("data/WDPA_Nov2018.csv")
-
-#saveRDS(WDPA_Nov2018.csv, "WDPA_Nov2018.rds")
-
-```
-
-#Load Data
-```{r}
-
-#Corbet data: when countries began using RBFs
-countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
-
-#Upside data
-projection_data <- readRDS("data/projection_data.rds")
-
-#MPA data
-MPA <- readRDS("data/WDPA_Nov2018.rds")
-
-#RAMS
-load("data/DBdata-model_fits_included.RData")
-
-#number_species <- unique(stock$scientificname)
-#341 different species
-
-#cooperative data from "Conservation incentives and collective choices in cooperative fisheries" paper (Ovando et al 2013)
-jc_coop <- read_csv("data/clean_cooperatives_data.csv")
-
-#EDF turf data
-edf_turf <- read_excel("data/EDF_TURF_data.xlsx")
-
-```
-
-Important/Necessary Data
-tcbest.data #the best estimate of catch for that stock
-tbbest.dat # the best estimate of biomass for that stock
-divbpref # B/bmsy
-divupref.data # u/umsy
-
-Juliette Notes:
-
-Handy functions for updating data frames:
-match()
-separate()
-
-Useful Websites:
-https://uc-r.github.io/tidyr
-
-#RAM data wrangling
-```{r}
-ram <- timeseries_values_views %>%
-  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
-  add_column("RAM")
-
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
-
-#ram_2012 <- ram %>%
-#  filter(Year > "2012") 
-##this wont work because projection data has projected out past 2012. need to UPDATE
-
-#updated 
-#projection_ram <- bind_rows(list(projection_data, ram_2012))
-
-2012-1950
-#62
-2050- 2012
-#38
-162+38
-
-acheck <- filter(projection_ram, Year == "2013") %>%
-  select("IdOrig", "CommName", "Year", "Biomass")
-
-acheck_count <- unique(acheck$IdOrig)
-acheck_count
-#4714
-
-yearcheck <- unique(projection_data$Year)
-yearcheck
-#101 years starts 1950 end 2050
-
-join_project_ram <- join(projection_data, ram, by = c("CommName", "Year"), type = "full")
-
-projectramcheck <- filter(join_project_ram, IdOrig == "NA")
-#returns no rows with NA, could still be right if updated projected
-
-#Checking to see if better way to do join
-# end up with WAY to many rows, something is off
-#unite_projection_commname <- projection_data %>% 
-#  unite(name_year, CommName, Year, sep = "-")
-#unite_ram_commname <- ram %>% 
-#  unite (name_year, CommName, Year, sep = "-")
-#join_project_ram_2 <- join(unite_projection_commname, unite_projection_commname, by = "name_year", type = "left")
-
-match_project_ram <- match(projection_data, ram)
-
-```
-
-#Data Wrangling: Projection and Countries ITQ
-```{r}
-
-#seperate out IdOrig column for Projection Data
-separate_projection <- projection_ram %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
-
-head(separate_projection, 10)
-
-#reunite just the two parts we care about: agency and stock
-unite_projection <- separate_projection %>% unite(assess_id_short, agency, stock, sep = "-")
-
-#simplifying Countries ITQ with unique columns to prepare to merge
-countries_ITQ_simple <- select(countries_ITQ, "assess_id_short", "year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-#rename year to be capitalized to merge with projection data
-colnames(countries_ITQ_simple) <- c("assess_id_short", "Year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-ITQ_projection_merge <- merge(unite_projection, countries_ITQ_simple, by = c("assess_id_short", "Year"), all = TRUE)
-
-#cleaning it up
-ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, data_enterer, sep = "-")
-
-```
-
-Playing with Data
-
-#Total number of species with stocks
-#Number of stocks with ITQs implemented
-```{r}
-IdOrig <- unique(ITQ_projection$SciName)
-IdOrig
-#1228 species total
-
-ITQ_projection_implemented <- filter(ITQ_projection, programstart != "NA")
-
-IdOrig_implemented <- unique(ITQ_projection_implemented$SciName)
-IdOrig_implemented
-#80 species with ITQ implemented
-```
-
-#Graphs for fun
-
-ABARES_BGRDRSE
-implemented ITQs in 1992
-```{r}
-
-ABARES_BGRDRSE <- filter(ITQ_projection, IdOrig == "ABARES-BGRDRSE-1960-2011-CHING")
-
-graph_ABARES_BGRDRSE <-ggplot(ABARES_BGRDRSE, aes(x=Year, y=Biomass))+
-  geom_line(size=1)+
-  ggtitle("ABARES_BGRDRSE (Australia")+
-  geom_point()+
-  geom_line()+
-  labs(x="Year", y="Yearly total biomass")+
-  theme_classic()+
-  scale_x_continuous(expand=c(0,0))+
-  scale_y_continuous(expand=c(0,0))+
-  geom_vline(xintercept = 1992)+
-  theme(legend.title=element_blank())
-
-ggplotly(graph_ABARES_BGRDRSE)
-
-#figure out an if then statement for line?
-
-```
-
-ADFG-HERRTOGE
-never implemented ITQs
-```{r}
-ADFG_HERRTOGE <- filter(ITQ_projection, IdOrig == "ADFG-HERRTOG-1990-2010-HIVELY")
-
-graph_ADFG_HERRTOGE <-ggplot(ADFG_HERRTOGE, aes(x=Year, y=Biomass))+
-  geom_line(size=1)+
-  ggtitle("ADFG-HERRTOGE (USA)")+
-  geom_point()+
-  geom_line()+
-  labs(x="Year", y="Yearly total biomass")+
-  theme_classic()+
-  scale_x_continuous(expand=c(0,0))+
-  scale_y_continuous(expand=c(0,0))+
-  theme(legend.title=element_blank())
-
-ggplotly(graph_ADFG_HERRTOGE)
-
-#figure out an if then statement for line?
-```
-
-Important/Necessary Data
-tcbest.data #the best estimate of catch for that stock
-tbbest.dat # the best estimate of biomass for that stock
-divbpref # B/bmsy
-divupref.data # u/umsy
-
-Attempts at updating ITQ_projection with Rams
-#asked ana about this -> waiting to hear back
-```{r}
-
-##this doesn't work; gives you vector not updated data frame
-RAMS_ITQ_projection <- match(ITQ_projection_year$CommYear, ram_merge$CommYear)
-
-#what happens when i just merge the two?
-#test_merge <- merge(ITQ_projection_year, ram_merge, by = c("Name_Year"))
-
-```
-
-##edf turf data wrangling
-# waiting for data from Gina if its more comprehensive than the EDF one
-```{r}
-
-edf_turf_unite <- edf_turf %>% unite(SciName, genus, species, sep = " ")
-
-edf_turf_simple <- edf_turf_unite %>%
-  add_column("turf") %>%
-  select("country", "start_date", "SciName") %>%
-  gsub('\\bNA NA\\b', 'NA')
-
-colnames(edf_turf_simple) <- c("Country", "turfstart", "SciName")
-
-##want to merge the edf simple with ITQ/Projections but maybe wait for Gina to respond with her TURF data
-##in ITQ data says only one species of fish in japan has TURFs but not true
-
-edf_projection_itq <- merge(ITQ_projection, edf_turf_simple, by = c("Country", "SciName"))
-#only three species from the EDF data match with the species from the upside/projection data; all in Japan
-
-```
-
-Need to create new dataset (half upside half ITQ): Species, turf/itq, country,and then matching all the parameters with the species
-
-################
-################
-###############
-PART 2
-1) pull the ITQ, IVQ, IQ fisheries out of upside.
-2) pull the TURF fisheries from EDF.
-3) For each fishery, we want species, location, and ITQ vs. TURF.
-
-From updating_projection.R script file
-```{r}
-
-#Load Data
-#Upside data
-projection_data <- readRDS("data/projection_data.rds")
-
-#RAMS
-load("data/DBdata-model_fits_included.RData")
-
-#Corbet data: when countries began using RBFs
-countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
-
-#RAM Data Tiddying
-ram <- timeseries_values_views %>%
-  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
-  add_column("RAM")
-
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
-
-#Update Projection with RAM
-projection_updated <- join(projection_data, ram, by = c("CommName", "Year"), type = "full")
-
-#Merge Projection and ITQ
-#seperate out IdOrig column for Projection Data
-separate_projection <- projection_updated %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
-
-head(separate_projection, 10)
-
-#reunite just the two parts we care about: agency and stock
-unite_projection <- separate_projection %>% unite(assess_id_short, agency, stock, sep = "-")
-
-#simplifying Countries ITQ with unique columns to prepare to merge
-countries_ITQ_simple <- select(countries_ITQ, "assess_id_short", "year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-#rename year to be capitalized to merge with projection data
-colnames(countries_ITQ_simple) <- c("assess_id_short", "Year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-ITQ_projection_merge <- merge(unite_projection, countries_ITQ_simple, by = c("assess_id_short", "Year"), all = TRUE)
-
-#cleaning it up
-ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, data_enterer, sep = "-")
-
-#create RDS from dataframe
-saveRDS(ITQ_projection, "ITQ_projection.rds")
-
-#simplified projection data
-ITQ_projection_simple <- ITQ_projection %>%
-  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi", "yearitq", "itq_now","iq", "itq", "ivq", "turf", "programstart")
-
-#create RDS from dataframe
-#saveRDS(ITQ_projection_simple, "projection_updated.rds")
-
-#upside updated
-upside_2018_updated <- ITQ_projection %>%
-  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi")
-
-#create RDS from dataframe
-#saveRDS(upside_2018_updated, "upside_2018_updated")
-
-```
-
-#load data
-```{r}
-
-# create dataframe with 
-ITQ_projection <- readRDS("processed_data/ITQ_projection.rds")
-
-itq <- ITQ_projection %>%
-  select("Country", "SciName", "itq_now","iq", "itq", "ivq", "turf", "programstart")
-
-#Load EDF TURF data
-
-edf_turf <- read_excel("data/EDF_TURF_data.xlsx")
-
-#load in DiscoverTURFs data
-
-d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx")
-
-```
-
-#data wrangling
-```{r}
-
-edf_turf_simple <- select(edf_turf, "country", "start_date", "SciName", "turf")
-#create new column that says "turf" and TRUE or FALSE
-
-colnames(edf_turf_simple) <- c("Country", "programstart", "SciName", "turf")
-
-#combining edf turf data from upside data
-edf_projection_1 <- join(edf_turf_simple, itq, by = c("Country", "programstart", "SciName", "turf"), type = "full")
-
-#combine edf/upside with discover turfs
-all_turf_1 <- join(edf_projection_1, d_turfs, by = c("Country", "SciName", "turf"), type = "full")
-
-#change "blank" NAs to real NAs
-#all_turf_1[is.na(all_turf_1)] <- "NA"
-
-#rearrange columns
-all_turf_itq <- all_turf_1[, c(1,3,2,5,6,7,8,4)]
-
-#turning NAs from no ITQ data to FALSE
-#all_turf_2[all_turf_2 == 0] <- NA
-
-all_turf_itq$iq[is.na(all_turf_itq$iq)] <- FALSE
-
-all_turf_itq$itq[is.na(all_turf_itq$itq)] <- FALSE
-
-all_turf_itq$ivq[is.na(all_turf_itq$ivq)] <- FALSE
-
-all_turf_itq$itq_now[is.na(all_turf_itq$itq_now)] <- 0
-
-#create RDS from dataframe
-#saveRDS(all_turf_itq, "all_turf_itq.rds")
-#write.csv(all_turf_itq, file = "all_turf_itq.csv")
-
-```
-
-###################
-##################
-
-Part 3
-
-1) include only species that are either TURF, ITQ, IVQ, etc. (omit species that are FALSE for everything).
-2) Include each fishery only once (not multiple years).
-3) so then see how hard it is to collect other characteristics for each species (like growth rate or ISCAAP category).
-
-1 & 2
-```{r}
-
-#filter out all countries that don't have itqs or turfs
-true_turf_itq_1 <- all_turf_itq %>%
-  filter (iq == "TRUE" | itq == "TRUE" | ivq == "TRUE" | turf == "TRUE") %>%
-  filter( Country != "NA") %>%
-  select("Country", "SciName", "iq", "itq", "ivq", "turf")
-
-true_turf_itq <- unique(true_turf_itq_1 [ , 1:6])
-
-unique(true_turf_itq$Country)
-#33 countries
-#Chile, Fiji, Italy, Japan, Mexico, Papua New Guinea, Samoa, Solomon Islands, Spain, Sri Lanka, Sweden, Vanuatu, Vietnam, Australia, USA, Canada, Peru, Argentina, South Africa, New Zealand, American Samoa, Belize, Brazil, Ecuador, France, Greece, India, Netherlands, Nigeria, Philippines, St Lucia, United States, United Kingdom
-
-#chile_itq_turf <- filter(true_turf_itq, Country == "Chile")
-#unique(chile_itq_turf$SciName)
-# 67
-
-#fiji_itq_turf <- filter(only_turf_itq, Country == "Fiji")
-#unique(fiji_itq_turf$SciName)
-
-#test_duplicate <- unique(fiji_itq_turf[ , 1:8])
-
-```
-
-3
-ISCAAP
-```{r}
-
-iscaap_cat_1 <- upside_2018_updated %>%
-  select("SciName", "SpeciesCat")
-
-iscaap_cat <- unique(iscaap_cat_1 [ , 1:2])
-
-true_turf_itq_iscaap_1 <- merge(true_turf_itq, iscaap_cat, by = "SciName", all = T)
-
-true_turf_itq_iscaap <- true_turf_itq_iscaap_1 %>%
-  filter( itq != "NA" & ivq != "NA" & iq != "NA" & turf != "NA")
-
-true_turf_itq_iscaap[is.na(true_turf_itq_iscaap)] <- "NA"
-
-missing_speccat <- true_turf_itq_iscaap %>%
-  filter(SpeciesCat == "NA")
-
-#write.csv(true_turf_itq_iscaap, file = "true_turf_itq_iscaap.csv")
-
-determine_spec_cat <- as.vector(missing_speccat$SciName)
-determine_spec_cat
-
-```
-
-FishBase
-
-```{r}
-
-library("rfishbase")
-
-species <- as.vector(true_turf_itq_iscaap$SciName)
-species
-
-table_species <- species(species)
-
-growth <- popgrowth(species)
-
-#fishtest <- species_list(Genus = "Labroides")
-#fishtest
-#species(fishtest)
-#even running the practice online tutorial get this error :Error in curl::curl_fetch_memory(url, handle = handle) : Timeout was reached: Connection timed out after 10004 milliseconds
-
-#fishbase_test <- validate_names(species, fields = c("Species", ""))
-
-```
-
-FAO website with fisheries data is currently unavaliable. Updated by hand for now; read in below 
-```{r}
-species_rightsbased <- read_csv("data/species_rightsbased.csv")
-
-ISSCAAP_species <- select(species_rightsbased, SciName, SpeciesCat)
-#write.csv(ISSCAAP_species, file ="ISSCAAP_species.csv")
-```
--	used FAO 3-Alpha species codes (ASFIS) updated 2/2009
--	ones with no ISSCAPP # still are shellfish, snails, crabs, not species specific, common name, species in NA, or a family name with more than 1 #
-
-###########
-
-Part 4:
-For TURF/ITQ data, add GDP/capita for each country, also do ISCAAP categories. Combine all ITQ,IQ etc. Run logit of Prob(ITQ) = f(ISCAAP, GDP).
-```{r}
-
-species_rightsbased_binary <- read_csv("data/species_rightsbased_binary.csv")
+species_rightsbased <- read_csv("data/species_rightsbased_binary.csv")
 
@@
 
-```{r}
+```{r, echo = FALSE, message = FALSE}
 
@@
 
-join_gdp_rightsbased <- join(gdp, species_rightsbased_binary, by = c("Country"), type = "full")
+join_gdp_rightsbased <- join(gdp, species_rightsbased, by = c("Country"), type = "full")
 
@@
 
-##make sure that these stats are not effected by year 2012 onward not having info on itq or not. i think this data was not year specific so it should be fine? but look at the data
-
-gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
+#gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
 
@@
 
-#turf_glm <- glm(turf ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
-#turf_glm
-#summary(turf_glm)
-
 ```
 
-Part 5:
-RAM only: F/Fmsy vs. B/Bmsy for all fisheries. Color ITQ differently.
+#F/Fmsy vs. B/Bmsy for all fisheries
 
-2. From upside sorts KOBE: ITQ versus non ITQ and the size of dot is the catch
-#this is all the data we have, make the same ones with only certain years and such
+```{r, echo = FALSE, message = FALSE}
 
-```{r}
-
-ITQ_projection <- readRDS("processed_data//not_actively_used/ITQ_projection.rds")
+ITQ_projection <- readRDS("data/ITQ_projection.rds")
 
 f_b_itq <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
+  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq") %>%
+  filter( itq != "NA", iq != "NA", ivq != "NA")
 
-#turf == TRUE ~ "2",
 #write.csv(f_b_itq, file = "f_b_itq.csv")
-#f_b_irights <- read_csv("data/f_b_irights.csv")
-#this was when i couldn't figure out how to do the if then statement in R
+f_b_irights <- read_csv("data/f_b_irights.csv")
 
-#F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights, size = catch ))+
-
-# get data frame that was
-F_B_graph <- ggplot(data = f_b_itq, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
+F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights ))+
   geom_point()+
@@
   theme(legend.title=element_blank())+
-  ylim(-1, 5)+
+  ylim(-1, 22)+
   xlim(-.3, 3)+
@@
 ```
-
-######
-MPA data wrangling
-######
-```{r}
-
-ISO_country_codes <- read_excel("data/ISO_country_codes.xlsx")
-MPA <- readRDS("data/WDPA_Nov2018.rds")
-
-mpa_simple <- MPA %>%
-  select("NAME", "PA_DEF", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS", "PARENT_ISO3") %>%
-  filter(MARINE != "0")
-
-colnames(mpa_simple) <- c("NAME", "PA_DEF", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS", "code")
-
-mpa_join <- join(mpa_simple, ISO_country_codes, by = c("code"), type = "full")
-
-mpa_updated <- mpa_join %>%
-  select("Country", "NAME", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS" ) %>%
-  filter(NAME != "NA" & DESIG_ENG != "NA" & DESIG_TYPE != "NA" & IUCN_CAT != "NA" & MARINE != "NA" & REP_M_AREA != "NA" & NO_TAKE != "NA" & STATUS != "NA")
-
-#write.csv(mpa_updated, file = "mpa_updated.csv")
-
-```
-
-PA_DEF: Allowed values: 1 (meets IUCN and/or CBD PA definition); 0 (does not meet IUCN and/or CBD PA definition (currently stored outside WDPA)).
-
-MARINE: Allowed values: 0 (100% Terrestrial PA), 1 (Coastal: marine and terrestrial PA), and 2 (100 % marine PA).
-
-#############
-############
-1.	From upside want to know the catch in ITQ versus non ITQ for most recent year
-
-- issues: unsure what year real data ends and projectio/modeling begins
-- pretty sure its 2016. there are thee fisheries with 2017 data in the updated RAMS dataset but more for 2016
-
-update recent years fisheries
-
-issue: the projection data updated with RAMs doens't have ITQ data associated with the countries
-- need a list of all the countries and whether or not they have ITQ in 2016 -> this can be pulled from Corbett's data. need to check if his data is from that year
-
-1.	From upside want to know the catch in ITQ versus non ITQ for most recent year
-corbet data only goes up until 2012 
-```{r}
-
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-f_b_itq_countries <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
-  mutate(rightsbased = case_when(
-    turf == TRUE ~ "2",
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-countries_itq_2012 <- f_b_itq_countries %>%
-  select (Country, rightsbased, Year, IdOrig, Catch) %>%
-  filter(Year == "2012")
-
-ITQ_projection_2016 <- ITQ_projection %>%
-  filter(Year == "2016") %>%
-  select(IdOrig, Country)
-
-itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012, by= c("IdOrig", "Country"), type= "full")
-
-itq_2016_rightsbasedTRUE <- filter(itq_2016_updated, rightsbased == "1")
-
-itq_2016_rightsbasedFALSE <- filter(itq_2016_updated, rightsbased == "0")
-
-itq_2016_rightsbasedTURF <- filter(itq_2016_updated, rightsbased == "2")
-
-sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
-#27,830,933
-sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
-#266,328,075
-
-sum(itq_2016_rightsbasedTURF$Catch, na.rm = TRUE)
-#1505000
-
-```
-
-updating projection datapast 2012  with the 2012 itq fisheries
-```{r}
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-f_b_itq_countries <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
-  mutate(rightsbased = case_when(
-    turf == TRUE ~ "2",
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-countries_itq_2012 <- f_b_itq_countries %>%
-  select (Country, rightsbased, Year, IdOrig, Catch) %>%
-  filter(Year == "2012")
-
-ITQ_projection_past2012 <- ITQ_projection %>%
-  filter(Year > 2012)
-
-ITQ_projection_past2012UPDATED <- join(ITQ_projection_past2012, countries_itq_2012, by = c("Country", "Year", "IdOrig"), type = "full" )
-
-ITQ_projection_pre2012 <- ITQ_projection %>%
-  filter(Year <= 2012)
-
-ITQ_projection_updated <- join(ITQ_projection_past2012UPDATED,ITQ_projection_pre2012, by = c("Country", "Year", "IdOrig"), type = "full")
-
-#saveRDS(ITQ_projection_updated, "ITQ_projection_updated.rds")
-
-ITQ_projection_updated <- readRDS("data/ITQ_projection_updated.rds")
-
-f_b_itq_updated <- ITQ_projection_updated %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-F_B_graph_updated <- ggplot(data = f_b_itq_updated, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(-1, 5)+
-  xlim(-.3, 3)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))
-
-#F_B_graph
-ggplotly(F_B_graph_updated)
-
-```
-
-###Did this chunck before figured out how to do if/then statements in r
-
-```{r}
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-#filter down the data to create a data set of countries that have ITQs so I can add that to the rams data. upside has this info but not the updated part
-
-#2012 is the most updated version of the upside data.
-used this to figure out which counties have ITQs and will make a data frame from that of a list of countires that have itqs and then update the final datafram (or inital rams dataframe)
-countries_with_ITQ <- ITQ_projection %>%
-  select (Country, itq, iq, ivq, Year, IdOrig) %>%
-  filter(Year == "2012")
-
-countries_with_ITQ_2 <- unique(countries_with_ITQ[, 1:6])
-countries_with_ITQ_3 <- filter(countries_with_ITQ_2, itq != "NA" | iq != "NA" | ivq != "NA")
-
-countries_with_ITQ_3$rightsbased <- 1
-countries_itq_2012 <- select(countries_with_ITQ_3, Country, IdOrig, rightsbased)
-
-#now need to create new column thats rights based fishereise 0 o for projection 2016
-
-ITQ_projection_2016 <- ITQ_projection %>%
-  filter(Year == "2016") %>%
-  select(IdOrig, Country, Catch)
-
-itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012, by= c("IdOrig", "Country"), type= "full")
-
-itq_2016_updated$rightsbased[is.na(itq_2016_updated$rightsbased)] <- 0
-
-#seperate rights based and not
-itq_2016_rightsbasedTRUE <- filter(itq_2016_updated, rightsbased == "1")
-
-itq_2016_rightsbasedFALSE <- filter(itq_2016_updated, rightsbased == "0")
-
-sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
-#27,830,933
-sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
-#266,328,075
-
-##units???
-
-```
-
-###Need to update the ITQ_projection rds file and the ITQ_projection_updated rds file (1st file is without applying ITQ info past 2012 and the second is)
-
-##ADD THIS INTO THE SCRIPT FOR UPDATING UPSIDE DATA
-```{r}
-ISSCAAP_species <- read_csv("data/ISSCAAP_species.csv")
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-ITQ_projection_isscaap_1 <- join(ISSCAAP_species,ITQ_projection, by = c("SciName", "SpeciesCat"), type = "full" )
-
-ITQ_projection_isscaap <- ITQ_projection_isscaap_1 %>%
-  filter(Country != "NA")
-
-```
-
-In the updated ITQ projection data there are lines of data that have 2012 with NA instead of TRUE/FALSE for itq.
-
-#data we have says that Mexico does not have ITQs?
-in 2012 only ones it says we have are Australia, USA, Canda, Japan, Peru, Argentina, South Africa, New Zealand
-
-Fixing upside data
-- take ITQ projection an filter it down to idorig, year, BvBmsy", "FvFmsy", "itq", "iq", "ivq"
-- filter out just ones with itqs, create a column thats rights based fisherse and make it one
-- filter out specifics of itq
-- merge/join that data with the countries_itq2012 with country, idorig, and rihgts based
-- make nas zero
--redo kobe plot with this data
-- also cut off at 5
-
-#this was from before figured out if then statement
-
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-itq_selected <- ITQ_projection %>%
-  select(IdOrig,Country, Year, BvBmsy, FvFmsy, itq, iq, ivq) %>%
-  filter(itq != "NA" | iq != "NA" | ivq != "NA")
-
-itq_selected$rightsbased <- 1
-
-itq_selected_2 <- select(itq_selected,Country, IdOrig, Year, rightsbased)
-
-itq_new_join <- join(itq_selected_2, countries_itq_2012, by = c(Country, IdOrig, Year), type = "full")
-
-##not using this anymore
-
-ITQ_projection <- readRDS("processed_data//not_actively_used/ITQ_projection.rds")
-
-countries_with_ITQ <- ITQ_projection %>%
-  select (Country, itq, iq, ivq, Year, IdOrig) %>%
-  filter(Year == "2012")
-
-countries_with_ITQ_2 <- unique(countries_with_ITQ[, 1:6])
-countries_with_ITQ_3 <- filter(countries_with_ITQ_2, itq != "NA" | iq != "NA" | ivq != "NA")
-
-countries_with_ITQ_3$rightsbased <- 1
-countries_itq_2012 <- select(countries_with_ITQ_3, Country, IdOrig, rightsbased)
-
-##need to update projection data
-
-f_b_itq <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA")
-
-ISSCAAP Codes and the non-species specific codes
-```{r}
-
-meta_isscaap_codes_1 <- join(isscaap_codes, ISSCAAP_species, by = c("SciName", "SpeciesCat"), type = "full")
-
-meta_isscaap_codes <- unique( meta_isscaap_codes_1[ , 1:2 ] )
-write_csv(meta_isscaap_codes, "meta_isscaap_codes.csv")
-```
-
-12/18/2018
-Using the newly updated upside/ITQ and filtering out only the most recent date for each fishery
-- make a df of these that have ITQs and those that don't -> apply to OG upside/ITQ data so that more recent years can have ITQ data
-- take this new df and filter out the most recent years with ITQs and KOBE plot. also do catches
-
-```{r}
-
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-upside_2016 <- ITQ_projection %>%
-  filter(Year <= "2016") %>%
-  unite(id_country, IdOrig, Country, sep = "-")
-
-upside_recent <- setDT(upside_2016)[,.SD[which.max(Year)],keyby=id_country]
-
-upside_allfisheriesITQ <- upside_recent %>%
-  select (id_country, itq, iq, ivq, Year, turf) %>%
-  filter(itq != "NA" & iq != "NA" & ivq != "NA" )
-
-```
-
-#Pulling out information about ITQs/TURFs in Corbette Data to apply to upside data
-```{r}
-
-Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
-
-#new dataframw with just most recent year of data for each fishery
-corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
-
-#filter out the fisheries with no data on itqs or turfs
-corbette_fisheries <- corbette_recent %>%
-  select(assess_id_short, year, speciescat, iq, itq, ivq, coop, turf)%>%
-  filter(itq != "NA" & iq != "NA" & ivq != "NA")%>%
-  filter(turf != "NA" )
-
-#new data frame with just data on fisheries with itqs
-fisheries_with_itq <- corbette_fisheries %>%
-   filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" | turf == "TRUE" )
-
-```
-
-reupdating upside data with new ITQ list
-
-```{r}
-#Load Data
-#Upside data
-projection_data <- readRDS("data/projection_data.rds")
-
-#RAMS
-load("data/DBdata-model_fits_included.RData")
-
-#RAM Data Tiddying
-ram <- timeseries_values_views %>%
-  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
-  add_column("RAM")
-
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
-
-#Update Projection with RAM
-projection_updated <- join(ram, projection_data, by = c("CommName", "Year"), type = "full")
-##note: RAM data has some fisheries not in the projection data, thus adding new fisheries to the upside projection data
-
-#separate and unit functions to create a shorter version of the stock assessment ID to merge with corbette ITQ/TURF data later
-separate_projection <- projection_updated%>% 
-  separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
-
-unite_projection <- separate_projection %>% 
-  unite(assess_id_short, agency, stock, sep = "-")
-
-colnames(fisheries_with_itq) <- c("assess_id_short", "Year","SpeciesCat" , "iq", "itq", "ivq", "coop", "turf")
-
-#merge corbette's data on ITQ/Turf implemented or not for each fishery
-fishery_itq_simple <- fisheries_with_itq %>%
-  select(assess_id_short,iq, itq, ivq, turf )
-
-ITQ_projection_merge <- merge(unite_projection, fisheries_with_itq, by = c("assess_id_short"), all = TRUE)
-
-#filter out data post 2016 because we know that those are projected/modeled data not recorded
-recent_pre2016 <- ITQ_projection_merge %>%
-  filter(Year.x <= "2016")
-
-#keep only info on most recent year for each fishery  
-fisheries_recent_1 <- setDT(recent_pre2016)[,.SD[which.max(Year.x)],keyby=assess_id_short]
-
-#select the columns we are interested in
-fisheries_recent <- fisheries_recent_1 %>%
-  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq, turf)
-
-#write dataframe to csv file
-#fisheries_recent <- write.csv(fisheries_recent, file = "fisheries_recent.csv")
-
-```
-
-##KOBE Plots with only most recent year of fisheries
-RAM only
-No data: ITQ = FALSE
-
-```{r}
-
-#read in data: this is updated projection data (updated using RAMs) and Corbett's ITQ/Turf data applied to each fishery. only data for most recent year for each fishery is represented.
-
-fisheries_recent <- read_csv("data/fisheries_recent.csv")
-
-#assuming that when no data is avaliable on the fishery inregardes to ITQ or Turfs that means there are none
-fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
-fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
-fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
-fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
-
-#only looking at fisheries data that come from RAMS database
-# creating new column called "rightsbased" where 1 = ITQ and 0 = No ITQ
-fisheries_KOBE_ram <- fisheries_recent %>%
-  filter(Dbase == "RAM") %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-#graphing logistics
-fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "0"]<- "No ITQ"
-fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "1"]<- "ITQ"
-
-F_B_graph_RAM <- ggplot(data = fisheries_KOBE_ram, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(0, 2.5)+
-  xlim(0, 2.5)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))+
-  ggtitle("KOBE Plot: RAM only Fisheries")
-
-#F_B_graph
-ggplotly(F_B_graph_RAM)
-
-```
-
-##KOBE Plots with only most recent year of fisheries
-RAM only
-No data: ITQ = FALSE
-```{r}
-
-#read in data: this is updated projection data (updated using RAMs) and Corbett's ITQ/Turf data applied to each fishery. only data for most recent year for each fishery is represented.
-fisheries_recent <- read_csv("data/fisheries_recent.csv")
-
-#assuming that when no data is avaliable on the fishery inregardes to ITQ or Turfs that means there are none
-fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
-fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
-fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
-fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
-
-fisheries_KOBE <- fisheries_recent %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "0"]<- "No ITQ"
-fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "1"]<- "ITQ"
-
-#graphing logistics
-F_B_graph <- ggplot(data = fisheries_KOBE, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(0, 2.5)+
-  xlim(0, 2.5)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))+
-  ggtitle("KOBE Plot:  All Fisheries")
-
-#F_B_graph
-ggplotly(F_B_graph)
-
-```
-
-## adding turf information to upside projection(ie: fisheries_recent)
-```{r}
-
-#load in data for turf/itq only projection
-turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
-
-turf_only <- turf_itq_isscaap %>%
-  select(SciName, Country, turf)
-
-fisheries_recent_generousturf_1 <- select(fisheries_recent, Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
-
-#merge the most recent data on each fishery with turf data
-fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turf_only, by = c("Country", "SciName")) #, all = "TRUE")
-
-#assuming that when no data is present for itqs/turf that means there are none
-fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
-fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
-fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
-fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
-
-fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
-  mutate(rightsbased = case_when(
-    turf == TRUE ~ "2",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1"
-    ))
-
-#create dfs for turf, itq, and no itq fisheries to calculate the sum of each
-#NOTE to rememeber: the data from these fisheries are the most recent numbers we have. they are not all in the same year 
-turfs <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
-itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "1")
-no_itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "0")
-
-sum(turfs$Catch, na.rm = TRUE)
-
-sum(itq$Catch, na.rm = TRUE)
-
-sum(no_itq$Catch, na.rm = TRUE)
-
-```
-
-turf only = 413 rows
-fisheries recent = 5294
-
-5643 actual rows
-5707 when manually added added
-- this means 64 species were matched with existing species in database
-- when separated out all by species it was worse
-
-- separate remaining by genus?
-
-12/20/2018
-new UN GDP data, 2016 only
-Scaled GDPs
-Rerun Regressions
-###itq or turf: probablity of itq = f(ISSCAPP and GDP)
-*regression converges*
-```{r}
-
-fisheries_recent <- read_csv("data/fisheries_recent.csv")
-
-fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
-fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
-fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
-fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
-
-turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
-
-turf_only <- turf_itq_isscaap %>%
-  select(SciName, Country, turf, SpeciesCat)
-
-fisheries_recent_generousturf_1 <- fisheries_recent %>%
-  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
-
-fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
-
-fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
-fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
-fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
-fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
-
-fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE | iq == FALSE | ivq == FALSE ~ "0"
-    ))
-
-gdp_all <- read_excel("data/un_gdp_2016.xls")
-
-gdp <- gdp_all %>%
-  select(Country, gdp_center) %>%
-  filter( gdp_center != "NA")
-
-join_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))
-
-gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )
-
-gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
-gdp_rightsbased$rightsbased <- as.numeric(gdp_rightsbased$rightsbased)
-
-itq_glm <- glm(formula = rightsbased ~ gdp_center + SpeciesCat, family = "binomial", data = gdp_rightsbased)
-itq_glm
-
-summary(itq_glm)
-
-```
-
-Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
-
-```{r}
-fisheries_recent <- read_csv("data/fisheries_recent.csv")
-
-fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
-fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
-fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
-fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
-
-turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
-
-turf_only <- turf_itq_isscaap %>%
-  select(SciName, Country, turf, SpeciesCat)
-
-fisheries_recent_generousturf_1 <- fisheries_recent %>%
-  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
-
-fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
-
-fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
-fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
-fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
-fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
-
-fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
-  mutate(rightsbased = case_when(
-    turf == TRUE ~ "1",
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "0"
-    ))
-
-gdp_all <- read_excel("data/un_gdp_2016.xls")
-
-gdp <- gdp_all %>%
-  select(Country, gdp_center) %>%
-  filter( gdp_center != "NA")
-
-join_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))
-
-gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )
-
-gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
-gdp_rightsbased$rightsbased <- as.numeric(gdp_rightsbased$rightsbased)
-
-itq_turf_glm <- glm(formula = rightsbased ~ gdp_center + SpeciesCat, family = "binomial", data = gdp_rightsbased)
-itq_glm
-
-summary(itq_turf_glm)
-
-```
-
-##Diagnostics
-
-```{r}
-
-##run above chunk to get gdp_rightsbased df not the old csv file that is now archived in data folder
-
-diagnostics <- gdp_rightsbased %>%
-  mutate(management = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    turf == TRUE ~ "2",
-    itq == FALSE | iq == FALSE | ivq == FALSE | turf == FALSE ~ "0"
-    )) %>%
-  select(Country, gdp_center, SpeciesCat, management)
-
-#diagnostics wont run with non-numeric?
-diagnostics$SpeciesCat <- as.numeric(diagnostics$SpeciesCat)
-diagnostics$management <- as.numeric(diagnostics$management)
-
-#2= gdp; 4= turf; 5 = SpeciesCat; 23 = itq; 24= ivq; 25 = iq; 26= binary rights based
-pairs(diagnostics[2:4])
-
-#pearson's r correlations
-cor(diagnostics[2:4])
-
-#run chi square?
-
-```
-## MPA stuff

### 2019-01-07 Past_draft_figs/Regressions.Rmd
estimates catch from average 5 years and 10 years

--- 2018-12-21 lab_notebook.Rmd
@@
 ---
-title: "lab_notebook"
+title: "Regressions"
 author: "Juliette Verstaen"
-date: "November 2, 2018"
-output: html_document
+date: "12/21/2018"
+output: pdf_document
+toc: true
+toc_depth: 2
 ---
@@
 
-#Loading packages
-```{r}
+```{r, include = FALSE }
 
@@
   library(plyr)
-  library(data.table)
 })
-
 ```
 
-#converting projection csv into rds
-no longer need the code because have already used it to create the files
-```{r}
+##Logit regressions
 
-#Upside data
-#projection_data_csv <- read_csv("data/ProjectionData.csv")
-
-#saveRDS(projection_data_csv, "projection_data.rds")
-
-#WDPA_Nov2018.csv <- read_csv("data/WDPA_Nov2018.csv")
-
-#saveRDS(WDPA_Nov2018.csv, "WDPA_Nov2018.rds")
-
-```
-
-#Load Data
-```{r}
-
-#Corbet data: when countries began using RBFs
-countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
-
-#Upside data
-projection_data <- readRDS("data/projection_data.rds")
-
-#MPA data
-MPA <- readRDS("data/WDPA_Nov2018.rds")
-
-#RAMS
-load("data/DBdata-model_fits_included.RData")
-
-#number_species <- unique(stock$scientificname)
-#341 different species
-
-#cooperative data from "Conservation incentives and collective choices in cooperative fisheries" paper (Ovando et al 2013)
-jc_coop <- read_csv("data/clean_cooperatives_data.csv")
-
-#EDF turf data
-edf_turf <- read_excel("data/EDF_TURF_data.xlsx")
-
-```
-
-Important/Necessary Data
-tcbest.data #the best estimate of catch for that stock
-tbbest.dat # the best estimate of biomass for that stock
-divbpref # B/bmsy
-divupref.data # u/umsy
-
-Juliette Notes:
-
-Handy functions for updating data frames:
-match()
-separate()
-
-Useful Websites:
-https://uc-r.github.io/tidyr
-
-#RAM data wrangling
-```{r}
-ram <- timeseries_values_views %>%
-  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
-  add_column("RAM")
-
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
-
-#ram_2012 <- ram %>%
-#  filter(Year > "2012") 
-##this wont work because projection data has projected out past 2012. need to UPDATE
-
-#updated 
-#projection_ram <- bind_rows(list(projection_data, ram_2012))
-
-2012-1950
-#62
-2050- 2012
-#38
-162+38
-
-acheck <- filter(projection_ram, Year == "2013") %>%
-  select("IdOrig", "CommName", "Year", "Biomass")
-
-acheck_count <- unique(acheck$IdOrig)
-acheck_count
-#4714
-
-yearcheck <- unique(projection_data$Year)
-yearcheck
-#101 years starts 1950 end 2050
-
-join_project_ram <- join(projection_data, ram, by = c("CommName", "Year"), type = "full")
-
-projectramcheck <- filter(join_project_ram, IdOrig == "NA")
-#returns no rows with NA, could still be right if updated projected
-
-#Checking to see if better way to do join
-# end up with WAY to many rows, something is off
-#unite_projection_commname <- projection_data %>% 
-#  unite(name_year, CommName, Year, sep = "-")
-#unite_ram_commname <- ram %>% 
-#  unite (name_year, CommName, Year, sep = "-")
-#join_project_ram_2 <- join(unite_projection_commname, unite_projection_commname, by = "name_year", type = "left")
-
-match_project_ram <- match(projection_data, ram)
-
-```
-
-#Data Wrangling: Projection and Countries ITQ
-```{r}
-
-#seperate out IdOrig column for Projection Data
-separate_projection <- projection_ram %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
-
-head(separate_projection, 10)
-
-#reunite just the two parts we care about: agency and stock
-unite_projection <- separate_projection %>% unite(assess_id_short, agency, stock, sep = "-")
-
-#simplifying Countries ITQ with unique columns to prepare to merge
-countries_ITQ_simple <- select(countries_ITQ, "assess_id_short", "year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-#rename year to be capitalized to merge with projection data
-colnames(countries_ITQ_simple) <- c("assess_id_short", "Year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-ITQ_projection_merge <- merge(unite_projection, countries_ITQ_simple, by = c("assess_id_short", "Year"), all = TRUE)
-
-#cleaning it up
-ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, data_enterer, sep = "-")
-
-```
-
-Playing with Data
-
-#Total number of species with stocks
-#Number of stocks with ITQs implemented
-```{r}
-IdOrig <- unique(ITQ_projection$SciName)
-IdOrig
-#1228 species total
-
-ITQ_projection_implemented <- filter(ITQ_projection, programstart != "NA")
-
-IdOrig_implemented <- unique(ITQ_projection_implemented$SciName)
-IdOrig_implemented
-#80 species with ITQ implemented
-```
-
-#Graphs for fun
-
-ABARES_BGRDRSE
-implemented ITQs in 1992
-```{r}
-
-ABARES_BGRDRSE <- filter(ITQ_projection, IdOrig == "ABARES-BGRDRSE-1960-2011-CHING")
-
-graph_ABARES_BGRDRSE <-ggplot(ABARES_BGRDRSE, aes(x=Year, y=Biomass))+
-  geom_line(size=1)+
-  ggtitle("ABARES_BGRDRSE (Australia")+
-  geom_point()+
-  geom_line()+
-  labs(x="Year", y="Yearly total biomass")+
-  theme_classic()+
-  scale_x_continuous(expand=c(0,0))+
-  scale_y_continuous(expand=c(0,0))+
-  geom_vline(xintercept = 1992)+
-  theme(legend.title=element_blank())
-
-ggplotly(graph_ABARES_BGRDRSE)
-
-#figure out an if then statement for line?
-
-```
-
-ADFG-HERRTOGE
-never implemented ITQs
-```{r}
-ADFG_HERRTOGE <- filter(ITQ_projection, IdOrig == "ADFG-HERRTOG-1990-2010-HIVELY")
-
-graph_ADFG_HERRTOGE <-ggplot(ADFG_HERRTOGE, aes(x=Year, y=Biomass))+
-  geom_line(size=1)+
-  ggtitle("ADFG-HERRTOGE (USA)")+
-  geom_point()+
-  geom_line()+
-  labs(x="Year", y="Yearly total biomass")+
-  theme_classic()+
-  scale_x_continuous(expand=c(0,0))+
-  scale_y_continuous(expand=c(0,0))+
-  theme(legend.title=element_blank())
-
-ggplotly(graph_ADFG_HERRTOGE)
-
-#figure out an if then statement for line?
-```
-
-Important/Necessary Data
-tcbest.data #the best estimate of catch for that stock
-tbbest.dat # the best estimate of biomass for that stock
-divbpref # B/bmsy
-divupref.data # u/umsy
-
-Attempts at updating ITQ_projection with Rams
-#asked ana about this -> waiting to hear back
-```{r}
-
-##this doesn't work; gives you vector not updated data frame
-RAMS_ITQ_projection <- match(ITQ_projection_year$CommYear, ram_merge$CommYear)
-
-#what happens when i just merge the two?
-#test_merge <- merge(ITQ_projection_year, ram_merge, by = c("Name_Year"))
-
-```
-
-##edf turf data wrangling
-# waiting for data from Gina if its more comprehensive than the EDF one
-```{r}
-
-edf_turf_unite <- edf_turf %>% unite(SciName, genus, species, sep = " ")
-
-edf_turf_simple <- edf_turf_unite %>%
-  add_column("turf") %>%
-  select("country", "start_date", "SciName") %>%
-  gsub('\\bNA NA\\b', 'NA')
-
-colnames(edf_turf_simple) <- c("Country", "turfstart", "SciName")
-
-##want to merge the edf simple with ITQ/Projections but maybe wait for Gina to respond with her TURF data
-##in ITQ data says only one species of fish in japan has TURFs but not true
-
-edf_projection_itq <- merge(ITQ_projection, edf_turf_simple, by = c("Country", "SciName"))
-#only three species from the EDF data match with the species from the upside/projection data; all in Japan
-
-```
-
-Need to create new dataset (half upside half ITQ): Species, turf/itq, country,and then matching all the parameters with the species
-
-################
-################
-###############
-PART 2
-1) pull the ITQ, IVQ, IQ fisheries out of upside.
-2) pull the TURF fisheries from EDF.
-3) For each fishery, we want species, location, and ITQ vs. TURF.
-
-From updating_projection.R script file
-```{r}
-
-#Load Data
-#Upside data
-projection_data <- readRDS("data/projection_data.rds")
-
-#RAMS
-load("data/DBdata-model_fits_included.RData")
-
-#Corbet data: when countries began using RBFs
-countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
-
-#RAM Data Tiddying
-ram <- timeseries_values_views %>%
-  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
-  add_column("RAM")
-
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
-
-#Update Projection with RAM
-projection_updated <- join(projection_data, ram, by = c("CommName", "Year"), type = "full")
-
-#Merge Projection and ITQ
-#seperate out IdOrig column for Projection Data
-separate_projection <- projection_updated %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
-
-head(separate_projection, 10)
-
-#reunite just the two parts we care about: agency and stock
-unite_projection <- separate_projection %>% unite(assess_id_short, agency, stock, sep = "-")
-
-#simplifying Countries ITQ with unique columns to prepare to merge
-countries_ITQ_simple <- select(countries_ITQ, "assess_id_short", "year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-#rename year to be capitalized to merge with projection data
-colnames(countries_ITQ_simple) <- c("assess_id_short", "Year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-ITQ_projection_merge <- merge(unite_projection, countries_ITQ_simple, by = c("assess_id_short", "Year"), all = TRUE)
-
-#cleaning it up
-ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, data_enterer, sep = "-")
-
-#create RDS from dataframe
-saveRDS(ITQ_projection, "ITQ_projection.rds")
-
-#simplified projection data
-ITQ_projection_simple <- ITQ_projection %>%
-  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi", "yearitq", "itq_now","iq", "itq", "ivq", "turf", "programstart")
-
-#create RDS from dataframe
-#saveRDS(ITQ_projection_simple, "projection_updated.rds")
-
-#upside updated
-upside_2018_updated <- ITQ_projection %>%
-  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi")
-
-#create RDS from dataframe
-#saveRDS(upside_2018_updated, "upside_2018_updated")
-
-```
-
-#load data
-```{r}
-
-# create dataframe with 
-ITQ_projection <- readRDS("processed_data/ITQ_projection.rds")
-
-itq <- ITQ_projection %>%
-  select("Country", "SciName", "itq_now","iq", "itq", "ivq", "turf", "programstart")
-
-#Load EDF TURF data
-
-edf_turf <- read_excel("data/EDF_TURF_data.xlsx")
-
-#load in DiscoverTURFs data
-
-d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx")
-
-```
-
-#data wrangling
-```{r}
-
-edf_turf_simple <- select(edf_turf, "country", "start_date", "SciName", "turf")
-#create new column that says "turf" and TRUE or FALSE
-
-colnames(edf_turf_simple) <- c("Country", "programstart", "SciName", "turf")
-
-#combining edf turf data from upside data
-edf_projection_1 <- join(edf_turf_simple, itq, by = c("Country", "programstart", "SciName", "turf"), type = "full")
-
-#combine edf/upside with discover turfs
-all_turf_1 <- join(edf_projection_1, d_turfs, by = c("Country", "SciName", "turf"), type = "full")
-
-#change "blank" NAs to real NAs
-#all_turf_1[is.na(all_turf_1)] <- "NA"
-
-#rearrange columns
-all_turf_itq <- all_turf_1[, c(1,3,2,5,6,7,8,4)]
-
-#turning NAs from no ITQ data to FALSE
-#all_turf_2[all_turf_2 == 0] <- NA
-
-all_turf_itq$iq[is.na(all_turf_itq$iq)] <- FALSE
-
-all_turf_itq$itq[is.na(all_turf_itq$itq)] <- FALSE
-
-all_turf_itq$ivq[is.na(all_turf_itq$ivq)] <- FALSE
-
-all_turf_itq$itq_now[is.na(all_turf_itq$itq_now)] <- 0
-
-#create RDS from dataframe
-#saveRDS(all_turf_itq, "all_turf_itq.rds")
-#write.csv(all_turf_itq, file = "all_turf_itq.csv")
-
-```
-
-###################
-##################
-
-Part 3
-
-1) include only species that are either TURF, ITQ, IVQ, etc. (omit species that are FALSE for everything).
-2) Include each fishery only once (not multiple years).
-3) so then see how hard it is to collect other characteristics for each species (like growth rate or ISCAAP category).
-
-1 & 2
-```{r}
-
-#filter out all countries that don't have itqs or turfs
-true_turf_itq_1 <- all_turf_itq %>%
-  filter (iq == "TRUE" | itq == "TRUE" | ivq == "TRUE" | turf == "TRUE") %>%
-  filter( Country != "NA") %>%
-  select("Country", "SciName", "iq", "itq", "ivq", "turf")
-
-true_turf_itq <- unique(true_turf_itq_1 [ , 1:6])
-
-unique(true_turf_itq$Country)
-#33 countries
-#Chile, Fiji, Italy, Japan, Mexico, Papua New Guinea, Samoa, Solomon Islands, Spain, Sri Lanka, Sweden, Vanuatu, Vietnam, Australia, USA, Canada, Peru, Argentina, South Africa, New Zealand, American Samoa, Belize, Brazil, Ecuador, France, Greece, India, Netherlands, Nigeria, Philippines, St Lucia, United States, United Kingdom
-
-#chile_itq_turf <- filter(true_turf_itq, Country == "Chile")
-#unique(chile_itq_turf$SciName)
-# 67
-
-#fiji_itq_turf <- filter(only_turf_itq, Country == "Fiji")
-#unique(fiji_itq_turf$SciName)
-
-#test_duplicate <- unique(fiji_itq_turf[ , 1:8])
-
-```
-
-3
-ISCAAP
-```{r}
-
-iscaap_cat_1 <- upside_2018_updated %>%
-  select("SciName", "SpeciesCat")
-
-iscaap_cat <- unique(iscaap_cat_1 [ , 1:2])
-
-true_turf_itq_iscaap_1 <- merge(true_turf_itq, iscaap_cat, by = "SciName", all = T)
-
-true_turf_itq_iscaap <- true_turf_itq_iscaap_1 %>%
-  filter( itq != "NA" & ivq != "NA" & iq != "NA" & turf != "NA")
-
-true_turf_itq_iscaap[is.na(true_turf_itq_iscaap)] <- "NA"
-
-missing_speccat <- true_turf_itq_iscaap %>%
-  filter(SpeciesCat == "NA")
-
-#write.csv(true_turf_itq_iscaap, file = "true_turf_itq_iscaap.csv")
-
-determine_spec_cat <- as.vector(missing_speccat$SciName)
-determine_spec_cat
-
-```
-
-FishBase
-
-```{r}
-
-library("rfishbase")
-
-species <- as.vector(true_turf_itq_iscaap$SciName)
-species
-
-table_species <- species(species)
-
-growth <- popgrowth(species)
-
-#fishtest <- species_list(Genus = "Labroides")
-#fishtest
-#species(fishtest)
-#even running the practice online tutorial get this error :Error in curl::curl_fetch_memory(url, handle = handle) : Timeout was reached: Connection timed out after 10004 milliseconds
-
-#fishbase_test <- validate_names(species, fields = c("Species", ""))
-
-```
-
-FAO website with fisheries data is currently unavaliable. Updated by hand for now; read in below 
-```{r}
-species_rightsbased <- read_csv("data/species_rightsbased.csv")
-
-ISSCAAP_species <- select(species_rightsbased, SciName, SpeciesCat)
-#write.csv(ISSCAAP_species, file ="ISSCAAP_species.csv")
-```
--	used FAO 3-Alpha species codes (ASFIS) updated 2/2009
--	ones with no ISSCAPP # still are shellfish, snails, crabs, not species specific, common name, species in NA, or a family name with more than 1 #
-
-###########
-
-Part 4:
-For TURF/ITQ data, add GDP/capita for each country, also do ISCAAP categories. Combine all ITQ,IQ etc. Run logit of Prob(ITQ) = f(ISCAAP, GDP).
-```{r}
-
-species_rightsbased_binary <- read_csv("data/species_rightsbased_binary.csv")
-
-upside_2018_updated <- readRDS("/GitHub/global_fisheries_managment/processed_data/upside_2018_updated.rds")
-
-gdp_all <- read_csv("/GitHub/global_fisheries_managment/data/gpd.csv")
-
-```
-
-```{r}
-
-gdp <- filter(gdp_all, current_gdp != "NA")
-
-join_gdp_rightsbased <- join(gdp, species_rightsbased_binary, by = c("Country"), type = "full")
-
-gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )
-
-#write.csv(gdp_rightsbased, file = "gdp_rightsbased.csv")
-
-```
-
-```{r}
-
-##make sure that these stats are not effected by year 2012 onward not having info on itq or not. i think this data was not year specific so it should be fine? but look at the data
-
-gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
-
-itq_glm <- glm(formula = i_right ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
-itq_glm
-
-summary(itq_glm)
-
-#turf_glm <- glm(turf ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
-#turf_glm
-#summary(turf_glm)
-
-```
-
-Part 5:
-RAM only: F/Fmsy vs. B/Bmsy for all fisheries. Color ITQ differently.
-
-2. From upside sorts KOBE: ITQ versus non ITQ and the size of dot is the catch
-#this is all the data we have, make the same ones with only certain years and such
-
-```{r}
-
-ITQ_projection <- readRDS("processed_data//not_actively_used/ITQ_projection.rds")
-
-f_b_itq <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-#turf == TRUE ~ "2",
-#write.csv(f_b_itq, file = "f_b_itq.csv")
-#f_b_irights <- read_csv("data/f_b_irights.csv")
-#this was when i couldn't figure out how to do the if then statement in R
-
-#F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights, size = catch ))+
-
-# get data frame that was
-F_B_graph <- ggplot(data = f_b_itq, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(-1, 5)+
-  xlim(-.3, 3)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))
-
-#F_B_graph
-ggplotly(F_B_graph)
-
-```
-
-######
-MPA data wrangling
-######
-```{r}
-
-ISO_country_codes <- read_excel("data/ISO_country_codes.xlsx")
-MPA <- readRDS("data/WDPA_Nov2018.rds")
-
-mpa_simple <- MPA %>%
-  select("NAME", "PA_DEF", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS", "PARENT_ISO3") %>%
-  filter(MARINE != "0")
-
-colnames(mpa_simple) <- c("NAME", "PA_DEF", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS", "code")
-
-mpa_join <- join(mpa_simple, ISO_country_codes, by = c("code"), type = "full")
-
-mpa_updated <- mpa_join %>%
-  select("Country", "NAME", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS" ) %>%
-  filter(NAME != "NA" & DESIG_ENG != "NA" & DESIG_TYPE != "NA" & IUCN_CAT != "NA" & MARINE != "NA" & REP_M_AREA != "NA" & NO_TAKE != "NA" & STATUS != "NA")
-
-#write.csv(mpa_updated, file = "mpa_updated.csv")
-
-```
-
-PA_DEF: Allowed values: 1 (meets IUCN and/or CBD PA definition); 0 (does not meet IUCN and/or CBD PA definition (currently stored outside WDPA)).
-
-MARINE: Allowed values: 0 (100% Terrestrial PA), 1 (Coastal: marine and terrestrial PA), and 2 (100 % marine PA).
-
-#############
-############
-1.	From upside want to know the catch in ITQ versus non ITQ for most recent year
-
-- issues: unsure what year real data ends and projectio/modeling begins
-- pretty sure its 2016. there are thee fisheries with 2017 data in the updated RAMS dataset but more for 2016
-
-update recent years fisheries
-
-issue: the projection data updated with RAMs doens't have ITQ data associated with the countries
-- need a list of all the countries and whether or not they have ITQ in 2016 -> this can be pulled from Corbett's data. need to check if his data is from that year
-
-1.	From upside want to know the catch in ITQ versus non ITQ for most recent year
-corbet data only goes up until 2012 
-```{r}
-
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-f_b_itq_countries <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
-  mutate(rightsbased = case_when(
-    turf == TRUE ~ "2",
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-countries_itq_2012 <- f_b_itq_countries %>%
-  select (Country, rightsbased, Year, IdOrig, Catch) %>%
-  filter(Year == "2012")
-
-ITQ_projection_2016 <- ITQ_projection %>%
-  filter(Year == "2016") %>%
-  select(IdOrig, Country)
-
-itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012, by= c("IdOrig", "Country"), type= "full")
-
-itq_2016_rightsbasedTRUE <- filter(itq_2016_updated, rightsbased == "1")
-
-itq_2016_rightsbasedFALSE <- filter(itq_2016_updated, rightsbased == "0")
-
-itq_2016_rightsbasedTURF <- filter(itq_2016_updated, rightsbased == "2")
-
-sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
-#27,830,933
-sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
-#266,328,075
-
-sum(itq_2016_rightsbasedTURF$Catch, na.rm = TRUE)
-#1505000
-
-```
-
-updating projection datapast 2012  with the 2012 itq fisheries
-```{r}
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-f_b_itq_countries <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
-  mutate(rightsbased = case_when(
-    turf == TRUE ~ "2",
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-countries_itq_2012 <- f_b_itq_countries %>%
-  select (Country, rightsbased, Year, IdOrig, Catch) %>%
-  filter(Year == "2012")
-
-ITQ_projection_past2012 <- ITQ_projection %>%
-  filter(Year > 2012)
-
-ITQ_projection_past2012UPDATED <- join(ITQ_projection_past2012, countries_itq_2012, by = c("Country", "Year", "IdOrig"), type = "full" )
-
-ITQ_projection_pre2012 <- ITQ_projection %>%
-  filter(Year <= 2012)
-
-ITQ_projection_updated <- join(ITQ_projection_past2012UPDATED,ITQ_projection_pre2012, by = c("Country", "Year", "IdOrig"), type = "full")
-
-#saveRDS(ITQ_projection_updated, "ITQ_projection_updated.rds")
-
-ITQ_projection_updated <- readRDS("data/ITQ_projection_updated.rds")
-
-f_b_itq_updated <- ITQ_projection_updated %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-F_B_graph_updated <- ggplot(data = f_b_itq_updated, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(-1, 5)+
-  xlim(-.3, 3)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))
-
-#F_B_graph
-ggplotly(F_B_graph_updated)
-
-```
-
-###Did this chunck before figured out how to do if/then statements in r
-
-```{r}
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-#filter down the data to create a data set of countries that have ITQs so I can add that to the rams data. upside has this info but not the updated part
-
-#2012 is the most updated version of the upside data.
-used this to figure out which counties have ITQs and will make a data frame from that of a list of countires that have itqs and then update the final datafram (or inital rams dataframe)
-countries_with_ITQ <- ITQ_projection %>%
-  select (Country, itq, iq, ivq, Year, IdOrig) %>%
-  filter(Year == "2012")
-
-countries_with_ITQ_2 <- unique(countries_with_ITQ[, 1:6])
-countries_with_ITQ_3 <- filter(countries_with_ITQ_2, itq != "NA" | iq != "NA" | ivq != "NA")
-
-countries_with_ITQ_3$rightsbased <- 1
-countries_itq_2012 <- select(countries_with_ITQ_3, Country, IdOrig, rightsbased)
-
-#now need to create new column thats rights based fishereise 0 o for projection 2016
-
-ITQ_projection_2016 <- ITQ_projection %>%
-  filter(Year == "2016") %>%
-  select(IdOrig, Country, Catch)
-
-itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012, by= c("IdOrig", "Country"), type= "full")
-
-itq_2016_updated$rightsbased[is.na(itq_2016_updated$rightsbased)] <- 0
-
-#seperate rights based and not
-itq_2016_rightsbasedTRUE <- filter(itq_2016_updated, rightsbased == "1")
-
-itq_2016_rightsbasedFALSE <- filter(itq_2016_updated, rightsbased == "0")
-
-sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
-#27,830,933
-sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
-#266,328,075
-
-##units???
-
-```
-
-###Need to update the ITQ_projection rds file and the ITQ_projection_updated rds file (1st file is without applying ITQ info past 2012 and the second is)
-
-##ADD THIS INTO THE SCRIPT FOR UPDATING UPSIDE DATA
-```{r}
-ISSCAAP_species <- read_csv("data/ISSCAAP_species.csv")
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-ITQ_projection_isscaap_1 <- join(ISSCAAP_species,ITQ_projection, by = c("SciName", "SpeciesCat"), type = "full" )
-
-ITQ_projection_isscaap <- ITQ_projection_isscaap_1 %>%
-  filter(Country != "NA")
-
-```
-
-In the updated ITQ projection data there are lines of data that have 2012 with NA instead of TRUE/FALSE for itq.
-
-#data we have says that Mexico does not have ITQs?
-in 2012 only ones it says we have are Australia, USA, Canda, Japan, Peru, Argentina, South Africa, New Zealand
-
-Fixing upside data
-- take ITQ projection an filter it down to idorig, year, BvBmsy", "FvFmsy", "itq", "iq", "ivq"
-- filter out just ones with itqs, create a column thats rights based fisherse and make it one
-- filter out specifics of itq
-- merge/join that data with the countries_itq2012 with country, idorig, and rihgts based
-- make nas zero
--redo kobe plot with this data
-- also cut off at 5
-
-#this was from before figured out if then statement
-
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-itq_selected <- ITQ_projection %>%
-  select(IdOrig,Country, Year, BvBmsy, FvFmsy, itq, iq, ivq) %>%
-  filter(itq != "NA" | iq != "NA" | ivq != "NA")
-
-itq_selected$rightsbased <- 1
-
-itq_selected_2 <- select(itq_selected,Country, IdOrig, Year, rightsbased)
-
-itq_new_join <- join(itq_selected_2, countries_itq_2012, by = c(Country, IdOrig, Year), type = "full")
-
-##not using this anymore
-
-ITQ_projection <- readRDS("processed_data//not_actively_used/ITQ_projection.rds")
-
-countries_with_ITQ <- ITQ_projection %>%
-  select (Country, itq, iq, ivq, Year, IdOrig) %>%
-  filter(Year == "2012")
-
-countries_with_ITQ_2 <- unique(countries_with_ITQ[, 1:6])
-countries_with_ITQ_3 <- filter(countries_with_ITQ_2, itq != "NA" | iq != "NA" | ivq != "NA")
-
-countries_with_ITQ_3$rightsbased <- 1
-countries_itq_2012 <- select(countries_with_ITQ_3, Country, IdOrig, rightsbased)
-
-##need to update projection data
-
-f_b_itq <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA")
-
-ISSCAAP Codes and the non-species specific codes
-```{r}
-
-meta_isscaap_codes_1 <- join(isscaap_codes, ISSCAAP_species, by = c("SciName", "SpeciesCat"), type = "full")
-
-meta_isscaap_codes <- unique( meta_isscaap_codes_1[ , 1:2 ] )
-write_csv(meta_isscaap_codes, "meta_isscaap_codes.csv")
-```
-
-12/18/2018
-Using the newly updated upside/ITQ and filtering out only the most recent date for each fishery
-- make a df of these that have ITQs and those that don't -> apply to OG upside/ITQ data so that more recent years can have ITQ data
-- take this new df and filter out the most recent years with ITQs and KOBE plot. also do catches
-
-```{r}
-
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-upside_2016 <- ITQ_projection %>%
-  filter(Year <= "2016") %>%
-  unite(id_country, IdOrig, Country, sep = "-")
-
-upside_recent <- setDT(upside_2016)[,.SD[which.max(Year)],keyby=id_country]
-
-upside_allfisheriesITQ <- upside_recent %>%
-  select (id_country, itq, iq, ivq, Year, turf) %>%
-  filter(itq != "NA" & iq != "NA" & ivq != "NA" )
-
-```
-
-#Pulling out information about ITQs/TURFs in Corbette Data to apply to upside data
-```{r}
-
-Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
-
-#new dataframw with just most recent year of data for each fishery
-corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
-
-#filter out the fisheries with no data on itqs or turfs
-corbette_fisheries <- corbette_recent %>%
-  select(assess_id_short, year, speciescat, iq, itq, ivq, coop, turf)%>%
-  filter(itq != "NA" & iq != "NA" & ivq != "NA")%>%
-  filter(turf != "NA" )
-
-#new data frame with just data on fisheries with itqs
-fisheries_with_itq <- corbette_fisheries %>%
-   filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" | turf == "TRUE" )
-
-```
-
-reupdating upside data with new ITQ list
-
-```{r}
-#Load Data
-#Upside data
-projection_data <- readRDS("data/projection_data.rds")
-
-#RAMS
-load("data/DBdata-model_fits_included.RData")
-
-#RAM Data Tiddying
-ram <- timeseries_values_views %>%
-  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
-  add_column("RAM")
-
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
-
-#Update Projection with RAM
-projection_updated <- join(ram, projection_data, by = c("CommName", "Year"), type = "full")
-##note: RAM data has some fisheries not in the projection data, thus adding new fisheries to the upside projection data
-
-#separate and unit functions to create a shorter version of the stock assessment ID to merge with corbette ITQ/TURF data later
-separate_projection <- projection_updated%>% 
-  separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
-
-unite_projection <- separate_projection %>% 
-  unite(assess_id_short, agency, stock, sep = "-")
-
-colnames(fisheries_with_itq) <- c("assess_id_short", "Year","SpeciesCat" , "iq", "itq", "ivq", "coop", "turf")
-
-#merge corbette's data on ITQ/Turf implemented or not for each fishery
-fishery_itq_simple <- fisheries_with_itq %>%
-  select(assess_id_short,iq, itq, ivq, turf )
-
-ITQ_projection_merge <- merge(unite_projection, fisheries_with_itq, by = c("assess_id_short"), all = TRUE)
-
-#filter out data post 2016 because we know that those are projected/modeled data not recorded
-recent_pre2016 <- ITQ_projection_merge %>%
-  filter(Year.x <= "2016")
-
-#keep only info on most recent year for each fishery  
-fisheries_recent_1 <- setDT(recent_pre2016)[,.SD[which.max(Year.x)],keyby=assess_id_short]
-
-#select the columns we are interested in
-fisheries_recent <- fisheries_recent_1 %>%
-  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq, turf)
-
-#write dataframe to csv file
-#fisheries_recent <- write.csv(fisheries_recent, file = "fisheries_recent.csv")
-
-```
-
-##KOBE Plots with only most recent year of fisheries
-RAM only
-No data: ITQ = FALSE
-
-```{r}
-
-#read in data: this is updated projection data (updated using RAMs) and Corbett's ITQ/Turf data applied to each fishery. only data for most recent year for each fishery is represented.
-
-fisheries_recent <- read_csv("data/fisheries_recent.csv")
-
-#assuming that when no data is avaliable on the fishery inregardes to ITQ or Turfs that means there are none
-fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
-fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
-fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
-fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
-
-#only looking at fisheries data that come from RAMS database
-# creating new column called "rightsbased" where 1 = ITQ and 0 = No ITQ
-fisheries_KOBE_ram <- fisheries_recent %>%
-  filter(Dbase == "RAM") %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-#graphing logistics
-fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "0"]<- "No ITQ"
-fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "1"]<- "ITQ"
-
-F_B_graph_RAM <- ggplot(data = fisheries_KOBE_ram, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(0, 2.5)+
-  xlim(0, 2.5)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))+
-  ggtitle("KOBE Plot: RAM only Fisheries")
-
-#F_B_graph
-ggplotly(F_B_graph_RAM)
-
-```
-
-##KOBE Plots with only most recent year of fisheries
-RAM only
-No data: ITQ = FALSE
-```{r}
-
-#read in data: this is updated projection data (updated using RAMs) and Corbett's ITQ/Turf data applied to each fishery. only data for most recent year for each fishery is represented.
-fisheries_recent <- read_csv("data/fisheries_recent.csv")
-
-#assuming that when no data is avaliable on the fishery inregardes to ITQ or Turfs that means there are none
-fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
-fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
-fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
-fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
-
-fisheries_KOBE <- fisheries_recent %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "0"]<- "No ITQ"
-fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "1"]<- "ITQ"
-
-#graphing logistics
-F_B_graph <- ggplot(data = fisheries_KOBE, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(0, 2.5)+
-  xlim(0, 2.5)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))+
-  ggtitle("KOBE Plot:  All Fisheries")
-
-#F_B_graph
-ggplotly(F_B_graph)
-
-```
-
-## adding turf information to upside projection(ie: fisheries_recent)
-```{r}
-
-#load in data for turf/itq only projection
-turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
-
-turf_only <- turf_itq_isscaap %>%
-  select(SciName, Country, turf)
-
-fisheries_recent_generousturf_1 <- select(fisheries_recent, Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
-
-#merge the most recent data on each fishery with turf data
-fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turf_only, by = c("Country", "SciName")) #, all = "TRUE")
-
-#assuming that when no data is present for itqs/turf that means there are none
-fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
-fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
-fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
-fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
-
-fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
-  mutate(rightsbased = case_when(
-    turf == TRUE ~ "2",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1"
-    ))
-
-#create dfs for turf, itq, and no itq fisheries to calculate the sum of each
-#NOTE to rememeber: the data from these fisheries are the most recent numbers we have. they are not all in the same year 
-turfs <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
-itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "1")
-no_itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "0")
-
-sum(turfs$Catch, na.rm = TRUE)
-
-sum(itq$Catch, na.rm = TRUE)
-
-sum(no_itq$Catch, na.rm = TRUE)
-
-```
-
-turf only = 413 rows
-fisheries recent = 5294
-
-5643 actual rows
-5707 when manually added added
-- this means 64 species were matched with existing species in database
-- when separated out all by species it was worse
-
-- separate remaining by genus?
-
-12/20/2018
 new UN GDP data, 2016 only
@@
 Rerun Regressions
-###itq or turf: probablity of itq = f(ISSCAPP and GDP)
-*regression converges*
+
+###1. itq or turf: probablity of itq = f(ISSCAPP and GDP)
+
+####wrangling
 ```{r}
@@
 
-join_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))
+merge_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))
 
-gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )
+gdp_rightsbased <- filter(merge_gdp_rightsbased, SpeciesCat != "NA" )
+
+```
+
+### Regression 1
+```{r}
 
@@
 
-itq_glm <- glm(formula = rightsbased ~ gdp_center + SpeciesCat, family = "binomial", data = gdp_rightsbased)
+itq_glm <- glm(formula = rightsbased ~ 1, family = "binomial", data = gdp_rightsbased)
 itq_glm
@@
 summary(itq_glm)
-
 ```
 
-Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
+###2. Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
 
+####Wrangling
 ```{r}
+
 fisheries_recent <- read_csv("data/fisheries_recent.csv")
@@
 
+```
+
+####Regression 2
+```{r}
+
 gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
@@
 ```
-## MPA stuff

### 2019-01-07 Past_draft_figs/lab_notebook_2.Rmd
estimates catch from average 5 years and 10 years

--- 2018-12-21 lab_notebook.Rmd
@@
   library(plyr)
-  library(data.table)
 })
-
-```
-
-#converting projection csv into rds
-no longer need the code because have already used it to create the files
-```{r}
-
-#Upside data
-#projection_data_csv <- read_csv("data/ProjectionData.csv")
-
-#saveRDS(projection_data_csv, "projection_data.rds")
-
-#WDPA_Nov2018.csv <- read_csv("data/WDPA_Nov2018.csv")
-
-#saveRDS(WDPA_Nov2018.csv, "WDPA_Nov2018.rds")
 
@@
 
-Important/Necessary Data
-tcbest.data #the best estimate of catch for that stock
-tbbest.dat # the best estimate of biomass for that stock
-divbpref # B/bmsy
-divupref.data # u/umsy
-
-Juliette Notes:
-
-Handy functions for updating data frames:
-match()
-separate()
-
-Useful Websites:
-https://uc-r.github.io/tidyr
-
-#RAM data wrangling
-```{r}
-ram <- timeseries_values_views %>%
-  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
-  add_column("RAM")
-
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
-
-#ram_2012 <- ram %>%
-#  filter(Year > "2012") 
-##this wont work because projection data has projected out past 2012. need to UPDATE
-
-#updated 
-#projection_ram <- bind_rows(list(projection_data, ram_2012))
-
-2012-1950
-#62
-2050- 2012
-#38
-162+38
-
-acheck <- filter(projection_ram, Year == "2013") %>%
-  select("IdOrig", "CommName", "Year", "Biomass")
-
-acheck_count <- unique(acheck$IdOrig)
-acheck_count
-#4714
-
-yearcheck <- unique(projection_data$Year)
-yearcheck
-#101 years starts 1950 end 2050
-
-join_project_ram <- join(projection_data, ram, by = c("CommName", "Year"), type = "full")
-
-projectramcheck <- filter(join_project_ram, IdOrig == "NA")
-#returns no rows with NA, could still be right if updated projected
-
-#Checking to see if better way to do join
-# end up with WAY to many rows, something is off
-#unite_projection_commname <- projection_data %>% 
-#  unite(name_year, CommName, Year, sep = "-")
-#unite_ram_commname <- ram %>% 
-#  unite (name_year, CommName, Year, sep = "-")
-#join_project_ram_2 <- join(unite_projection_commname, unite_projection_commname, by = "name_year", type = "left")
-
-match_project_ram <- match(projection_data, ram)
-
-```
-
-#Data Wrangling: Projection and Countries ITQ
 ```{r}
 
-#seperate out IdOrig column for Projection Data
-separate_projection <- projection_ram %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
-
-head(separate_projection, 10)
-
-#reunite just the two parts we care about: agency and stock
-unite_projection <- separate_projection %>% unite(assess_id_short, agency, stock, sep = "-")
-
-#simplifying Countries ITQ with unique columns to prepare to merge
-countries_ITQ_simple <- select(countries_ITQ, "assess_id_short", "year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-#rename year to be capitalized to merge with projection data
-colnames(countries_ITQ_simple) <- c("assess_id_short", "Year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")
-
-ITQ_projection_merge <- merge(unite_projection, countries_ITQ_simple, by = c("assess_id_short", "Year"), all = TRUE)
-
-#cleaning it up
-ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, data_enterer, sep = "-")
-
-```
-
-Playing with Data
-
-#Total number of species with stocks
-#Number of stocks with ITQs implemented
-```{r}
-IdOrig <- unique(ITQ_projection$SciName)
-IdOrig
-#1228 species total
-
-ITQ_projection_implemented <- filter(ITQ_projection, programstart != "NA")
-
-IdOrig_implemented <- unique(ITQ_projection_implemented$SciName)
-IdOrig_implemented
-#80 species with ITQ implemented
-```
-
-#Graphs for fun
-
-ABARES_BGRDRSE
-implemented ITQs in 1992
-```{r}
-
-ABARES_BGRDRSE <- filter(ITQ_projection, IdOrig == "ABARES-BGRDRSE-1960-2011-CHING")
-
-graph_ABARES_BGRDRSE <-ggplot(ABARES_BGRDRSE, aes(x=Year, y=Biomass))+
-  geom_line(size=1)+
-  ggtitle("ABARES_BGRDRSE (Australia")+
-  geom_point()+
-  geom_line()+
-  labs(x="Year", y="Yearly total biomass")+
-  theme_classic()+
-  scale_x_continuous(expand=c(0,0))+
-  scale_y_continuous(expand=c(0,0))+
-  geom_vline(xintercept = 1992)+
-  theme(legend.title=element_blank())
-
-ggplotly(graph_ABARES_BGRDRSE)
-
-#figure out an if then statement for line?
-
-```
-
-ADFG-HERRTOGE
-never implemented ITQs
-```{r}
-ADFG_HERRTOGE <- filter(ITQ_projection, IdOrig == "ADFG-HERRTOG-1990-2010-HIVELY")
-
-graph_ADFG_HERRTOGE <-ggplot(ADFG_HERRTOGE, aes(x=Year, y=Biomass))+
-  geom_line(size=1)+
-  ggtitle("ADFG-HERRTOGE (USA)")+
-  geom_point()+
-  geom_line()+
-  labs(x="Year", y="Yearly total biomass")+
-  theme_classic()+
-  scale_x_continuous(expand=c(0,0))+
-  scale_y_continuous(expand=c(0,0))+
-  theme(legend.title=element_blank())
-
-ggplotly(graph_ADFG_HERRTOGE)
-
-#figure out an if then statement for line?
-```
-
-Important/Necessary Data
-tcbest.data #the best estimate of catch for that stock
-tbbest.dat # the best estimate of biomass for that stock
-divbpref # B/bmsy
-divupref.data # u/umsy
-
-Attempts at updating ITQ_projection with Rams
-#asked ana about this -> waiting to hear back
-```{r}
-
-##this doesn't work; gives you vector not updated data frame
-RAMS_ITQ_projection <- match(ITQ_projection_year$CommYear, ram_merge$CommYear)
-
-#what happens when i just merge the two?
-#test_merge <- merge(ITQ_projection_year, ram_merge, by = c("Name_Year"))
-
-```
-
-##edf turf data wrangling
-# waiting for data from Gina if its more comprehensive than the EDF one
-```{r}
-
-edf_turf_unite <- edf_turf %>% unite(SciName, genus, species, sep = " ")
-
-edf_turf_simple <- edf_turf_unite %>%
-  add_column("turf") %>%
-  select("country", "start_date", "SciName") %>%
-  gsub('\\bNA NA\\b', 'NA')
-
-colnames(edf_turf_simple) <- c("Country", "turfstart", "SciName")
-
-##want to merge the edf simple with ITQ/Projections but maybe wait for Gina to respond with her TURF data
-##in ITQ data says only one species of fish in japan has TURFs but not true
-
-edf_projection_itq <- merge(ITQ_projection, edf_turf_simple, by = c("Country", "SciName"))
-#only three species from the EDF data match with the species from the upside/projection data; all in Japan
-
-```
-
-Need to create new dataset (half upside half ITQ): Species, turf/itq, country,and then matching all the parameters with the species
-
-################
-################
-###############
-PART 2
-1) pull the ITQ, IVQ, IQ fisheries out of upside.
-2) pull the TURF fisheries from EDF.
-3) For each fishery, we want species, location, and ITQ vs. TURF.
-
-From updating_projection.R script file
-```{r}
+#Load Packages
+suppressPackageStartupMessages({
+  library(tidyverse)
+  library(tidyr)
+  library(here)
+  library(ggplot2)
+  library(dplyr)
+  library(readxl)
+  library(devtools)
+  library(plotly)
+  library(base)
+  library(rio)
+  library(plyr)
+})
 
@@
 
-#create RDS from dataframe
-saveRDS(ITQ_projection, "ITQ_projection.rds")
+########
+ITQ_projection_merge_different <- join(unite_projection, countries_ITQ_simple, by = c("assess_id_short", "Year"), type= "full")
 
-#simplified projection data
-ITQ_projection_simple <- ITQ_projection %>%
-  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi", "yearitq", "itq_now","iq", "itq", "ivq", "turf", "programstart")
+ITQ_projection_different <- ITQ_projection_merge_different %>% unite(IdOrig, assess_id_short, t0, tf, data_enterer, sep = "-")
 
-#create RDS from dataframe
-#saveRDS(ITQ_projection_simple, "projection_updated.rds")
-
-#upside updated
-upside_2018_updated <- ITQ_projection %>%
-  select("Country", "Year", "CommName", "SciName", "SpeciesCat", "CatchShare", "Catch", "Biomass", "BvBmsy", "FvFmsy","MSY", "Price", "g", "k", "c", "phi")
-
-#create RDS from dataframe
-#saveRDS(upside_2018_updated, "upside_2018_updated")
+unique(ITQ_projection$itq)
+unique(ITQ_projection_different$itq)
 
 ```
-
-#load data
-```{r}
-
-# create dataframe with 
-ITQ_projection <- readRDS("processed_data/ITQ_projection.rds")
-
-itq <- ITQ_projection %>%
-  select("Country", "SciName", "itq_now","iq", "itq", "ivq", "turf", "programstart")
-
-#Load EDF TURF data
-
-edf_turf <- read_excel("data/EDF_TURF_data.xlsx")
-
-#load in DiscoverTURFs data
-
-d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx")
-
-```
-
-#data wrangling
-```{r}
-
-edf_turf_simple <- select(edf_turf, "country", "start_date", "SciName", "turf")
-#create new column that says "turf" and TRUE or FALSE
-
-colnames(edf_turf_simple) <- c("Country", "programstart", "SciName", "turf")
-
-#combining edf turf data from upside data
-edf_projection_1 <- join(edf_turf_simple, itq, by = c("Country", "programstart", "SciName", "turf"), type = "full")
-
-#combine edf/upside with discover turfs
-all_turf_1 <- join(edf_projection_1, d_turfs, by = c("Country", "SciName", "turf"), type = "full")
-
-#change "blank" NAs to real NAs
-#all_turf_1[is.na(all_turf_1)] <- "NA"
-
-#rearrange columns
-all_turf_itq <- all_turf_1[, c(1,3,2,5,6,7,8,4)]
-
-#turning NAs from no ITQ data to FALSE
-#all_turf_2[all_turf_2 == 0] <- NA
-
-all_turf_itq$iq[is.na(all_turf_itq$iq)] <- FALSE
-
-all_turf_itq$itq[is.na(all_turf_itq$itq)] <- FALSE
-
-all_turf_itq$ivq[is.na(all_turf_itq$ivq)] <- FALSE
-
-all_turf_itq$itq_now[is.na(all_turf_itq$itq_now)] <- 0
-
-#create RDS from dataframe
-#saveRDS(all_turf_itq, "all_turf_itq.rds")
-#write.csv(all_turf_itq, file = "all_turf_itq.csv")
-
-```
-
-###################
-##################
-
-Part 3
-
-1) include only species that are either TURF, ITQ, IVQ, etc. (omit species that are FALSE for everything).
-2) Include each fishery only once (not multiple years).
-3) so then see how hard it is to collect other characteristics for each species (like growth rate or ISCAAP category).
-
-1 & 2
-```{r}
-
-#filter out all countries that don't have itqs or turfs
-true_turf_itq_1 <- all_turf_itq %>%
-  filter (iq == "TRUE" | itq == "TRUE" | ivq == "TRUE" | turf == "TRUE") %>%
-  filter( Country != "NA") %>%
-  select("Country", "SciName", "iq", "itq", "ivq", "turf")
-
-true_turf_itq <- unique(true_turf_itq_1 [ , 1:6])
-
-unique(true_turf_itq$Country)
-#33 countries
-#Chile, Fiji, Italy, Japan, Mexico, Papua New Guinea, Samoa, Solomon Islands, Spain, Sri Lanka, Sweden, Vanuatu, Vietnam, Australia, USA, Canada, Peru, Argentina, South Africa, New Zealand, American Samoa, Belize, Brazil, Ecuador, France, Greece, India, Netherlands, Nigeria, Philippines, St Lucia, United States, United Kingdom
-
-#chile_itq_turf <- filter(true_turf_itq, Country == "Chile")
-#unique(chile_itq_turf$SciName)
-# 67
-
-#fiji_itq_turf <- filter(only_turf_itq, Country == "Fiji")
-#unique(fiji_itq_turf$SciName)
-
-#test_duplicate <- unique(fiji_itq_turf[ , 1:8])
-
-```
-
-3
-ISCAAP
-```{r}
-
-iscaap_cat_1 <- upside_2018_updated %>%
-  select("SciName", "SpeciesCat")
-
-iscaap_cat <- unique(iscaap_cat_1 [ , 1:2])
-
-true_turf_itq_iscaap_1 <- merge(true_turf_itq, iscaap_cat, by = "SciName", all = T)
-
-true_turf_itq_iscaap <- true_turf_itq_iscaap_1 %>%
-  filter( itq != "NA" & ivq != "NA" & iq != "NA" & turf != "NA")
-
-true_turf_itq_iscaap[is.na(true_turf_itq_iscaap)] <- "NA"
-
-missing_speccat <- true_turf_itq_iscaap %>%
-  filter(SpeciesCat == "NA")
-
-#write.csv(true_turf_itq_iscaap, file = "true_turf_itq_iscaap.csv")
-
-determine_spec_cat <- as.vector(missing_speccat$SciName)
-determine_spec_cat
-
-```
-
-FishBase
-
-```{r}
-
-library("rfishbase")
-
-species <- as.vector(true_turf_itq_iscaap$SciName)
-species
-
-table_species <- species(species)
-
-growth <- popgrowth(species)
-
-#fishtest <- species_list(Genus = "Labroides")
-#fishtest
-#species(fishtest)
-#even running the practice online tutorial get this error :Error in curl::curl_fetch_memory(url, handle = handle) : Timeout was reached: Connection timed out after 10004 milliseconds
-
-#fishbase_test <- validate_names(species, fields = c("Species", ""))
-
-```
-
-FAO website with fisheries data is currently unavaliable. Updated by hand for now; read in below 
-```{r}
-species_rightsbased <- read_csv("data/species_rightsbased.csv")
-
-ISSCAAP_species <- select(species_rightsbased, SciName, SpeciesCat)
-#write.csv(ISSCAAP_species, file ="ISSCAAP_species.csv")
-```
--	used FAO 3-Alpha species codes (ASFIS) updated 2/2009
--	ones with no ISSCAPP # still are shellfish, snails, crabs, not species specific, common name, species in NA, or a family name with more than 1 #
-
-###########
-
-Part 4:
-For TURF/ITQ data, add GDP/capita for each country, also do ISCAAP categories. Combine all ITQ,IQ etc. Run logit of Prob(ITQ) = f(ISCAAP, GDP).
-```{r}
-
-species_rightsbased_binary <- read_csv("data/species_rightsbased_binary.csv")
-
-upside_2018_updated <- readRDS("/GitHub/global_fisheries_managment/processed_data/upside_2018_updated.rds")
-
-gdp_all <- read_csv("/GitHub/global_fisheries_managment/data/gpd.csv")
-
-```
-
-```{r}
-
-gdp <- filter(gdp_all, current_gdp != "NA")
-
-join_gdp_rightsbased <- join(gdp, species_rightsbased_binary, by = c("Country"), type = "full")
-
-gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )
-
-#write.csv(gdp_rightsbased, file = "gdp_rightsbased.csv")
-
-```
-
-```{r}
-
-##make sure that these stats are not effected by year 2012 onward not having info on itq or not. i think this data was not year specific so it should be fine? but look at the data
-
-gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
-
-itq_glm <- glm(formula = i_right ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
-itq_glm
-
-summary(itq_glm)
-
-#turf_glm <- glm(turf ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
-#turf_glm
-#summary(turf_glm)
-
-```
-
-Part 5:
-RAM only: F/Fmsy vs. B/Bmsy for all fisheries. Color ITQ differently.
-
-2. From upside sorts KOBE: ITQ versus non ITQ and the size of dot is the catch
-#this is all the data we have, make the same ones with only certain years and such
-
-```{r}
-
-ITQ_projection <- readRDS("processed_data//not_actively_used/ITQ_projection.rds")
-
-f_b_itq <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-#turf == TRUE ~ "2",
-#write.csv(f_b_itq, file = "f_b_itq.csv")
-#f_b_irights <- read_csv("data/f_b_irights.csv")
-#this was when i couldn't figure out how to do the if then statement in R
-
-#F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights, size = catch ))+
-
-# get data frame that was
-F_B_graph <- ggplot(data = f_b_itq, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(-1, 5)+
-  xlim(-.3, 3)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))
-
-#F_B_graph
-ggplotly(F_B_graph)
-
-```
-
-######
-MPA data wrangling
-######
-```{r}
-
-ISO_country_codes <- read_excel("data/ISO_country_codes.xlsx")
-MPA <- readRDS("data/WDPA_Nov2018.rds")
-
-mpa_simple <- MPA %>%
-  select("NAME", "PA_DEF", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS", "PARENT_ISO3") %>%
-  filter(MARINE != "0")
-
-colnames(mpa_simple) <- c("NAME", "PA_DEF", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS", "code")
-
-mpa_join <- join(mpa_simple, ISO_country_codes, by = c("code"), type = "full")
-
-mpa_updated <- mpa_join %>%
-  select("Country", "NAME", "DESIG_ENG", "DESIG_TYPE", "IUCN_CAT", "MARINE", "REP_M_AREA", "NO_TAKE", "STATUS" ) %>%
-  filter(NAME != "NA" & DESIG_ENG != "NA" & DESIG_TYPE != "NA" & IUCN_CAT != "NA" & MARINE != "NA" & REP_M_AREA != "NA" & NO_TAKE != "NA" & STATUS != "NA")
-
-#write.csv(mpa_updated, file = "mpa_updated.csv")
-
-```
-
-PA_DEF: Allowed values: 1 (meets IUCN and/or CBD PA definition); 0 (does not meet IUCN and/or CBD PA definition (currently stored outside WDPA)).
-
-MARINE: Allowed values: 0 (100% Terrestrial PA), 1 (Coastal: marine and terrestrial PA), and 2 (100 % marine PA).
-
-#############
-############
-1.	From upside want to know the catch in ITQ versus non ITQ for most recent year
-
-- issues: unsure what year real data ends and projectio/modeling begins
-- pretty sure its 2016. there are thee fisheries with 2017 data in the updated RAMS dataset but more for 2016
-
-update recent years fisheries
-
-issue: the projection data updated with RAMs doens't have ITQ data associated with the countries
-- need a list of all the countries and whether or not they have ITQ in 2016 -> this can be pulled from Corbett's data. need to check if his data is from that year
-
-1.	From upside want to know the catch in ITQ versus non ITQ for most recent year
-corbet data only goes up until 2012 
-```{r}
-
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-f_b_itq_countries <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
-  mutate(rightsbased = case_when(
-    turf == TRUE ~ "2",
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-countries_itq_2012 <- f_b_itq_countries %>%
-  select (Country, rightsbased, Year, IdOrig, Catch) %>%
-  filter(Year == "2012")
-
-ITQ_projection_2016 <- ITQ_projection %>%
-  filter(Year == "2016") %>%
-  select(IdOrig, Country)
-
-itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012, by= c("IdOrig", "Country"), type= "full")
-
-itq_2016_rightsbasedTRUE <- filter(itq_2016_updated, rightsbased == "1")
-
-itq_2016_rightsbasedFALSE <- filter(itq_2016_updated, rightsbased == "0")
-
-itq_2016_rightsbasedTURF <- filter(itq_2016_updated, rightsbased == "2")
-
-sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
-#27,830,933
-sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
-#266,328,075
-
-sum(itq_2016_rightsbasedTURF$Catch, na.rm = TRUE)
-#1505000
-
-```
-
-updating projection datapast 2012  with the 2012 itq fisheries
-```{r}
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-f_b_itq_countries <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
-  mutate(rightsbased = case_when(
-    turf == TRUE ~ "2",
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-countries_itq_2012 <- f_b_itq_countries %>%
-  select (Country, rightsbased, Year, IdOrig, Catch) %>%
-  filter(Year == "2012")
-
-ITQ_projection_past2012 <- ITQ_projection %>%
-  filter(Year > 2012)
-
-ITQ_projection_past2012UPDATED <- join(ITQ_projection_past2012, countries_itq_2012, by = c("Country", "Year", "IdOrig"), type = "full" )
-
-ITQ_projection_pre2012 <- ITQ_projection %>%
-  filter(Year <= 2012)
-
-ITQ_projection_updated <- join(ITQ_projection_past2012UPDATED,ITQ_projection_pre2012, by = c("Country", "Year", "IdOrig"), type = "full")
-
-#saveRDS(ITQ_projection_updated, "ITQ_projection_updated.rds")
-
-ITQ_projection_updated <- readRDS("data/ITQ_projection_updated.rds")
-
-f_b_itq_updated <- ITQ_projection_updated %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-F_B_graph_updated <- ggplot(data = f_b_itq_updated, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(-1, 5)+
-  xlim(-.3, 3)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))
-
-#F_B_graph
-ggplotly(F_B_graph_updated)
-
-```
-
-###Did this chunck before figured out how to do if/then statements in r
-
-```{r}
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-#filter down the data to create a data set of countries that have ITQs so I can add that to the rams data. upside has this info but not the updated part
-
-#2012 is the most updated version of the upside data.
-used this to figure out which counties have ITQs and will make a data frame from that of a list of countires that have itqs and then update the final datafram (or inital rams dataframe)
-countries_with_ITQ <- ITQ_projection %>%
-  select (Country, itq, iq, ivq, Year, IdOrig) %>%
-  filter(Year == "2012")
-
-countries_with_ITQ_2 <- unique(countries_with_ITQ[, 1:6])
-countries_with_ITQ_3 <- filter(countries_with_ITQ_2, itq != "NA" | iq != "NA" | ivq != "NA")
-
-countries_with_ITQ_3$rightsbased <- 1
-countries_itq_2012 <- select(countries_with_ITQ_3, Country, IdOrig, rightsbased)
-
-#now need to create new column thats rights based fishereise 0 o for projection 2016
-
-ITQ_projection_2016 <- ITQ_projection %>%
-  filter(Year == "2016") %>%
-  select(IdOrig, Country, Catch)
-
-itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012, by= c("IdOrig", "Country"), type= "full")
-
-itq_2016_updated$rightsbased[is.na(itq_2016_updated$rightsbased)] <- 0
-
-#seperate rights based and not
-itq_2016_rightsbasedTRUE <- filter(itq_2016_updated, rightsbased == "1")
-
-itq_2016_rightsbasedFALSE <- filter(itq_2016_updated, rightsbased == "0")
-
-sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
-#27,830,933
-sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
-#266,328,075
-
-##units???
-
-```
-
-###Need to update the ITQ_projection rds file and the ITQ_projection_updated rds file (1st file is without applying ITQ info past 2012 and the second is)
-
-##ADD THIS INTO THE SCRIPT FOR UPDATING UPSIDE DATA
-```{r}
-ISSCAAP_species <- read_csv("data/ISSCAAP_species.csv")
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-ITQ_projection_isscaap_1 <- join(ISSCAAP_species,ITQ_projection, by = c("SciName", "SpeciesCat"), type = "full" )
-
-ITQ_projection_isscaap <- ITQ_projection_isscaap_1 %>%
-  filter(Country != "NA")
-
-```
-
-In the updated ITQ projection data there are lines of data that have 2012 with NA instead of TRUE/FALSE for itq.
-
-#data we have says that Mexico does not have ITQs?
-in 2012 only ones it says we have are Australia, USA, Canda, Japan, Peru, Argentina, South Africa, New Zealand
-
-Fixing upside data
-- take ITQ projection an filter it down to idorig, year, BvBmsy", "FvFmsy", "itq", "iq", "ivq"
-- filter out just ones with itqs, create a column thats rights based fisherse and make it one
-- filter out specifics of itq
-- merge/join that data with the countries_itq2012 with country, idorig, and rihgts based
-- make nas zero
--redo kobe plot with this data
-- also cut off at 5
-
-#this was from before figured out if then statement
-
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-itq_selected <- ITQ_projection %>%
-  select(IdOrig,Country, Year, BvBmsy, FvFmsy, itq, iq, ivq) %>%
-  filter(itq != "NA" | iq != "NA" | ivq != "NA")
-
-itq_selected$rightsbased <- 1
-
-itq_selected_2 <- select(itq_selected,Country, IdOrig, Year, rightsbased)
-
-itq_new_join <- join(itq_selected_2, countries_itq_2012, by = c(Country, IdOrig, Year), type = "full")
-
-##not using this anymore
-
-ITQ_projection <- readRDS("processed_data//not_actively_used/ITQ_projection.rds")
-
-countries_with_ITQ <- ITQ_projection %>%
-  select (Country, itq, iq, ivq, Year, IdOrig) %>%
-  filter(Year == "2012")
-
-countries_with_ITQ_2 <- unique(countries_with_ITQ[, 1:6])
-countries_with_ITQ_3 <- filter(countries_with_ITQ_2, itq != "NA" | iq != "NA" | ivq != "NA")
-
-countries_with_ITQ_3$rightsbased <- 1
-countries_itq_2012 <- select(countries_with_ITQ_3, Country, IdOrig, rightsbased)
-
-##need to update projection data
-
-f_b_itq <- ITQ_projection %>%
-  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq") %>%
-  filter( itq != "NA", iq != "NA", ivq != "NA")
-
-ISSCAAP Codes and the non-species specific codes
-```{r}
-
-meta_isscaap_codes_1 <- join(isscaap_codes, ISSCAAP_species, by = c("SciName", "SpeciesCat"), type = "full")
-
-meta_isscaap_codes <- unique( meta_isscaap_codes_1[ , 1:2 ] )
-write_csv(meta_isscaap_codes, "meta_isscaap_codes.csv")
-```
-
-12/18/2018
-Using the newly updated upside/ITQ and filtering out only the most recent date for each fishery
-- make a df of these that have ITQs and those that don't -> apply to OG upside/ITQ data so that more recent years can have ITQ data
-- take this new df and filter out the most recent years with ITQs and KOBE plot. also do catches
-
-```{r}
-
-ITQ_projection <- readRDS("data/ITQ_projection.rds")
-
-upside_2016 <- ITQ_projection %>%
-  filter(Year <= "2016") %>%
-  unite(id_country, IdOrig, Country, sep = "-")
-
-upside_recent <- setDT(upside_2016)[,.SD[which.max(Year)],keyby=id_country]
-
-upside_allfisheriesITQ <- upside_recent %>%
-  select (id_country, itq, iq, ivq, Year, turf) %>%
-  filter(itq != "NA" & iq != "NA" & ivq != "NA" )
-
-```
-
-#Pulling out information about ITQs/TURFs in Corbette Data to apply to upside data
-```{r}
-
-Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
-
-#new dataframw with just most recent year of data for each fishery
-corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
-
-#filter out the fisheries with no data on itqs or turfs
-corbette_fisheries <- corbette_recent %>%
-  select(assess_id_short, year, speciescat, iq, itq, ivq, coop, turf)%>%
-  filter(itq != "NA" & iq != "NA" & ivq != "NA")%>%
-  filter(turf != "NA" )
-
-#new data frame with just data on fisheries with itqs
-fisheries_with_itq <- corbette_fisheries %>%
-   filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" | turf == "TRUE" )
-
-```
-
-reupdating upside data with new ITQ list
-
-```{r}
-#Load Data
-#Upside data
-projection_data <- readRDS("data/projection_data.rds")
-
-#RAMS
-load("data/DBdata-model_fits_included.RData")
-
-#RAM Data Tiddying
-ram <- timeseries_values_views %>%
-  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
-  add_column("RAM")
-
-colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
-
-#Update Projection with RAM
-projection_updated <- join(ram, projection_data, by = c("CommName", "Year"), type = "full")
-##note: RAM data has some fisheries not in the projection data, thus adding new fisheries to the upside projection data
-
-#separate and unit functions to create a shorter version of the stock assessment ID to merge with corbette ITQ/TURF data later
-separate_projection <- projection_updated%>% 
-  separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))
-
-unite_projection <- separate_projection %>% 
-  unite(assess_id_short, agency, stock, sep = "-")
-
-colnames(fisheries_with_itq) <- c("assess_id_short", "Year","SpeciesCat" , "iq", "itq", "ivq", "coop", "turf")
-
-#merge corbette's data on ITQ/Turf implemented or not for each fishery
-fishery_itq_simple <- fisheries_with_itq %>%
-  select(assess_id_short,iq, itq, ivq, turf )
-
-ITQ_projection_merge <- merge(unite_projection, fisheries_with_itq, by = c("assess_id_short"), all = TRUE)
-
-#filter out data post 2016 because we know that those are projected/modeled data not recorded
-recent_pre2016 <- ITQ_projection_merge %>%
-  filter(Year.x <= "2016")
-
-#keep only info on most recent year for each fishery  
-fisheries_recent_1 <- setDT(recent_pre2016)[,.SD[which.max(Year.x)],keyby=assess_id_short]
-
-#select the columns we are interested in
-fisheries_recent <- fisheries_recent_1 %>%
-  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq, turf)
-
-#write dataframe to csv file
-#fisheries_recent <- write.csv(fisheries_recent, file = "fisheries_recent.csv")
-
-```
-
-##KOBE Plots with only most recent year of fisheries
-RAM only
-No data: ITQ = FALSE
-
-```{r}
-
-#read in data: this is updated projection data (updated using RAMs) and Corbett's ITQ/Turf data applied to each fishery. only data for most recent year for each fishery is represented.
-
-fisheries_recent <- read_csv("data/fisheries_recent.csv")
-
-#assuming that when no data is avaliable on the fishery inregardes to ITQ or Turfs that means there are none
-fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
-fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
-fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
-fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
-
-#only looking at fisheries data that come from RAMS database
-# creating new column called "rightsbased" where 1 = ITQ and 0 = No ITQ
-fisheries_KOBE_ram <- fisheries_recent %>%
-  filter(Dbase == "RAM") %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-#graphing logistics
-fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "0"]<- "No ITQ"
-fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "1"]<- "ITQ"
-
-F_B_graph_RAM <- ggplot(data = fisheries_KOBE_ram, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(0, 2.5)+
-  xlim(0, 2.5)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))+
-  ggtitle("KOBE Plot: RAM only Fisheries")
-
-#F_B_graph
-ggplotly(F_B_graph_RAM)
-
-```
-
-##KOBE Plots with only most recent year of fisheries
-RAM only
-No data: ITQ = FALSE
-```{r}
-
-#read in data: this is updated projection data (updated using RAMs) and Corbett's ITQ/Turf data applied to each fishery. only data for most recent year for each fishery is represented.
-fisheries_recent <- read_csv("data/fisheries_recent.csv")
-
-#assuming that when no data is avaliable on the fishery inregardes to ITQ or Turfs that means there are none
-fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
-fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
-fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
-fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
-
-fisheries_KOBE <- fisheries_recent %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))
-
-fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "0"]<- "No ITQ"
-fisheries_KOBE$rightsbased[fisheries_KOBE$rightsbased == "1"]<- "ITQ"
-
-#graphing logistics
-F_B_graph <- ggplot(data = fisheries_KOBE, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
-  geom_point()+
-  labs(x = "B/Bmsy", y= "F/Fsmy") +
-  theme_minimal()+
-  theme(legend.title=element_blank())+
-  ylim(0, 2.5)+
-  xlim(0, 2.5)+
-  geom_hline(aes(yintercept=1))+
-  geom_vline(aes(xintercept=1))+
-  ggtitle("KOBE Plot:  All Fisheries")
-
-#F_B_graph
-ggplotly(F_B_graph)
-
-```
-
-## adding turf information to upside projection(ie: fisheries_recent)
-```{r}
-
-#load in data for turf/itq only projection
-turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
-
-turf_only <- turf_itq_isscaap %>%
-  select(SciName, Country, turf)
-
-fisheries_recent_generousturf_1 <- select(fisheries_recent, Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
-
-#merge the most recent data on each fishery with turf data
-fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turf_only, by = c("Country", "SciName")) #, all = "TRUE")
-
-#assuming that when no data is present for itqs/turf that means there are none
-fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
-fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
-fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
-fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
-
-fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
-  mutate(rightsbased = case_when(
-    turf == TRUE ~ "2",
-    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1"
-    ))
-
-#create dfs for turf, itq, and no itq fisheries to calculate the sum of each
-#NOTE to rememeber: the data from these fisheries are the most recent numbers we have. they are not all in the same year 
-turfs <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
-itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "1")
-no_itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "0")
-
-sum(turfs$Catch, na.rm = TRUE)
-
-sum(itq$Catch, na.rm = TRUE)
-
-sum(no_itq$Catch, na.rm = TRUE)
-
-```
-
-turf only = 413 rows
-fisheries recent = 5294
-
-5643 actual rows
-5707 when manually added added
-- this means 64 species were matched with existing species in database
-- when separated out all by species it was worse
-
-- separate remaining by genus?
-
-12/20/2018
-new UN GDP data, 2016 only
-Scaled GDPs
-Rerun Regressions
-###itq or turf: probablity of itq = f(ISSCAPP and GDP)
-*regression converges*
-```{r}
-
-fisheries_recent <- read_csv("data/fisheries_recent.csv")
-
-fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
-fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
-fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
-fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
-
-turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
-
-turf_only <- turf_itq_isscaap %>%
-  select(SciName, Country, turf, SpeciesCat)
-
-fisheries_recent_generousturf_1 <- fisheries_recent %>%
-  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
-
-fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
-
-fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
-fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
-fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
-fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
-
-fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
-  mutate(rightsbased = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    itq == FALSE | iq == FALSE | ivq == FALSE ~ "0"
-    ))
-
-gdp_all <- read_excel("data/un_gdp_2016.xls")
-
-gdp <- gdp_all %>%
-  select(Country, gdp_center) %>%
-  filter( gdp_center != "NA")
-
-join_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))
-
-gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )
-
-gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
-gdp_rightsbased$rightsbased <- as.numeric(gdp_rightsbased$rightsbased)
-
-itq_glm <- glm(formula = rightsbased ~ gdp_center + SpeciesCat, family = "binomial", data = gdp_rightsbased)
-itq_glm
-
-summary(itq_glm)
-
-```
-
-Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
-
-```{r}
-fisheries_recent <- read_csv("data/fisheries_recent.csv")
-
-fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
-fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
-fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
-fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"
-
-turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")
-
-turf_only <- turf_itq_isscaap %>%
-  select(SciName, Country, turf, SpeciesCat)
-
-fisheries_recent_generousturf_1 <- fisheries_recent %>%
-  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)
-
-fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")
-
-fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
-fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
-fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
-fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"
-
-fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
-  mutate(rightsbased = case_when(
-    turf == TRUE ~ "1",
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "0"
-    ))
-
-gdp_all <- read_excel("data/un_gdp_2016.xls")
-
-gdp <- gdp_all %>%
-  select(Country, gdp_center) %>%
-  filter( gdp_center != "NA")
-
-join_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))
-
-gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )
-
-gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
-gdp_rightsbased$rightsbased <- as.numeric(gdp_rightsbased$rightsbased)
-
-itq_turf_glm <- glm(formula = rightsbased ~ gdp_center + SpeciesCat, family = "binomial", data = gdp_rightsbased)
-itq_glm
-
-summary(itq_turf_glm)
-
-```
-
-##Diagnostics
-
-```{r}
-
-##run above chunk to get gdp_rightsbased df not the old csv file that is now archived in data folder
-
-diagnostics <- gdp_rightsbased %>%
-  mutate(management = case_when(
-    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
-    turf == TRUE ~ "2",
-    itq == FALSE | iq == FALSE | ivq == FALSE | turf == FALSE ~ "0"
-    )) %>%
-  select(Country, gdp_center, SpeciesCat, management)
-
-#diagnostics wont run with non-numeric?
-diagnostics$SpeciesCat <- as.numeric(diagnostics$SpeciesCat)
-diagnostics$management <- as.numeric(diagnostics$management)
-
-#2= gdp; 4= turf; 5 = SpeciesCat; 23 = itq; 24= ivq; 25 = iq; 26= binary rights based
-pairs(diagnostics[2:4])
-
-#pearson's r correlations
-cor(diagnostics[2:4])
-
-#run chi square?
-
-```
-## MPA stuff

### 2019-01-07 scripts/fisheries_last_10_years.R

@@ -1,15 +1,15 @@
 
 #Loading packages
-  library(tidyverse)
-  library(tidyr)
-  library(here)
-  library(ggplot2)
-  library(dplyr)
-  library(readxl)
-  library(devtools)
-  library(plotly)
-  library(rio)
-  library(data.table)
+library(tidyverse)
+library(tidyr)
+library(here)
+library(ggplot2)
+library(dplyr)
+library(readxl)
+library(devtools)
+library(plotly)
+library(rio)
+library(data.table)
 
 Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
 
@@ -17,8 +17,8 @@ Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
 corbette_recent <- Countries_ITQ %>% 
   group_by(assess_id_short) %>% 
   filter(year == max(year))
-  
-  # setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
+
+# setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
 
 
 # corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
@@ -57,7 +57,7 @@ colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", 
 
 ram_data <- ram %>% 
   left_join(projection_data %>% filter(Dbase == "RAM") %>% select(-BvBmsy,-FvFmsy,-Catch,-Biomass), by = c("CommName","Year")) %>% 
-select(colnames(projection_data))
+  select(colnames(projection_data))
 
 # projection_updated <- dplyr::full_join(projection_data, ram, by = c("CommName", "Year"))
 
@@ -67,8 +67,8 @@ projection_updated <- projection_data %>%
   group_by(IdOrig) %>% 
   dplyr::mutate(final_year = max(Year))
 
-  # 
-  # dplyr::full_join(projection_data, ram, by = c("CommName", "Year"))
+# 
+# dplyr::full_join(projection_data, ram, by = c("CommName", "Year"))
 
 ##note: RAM data has some fisheries not in the projection data, thus adding new fisheries to the upside projection data
 
@@ -87,33 +87,30 @@ fishery_itq_simple <- fisheries_with_itq %>%
 
[…]

### 2019-01-07 scripts/fisheries_last_5_years.R

@@ -1,15 +1,15 @@
 
 #Loading packages
-  library(tidyverse)
-  library(tidyr)
-  library(here)
-  library(ggplot2)
-  library(dplyr)
-  library(readxl)
-  library(devtools)
-  library(plotly)
-  library(rio)
-  library(data.table)
+library(tidyverse)
+library(tidyr)
+library(here)
+library(ggplot2)
+library(dplyr)
+library(readxl)
+library(devtools)
+library(plotly)
+library(rio)
+library(data.table)
 
 Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
 
@@ -17,8 +17,8 @@ Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
 corbette_recent <- Countries_ITQ %>% 
   group_by(assess_id_short) %>% 
   filter(year == max(year))
-  
-  # setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
+
+# setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
 
 
 # corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
@@ -57,7 +57,7 @@ colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", 
 
 ram_data <- ram %>% 
   left_join(projection_data %>% filter(Dbase == "RAM") %>% select(-BvBmsy,-FvFmsy,-Catch,-Biomass), by = c("CommName","Year")) %>% 
-select(colnames(projection_data))
+  select(colnames(projection_data))
 
 # projection_updated <- dplyr::full_join(projection_data, ram, by = c("CommName", "Year"))
 
@@ -67,8 +67,8 @@ projection_updated <- projection_data %>%
   group_by(IdOrig) %>% 
   dplyr::mutate(final_year = max(Year))
 
-  # 
-  # dplyr::full_join(projection_data, ram, by = c("CommName", "Year"))
+# 
+# dplyr::full_join(projection_data, ram, by = c("CommName", "Year"))
 
 ##note: RAM data has some fisheries not in the projection data, thus adding new fisheries to the upside projection data
 
@@ -87,33 +87,27 @@ fishery_itq_simple <- fisheries_with_itq %>%
 
[…]

### 2019-01-07 draft_figures_01.07.19.Rmd
5 and 10 year catch averages

--- 2019-01-05 draft_figures_12.23.18.Rmd
@@
 Global Catch Estimate = 80 million
+
+##Percent Catch ITQ over last 5 Years
+
+##Percent Catch ITQ over last 10 Years
+```{r}
+
+fisheries_recent_10years <- read_csv("data/fisheries_recent_10years.csv")
+
+#assuming that when no data is present for itqs/turf that means there are none
+fisheries_recent_10years$turf[is.na(fisheries_recent_10years$turf)] <- "FALSE"
+fisheries_recent_10years$itq[is.na(fisheries_recent_10years$itq)] <- "FALSE"
+fisheries_recent_10years$ivq[is.na(fisheries_recent_10years$ivq)] <- "FALSE"
+fisheries_recent_10years$iq[is.na(fisheries_recent_10years$iq)] <- "FALSE"
+
+###creating new column for management; also merging country and the name of species in order to have a way of IDing the fishery to merge with averages in next code peiece
+fisheries_turf_itqs_10years_1 <- fisheries_recent_10years %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"
+    ))
+
+##get average catch over last 5 years for each fishery
+mean_10years <- aggregate(fisheries_turf_itqs_10years_1[, 7], list(fisheries_turf_itqs_10years_1$assess_id_short), mean)
+colnames(mean_10years) <- c("assess_id_short", "TenYearCatchAvg")
+
+fisheries_turf_itqs_10years_2 <- select(fisheries_turf_itqs_10years_1, "assess_id_short", "rightsbased", "CommName")
+
+fisheries_turf_itqs_10years <-  merge(fisheries_turf_itqs_10years_2, mean_10years, by.x = "assess_id_short")
+
+turfs_catch <- filter(fisheries_turf_itqs_10years, rightsbased == "2")
+itq_catch <- filter(fisheries_turf_itqs_10years, rightsbased == "1")
+no_itq_catch <- filter(fisheries_turf_itqs_10years, rightsbased == "0")
+
+sum(turfs_catch$TenYearCatchAvg, na.rm = TRUE)
+
+sum(itq_catch$TenYearCatchAvg, na.rm = TRUE)
+
+sum(no_itq_catch$TenYearCatchAvg, na.rm = TRUE)
+
+```
+Turf: 234,000
+ITQ: 4,115,210 = 5.1%
 

### 2019-01-07 scripts/Testing/fisheries_last_5_years_method2.R

@@ -1,0 +1,113 @@
+
+#Loading packages
+library(tidyverse)
+library(tidyr)
+library(here)
+library(ggplot2)
+library(dplyr)
+library(readxl)
+library(devtools)
+library(plotly)
+library(rio)
+library(data.table)
+
+Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
+
+#new dataframe with just most recent year of data for each fishery
+corbette_recent <- Countries_ITQ %>% 
+  group_by(assess_id_short) %>% 
+  filter(year == max(year))
+
+# setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
+
+
+# corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]
+
+#filter out the fisheries with no data on itqs or turfs
+corbette_fisheries <- corbette_recent %>%
+  select(assess_id_short, year, speciescat, iq, itq, ivq, coop, turf)%>%
+  filter(itq != "NA" & iq != "NA" & ivq != "NA")%>%
+  filter(turf != "NA" ) 
+
+
+#new data frame with just data on fisheries with itqs
+fisheries_with_itq <- corbette_fisheries %>%
+  filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" | turf == "TRUE" )
+#Load Data
+#Upside data
+projection_data <- readRDS("data/projection_data.rds") %>% 
+  filter(Scenario == "Historic") %>% 
+  group_by(IdOrig) %>% 
+  dplyr::mutate(max_year = max(Year)) %>% 
+  filter(max_year == 2012)
+
+
+#RAM
+load("data/DBdata-model_fits_included.RData")
+
+
+#RAM Data Tiddying
+ram <- timeseries_values_views %>%
+  select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
+  add_column("RAM")
+
+colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
+
+#Update Projection with RAM
+
+ram_data <- ram %>% 
+  left_join(projection_data %>% filter(Dbase == "RAM") %>% select(-BvBmsy,-FvFmsy,-Catch,-Biomass), by = c("CommName","Year")) %>% 
+  select(colnames(projection_data))
+
+# projection_updated <- dplyr::full_join(projection_data, ram, by = c("CommName", "Year"))
+
[…]

### 2019-01-10 lab_notebook.Rmd
pushing

@@
 Total: 70,334,153
+
+#####
+1/7/2019
+Catch estimate with average over last 5 years and over last 10 years
+
+##Percent Catch ITQ over last 5 Years
+
+```{r}
+
+fisheries_recent_5years <- read_csv("data/fisheries_recent_5years.csv")
+
+#assuming that when no data is present for itqs/turf that means there are none
+fisheries_recent_5years$turf[is.na(fisheries_recent_5years$turf)] <- "FALSE"
+fisheries_recent_5years$itq[is.na(fisheries_recent_5years$itq)] <- "FALSE"
+fisheries_recent_5years$ivq[is.na(fisheries_recent_5years$ivq)] <- "FALSE"
+fisheries_recent_5years$iq[is.na(fisheries_recent_5years$iq)] <- "FALSE"
+
+###creating new column for management; also merging country and the name of species in order to have a way of IDing the fishery to merge with averages in next code peiece
+fisheries_turf_itqs_5years_1 <- fisheries_recent_5years %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"
+    ))
+
+##get average catch over last 5 years for each fishery
+mean_5years <- aggregate(fisheries_turf_itqs_5years_1[, 7], list(fisheries_turf_itqs_5years_1$assess_id_short), mean)
+
+colnames(mean_5years) <- c("assess_id_short", "FiveYearCatchAvg")
+
+fisheries_turf_itqs_5years <-  merge(fisheries_turf_itqs_5years_1, mean_5years, by.x = "assess_id_short")
+
+turfs_catch <- filter(fisheries_turf_itqs_5years, rightsbased == "2")
+itq_catch <- filter(fisheries_turf_itqs_5years, rightsbased == "1")
+no_itq_catch <- filter(fisheries_turf_itqs_5years, rightsbased == "0")
+
+sum(turfs_catch$FiveYearCatchAvg, na.rm = TRUE)
+
+sum(itq_catch$FiveYearCatchAvg, na.rm = TRUE)
+
+sum(no_itq_catch$FiveYearCatchAvg, na.rm = TRUE)
+
+```
+Turf: 234,000
+ITQ: 4,093,520 = 5.1%
+
+##Percent Catch ITQ over last 10 Years
+** different method
+```{r}
+
+fisheries_recent_10years <- read_csv("data/fisheries_recent_10years.csv")
+
+#assuming that when no data is present for itqs/turf that means there are none
+fisheries_recent_10years$turf[is.na(fisheries_recent_10years$turf)] <- "FALSE"
+fisheries_recent_10years$itq[is.na(fisheries_recent_10years$itq)] <- "FALSE"
+fisheries_recent_10years$ivq[is.na(fisheries_recent_10years$ivq)] <- "FALSE"
+fisheries_recent_10years$iq[is.na(fisheries_recent_10years$iq)] <- "FALSE"
+
+###creating new column for management; also merging country and the name of species in order to have a way of IDing the fishery to merge with averages in next code peiece
+fisheries_turf_itqs_10years_1 <- fisheries_recent_10years %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"
+    ))
+
+##get average catch over last 5 years for each fishery
+mean_10years <- aggregate(fisheries_turf_itqs_10years_1[, 7], list(fisheries_turf_itqs_10years_1$assess_id_short), mean)
+colnames(mean_10years) <- c("assess_id_short", "TenYearCatchAvg")
+
+fisheries_turf_itqs_10years_2 <- select(fisheries_turf_itqs_10years_1, "assess_id_short", "rightsbased", "CommName")
+
+fisheries_turf_itqs_10years <-  merge(fisheries_turf_itqs_10years_2, mean_10years, by.x = "assess_id_short")
+
+turfs_catch <- filter(fisheries_turf_itqs_10years, rightsbased == "2")
+itq_catch <- filter(fisheries_turf_itqs_10years, rightsbased == "1")
+no_itq_catch <- filter(fisheries_turf_itqs_10years, rightsbased == "0")
+
+sum(turfs_catch$TenYearCatchAvg, na.rm = TRUE)
+
+sum(itq_catch$TenYearCatchAvg, na.rm = TRUE)
+
+sum(no_itq_catch$TenYearCatchAvg, na.rm = TRUE)
+
+```
+Turf: 234,000
+ITQ: 4,115,210 = 5.1%

### 2019-01-10 scripts/Testing/fisheries_last_5_years_method2.R

@@ -87,6 +87,7 @@ fishery_itq_simple <- fisheries_with_itq %>%
 
 ITQ_projection_merge <- full_join(unite_projection, fisheries_with_itq %>% select(-Year), by = c("assess_id_short"))
 
+#once made seperate columns for each 5 years need to only keep the ones where the "final" year matches the Year
 
 ##filter out the last 5 years of data
 recent_pre2016_5years <- ITQ_projection_merge %>%
@@ -94,7 +95,7 @@ recent_pre2016_5years <- ITQ_projection_merge %>%
   dplyr::mutate(final_3year = (final_year-2)) %>%
   dplyr::mutate(final_4year = (final_year-3)) %>%
   dplyr::mutate(final_5year = (final_year-4)) %>%
-  filter(Year <= final_year | Year <= final_2year | Year <= final_3year | Year <= final_4year | Year <= final_5year)
+  filter(Year <= final_year | Year <= final_2year | Year <= final_3year | Year <= final_4year | Year <= final_5year) %>%
 
 #keep only info on most recent year for each fishery  
 fisheries_recent_5years_1 <- recent_pre2016_5years %>% 

### 2019-01-10 scripts/fisheries_last_5_years.R

@@ -89,16 +89,13 @@ ITQ_projection_merge <- full_join(unite_projection, fisheries_with_itq %>% selec
 
 
 ##filter out the last 5 years of data
-recent_pre2016_5years <- ITQ_projection_merge %>%
+fisheries_recent_5years_1 <- ITQ_projection_merge %>%
   dplyr::mutate(final_2year = (final_year-1)) %>%
   dplyr::mutate(final_3year = (final_year-2)) %>%
   dplyr::mutate(final_4year = (final_year-3)) %>%
   dplyr::mutate(final_5year = (final_year-4)) %>%
-  filter(Year <= final_year | Year <= final_2year | Year <= final_3year | Year <= final_4year | Year <= final_5year)
-
-#keep only info on most recent year for each fishery  
-fisheries_recent_5years_1 <- recent_pre2016_5years %>% 
-  filter(Year == final_year & final_year > 2007)
+  filter(Year <= final_year | Year <= final_2year | Year <= final_3year | Year <= final_4year | Year <= final_5year) %>%
+  filter(Year > 2007)
 
 
 #select the columns we are interested in
@@ -107,7 +104,7 @@ fisheries_recent_5years <- fisheries_recent_5years_1 %>%
   filter(SpeciesCat.x != "11")
 
 #write dataframe to csv file
-#fisheries_recent_5years <- write.csv(fisheries_recent_5years, file = "fisheries_recent_5years.csv")
+fisheries_recent_5years <- write.csv(fisheries_recent_5years, file = "fisheries_recent_5years.csv")
 
 
 

### 2019-01-10 documents/dan-figs-and-calcs.Rmd
a few random things

---
title: "dan_global_fisheries"
output: html_notebook
---

```{r}
library(tidyverse)
library(readxl)
library(tidyxl)
library(here)

# source(here("scripts","2016_projection_updated.R"))

fisheries_recent <- read_csv(here("processed_data","fisheries_recent.csv"))%>% 
  janitor::clean_names()

```

```{r}

```

# rbfm

However, while these fisheries make up XX\% of global captures
```{r}

global_summaries <- fisheries_recent %>% 
  group_by(dbase) %>% 
  summarise(total_catch = sum(catch, na.rm = T),
            n = n_distinct(assess_id_short))

```

# mpas

```{r}

mpas <- readxl::read_xlsx(here("data","MPA Analysis. Country Analysis.xlsx"), sheet = "clean_mpa") %>% janitor::clean_names()

```

### 2019-01-10 scripts/2016_projection_updated.R

@@ -10,8 +10,9 @@
   library(plotly)
   library(rio)
   library(data.table)
-
-Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")
+  library(here)
+  
+Countries_ITQ <- read_excel(here("data","Countries_ITQ.xlsx"))
 
 #new dataframw with just most recent year of data for each fishery
 corbette_recent <- Countries_ITQ %>% 
@@ -35,21 +36,27 @@ fisheries_with_itq <- corbette_fisheries %>%
   filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" | turf == "TRUE" )
 #Load Data
 #Upside data
-projection_data <- readRDS("data/projection_data.rds") %>% 
+projection_data <- readRDS(here("data","projection_data.rds")) %>% 
   filter(Scenario == "Historic") %>% 
   group_by(IdOrig) %>% 
   dplyr::mutate(max_year = max(Year)) %>% 
   filter(max_year == 2012)
 
+test <- projection_data %>% 
+  filter(Year == max_year) %>% 
+  group_by(CatchShare, Dbase) %>% 
+  summarise(total_catch = sum(Catch))
+
 
 #RAM
-load("data/DBdata-model_fits_included.RData")
+load(here("data","DBdata-model_fits_included.RData"))
 
 
 #RAM Data Tiddying
 ram <- timeseries_values_views %>%
   select("stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref") %>%
   add_column("RAM")
+
 
 colnames(ram) <- c( "CommName", "Year", "Biomass", "Catch", "BvBmsy", "FvFmsy", "DBase")
 
@@ -100,6 +107,9 @@ fisheries_recent_1 <- recent_pre2016 %>%
 fisheries_recent <- fisheries_recent_1 %>%
   select(Country, assess_id_short, Year, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq, turf)
 
+ b <- fisheries_recent %>% 
+   filter(!is.na(itq) | !is.na(ivq) | !is.na(iq))
+
 a = fisheries_recent %>% 
   ggplot(aes(BvBmsy, FvFmsy, color =Dbase )) + 
   geom_point() + 
@@ -112,5 +122,5 @@ a = fisheries_recent %>%
 
 
[…]

### 2019-01-10 Past_draft_figs/draft_figures.Rmd

---
title: "Draft Figures and Analyses"
author: "Juliette Verstaen"
date: "12/9/2018"
output: pdf_document
toc: true
toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE }

suppressPackageStartupMessages({
  library(tidyverse)
  library(tidyr)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(readxl)
  library(devtools)
  library(plotly)
  library(base)
  library(rio)
  library(plyr)
})
```

## 1. Plot each fishery B/Bmsy versus F/Fsmy
**Data used**:   updated upside data with Corbett's ITQ/no ITQ data

**Note:**

- Corbett's ITQ data is only until 2012

- Chris's upside data is now updated until 2016 with the more recent RAM data that Dan had.

**Issues:**

1. Since Corbett's ITQ data is only until 2012, all the fisheries specific data we have past that does not have ITQ data assocaited with them. I made "KOBE" plots with the following data:

    a.  fisheries 1950 - 2012

    b.  fisheries 1950 - 2016

2. Dealing with fisheries with no data on ITQs:
ITQ related analyzes are limited to fisheries that Corbette had data on. I removed the fisheries that have no information on presence or absence of ITQs. I am unsure if this is biasing the data; should we assume that the fisheries with no definate information on ITQs have no ITQs? This seems like it woud be biased as well. 
    - Corbette's ITQ data includes 375 different fisheries years 1950-2012 for a total of ~15,000 lines of data

###a. "KOBE" plots with ITQs not updated past 2012
*All fisheries 1950-2012 *
```{r}

ITQ_projection <- readRDS("data/ITQ_projection.rds")

f_b_itq <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0")) %>%
  filter(Year >= "1950") %>%
  filter(Year <= "2012")

f_b_itq$rightsbased[f_b_itq$rightsbased == "0"]<- "No ITQ"
f_b_itq$rightsbased[f_b_itq$rightsbased == "1"]<- "ITQ"

ggplot(data = f_b_itq, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 5)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  ggtitle("Fisheries 1950-2012")

```

###b. "KOBE" plots with ITQs updated through 2016
*All fisheries 1950-2016 *
```{r}

ITQ_projection_updated <- readRDS("data/ITQ_projection_updated.rds")

f_b_itq_updated <- ITQ_projection_updated %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0")) %>%
  filter(Year >= "1950") %>%
  filter(Year <= "2016")

f_b_itq_updated$rightsbased[f_b_itq_updated$rightsbased == "0"]<- "No ITQ"
f_b_itq_updated$rightsbased[f_b_itq_updated$rightsbased == "1"]<- "ITQ"

ggplot(data = f_b_itq_updated, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 5)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  ggtitle("Fisheries 1950-2016")

```

##2. Total Global Catch from ITQ, TURF, or No ITQ fisheries

**Data used**:   updated upside data with Corbett's ITQ/no ITQ data

**Notes:**

- Same issues as before with Corbett data only until 2012
- For analysis through 2016: extracted information about which fisheries had ITQs in 2012 and applied it to the same fisheries into the future. This doesn't take into account other fisheries implement ITQs past 2012, or if fisheries stop ITQs. Only countries with ITQs in 2012 are : Australia, USA, Canda, Japan, Peru, Argentina, South Africa, New Zealand

*The analysis below does not include TURF information from DiscoverTurf GP because that data is not fishery specific enough to merge with the upside/Corbette data*

**technical note for JV: what units is the catch in the upside/rams data?**

###a. Total Catch ITQ, No ITQ, TURF in 2012
```{r}
ITQ_projection <- readRDS("data/ITQ_projection.rds")

f_b_itq_countries <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
  filter( itq != "NA" & iq != "NA" & ivq != "NA" & turf != "NA") %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

countries_itq_2012 <- f_b_itq_countries %>%
  select (Country, rightsbased, Year, IdOrig, Catch) %>%
  filter(Year == "2012")

itq_2012_rightsbasedTRUE <- filter(countries_itq_2012, rightsbased == "1")

itq_2012_rightsbasedFALSE <- filter(countries_itq_2012, rightsbased == "0")

itq_2012_rightsbasedTURF <- filter(countries_itq_2012, rightsbased == "2")

sum(itq_2012_rightsbasedTRUE$Catch, na.rm = TRUE)
#4,350,545

sum(itq_2012_rightsbasedFALSE$Catch, na.rm = TRUE)
#149,554

sum(itq_2012_rightsbasedTURF$Catch, na.rm = TRUE)
#260,000
```
####**2012 total catch:**

ITQs: 4,350,545

No ITQ: 149,554 (all USA)

TURF: 260,000(all Japan)

###b. Total Catch ITQ, No ITQ, TURF in 2016
```{r}

ITQ_projection <- readRDS("data/ITQ_projection.rds")

f_b_itq_countries <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
  filter( itq != "NA" & iq != "NA" & ivq != "NA" & turf != "NA") %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

countries_itq_2012_2 <- f_b_itq_countries %>%
  select (Country, rightsbased, Year, IdOrig) %>%
  filter(Year == "2012")  %>%
  select(Country, rightsbased, IdOrig)

ITQ_projection_2016 <- ITQ_projection %>%
  filter(Year == "2016") %>%
  select(IdOrig, Country, Year, Catch)

itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012_2, by= c("IdOrig", "Country"), type= "full")

itq_2016_rightsbasedTRUE <- filter(itq_2016_updated, rightsbased == "1")

itq_2016_rightsbasedFALSE <- filter(itq_2016_updated, rightsbased == "0")

itq_2016_rightsbasedTURF <- filter(itq_2016_updated, rightsbased == "2")

sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
#20,217,168

sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
#1,154,957

sum(itq_2016_rightsbasedTURF$Catch, na.rm = TRUE)
#382,370.4
```

####**2016 total catch:**

ITQs: 20,217,168

No ITQ: 1,154,957 (all in the USA)

TURF: 382,370.4 (all in Japan)

##3. Probability of ITQ

###itq or turf: probablity of itq = f(ISSCAPP and GDP)
*regression converges*
```{r}

turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")

gdp_all <- read_csv("/GitHub/global_fisheries_managment/data/gpd.csv")

gdp <- filter(gdp_all, current_gdp != "NA")

turf_itq_isscaap_mutate <- turf_itq_isscaap %>%
  mutate(i_right = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0")) %>%
  mutate(TURF = case_when(
    turf == TRUE ~ "1", 
    turf = FALSE ~"0"
  )) %>%
  select(SciName, Country, SpeciesCat, i_right, TURF)

turf_itq_isscaap_mutate$TURF[is.na(turf_itq_isscaap_mutate$TURF)] <- "0"

join_gdp_rightsbased <- merge(gdp, turf_itq_isscaap_mutate, by = c("Country"))

gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )

gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
gdp_rightsbased$i_right <- as.numeric(gdp_rightsbased$i_right)

itq_glm <- glm(formula = i_right ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
itq_glm

summary(itq_glm)

```

##4. Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
*regression does not converge*
```{r}
turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")

gdp_all <- read_csv("/GitHub/global_fisheries_managment/data/gpd.csv")

gdp <- filter(gdp_all, current_gdp != "NA")

species_rightsbased_mutate_2 <- turf_itq_isscaap %>%
  mutate(rightbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "0",
    turf == TRUE ~ "1"))

gdp <- filter(gdp_all, current_gdp != "NA")

join_gdp_rightsbased_2 <- join(gdp, species_rightsbased_mutate_2, by = c("Country"), type = "full")

gdp_rightsbased_2 <- filter(join_gdp_rightsbased_2, SpeciesCat != "NA" )

gdp_rightsbased_2$SpeciesCat <- factor(gdp_rightsbased_2$SpeciesCat)
gdp_rightsbased_2$rightbased <- as.numeric(gdp_rightsbased_2$rightbased)

rightbased_glm <- glm(formula = rightbased ~ current_gdp + SpeciesCat + programstart, family = "binomial", data = gdp_rightsbased_2)
rightbased_glm

summary(rightbased_glm)

```

##5. MPA Area by Country

*Note: did not filter out MPAs that did no meet IUCN and/or CBD PA definition*

MPA data: from protectedplanet.net
```{r}
mpa_updated <- read_csv("data/mpa_updated.csv") 
```

###MPAs that are completly No Take
The top 10 countries with the largest MPA area (km$$^2$$). These MPAs are 100% no take.
```{r}

##Completly no Take
mpa <- mpa_updated %>%
  select(Country, REP_M_AREA, MARINE, NO_TAKE) %>%
  filter(MARINE == "2" | MARINE == "1") %>%
  filter(NO_TAKE == "All") %>%
  group_by(Country)

mpa_area <- aggregate(mpa$REP_M_AREA, by=list(Country=mpa$Country), FUN=sum)
mpa_area

names(mpa_area) <-c("Country", "Area")

mpa_area_10 <- top_n(mpa_area, 10, Area)
mpa_area_10

##all countries
mpa_area_10$Country <- factor(mpa_area_10$Country, levels = mpa_area_10$Country[order(mpa_area_10$Area)])

ggplot(mpa_area_10, aes(x = Country, y = Area)) +
  geom_bar(stat = "identity")+
  ggtitle("Top 10 Countries with No Take MPAs")+
  coord_flip()+
  theme_bw()+
  ylab("Area km2")

```

###MPAs that are completly No Take
The top 10 countries (minus areas beyond national jurisdiction) with the largest MPA area (km$$^2$$). These MPAs are 100% no take.
```{r}

##Completly no Take
mpa <- mpa_updated %>%
  select(Country, REP_M_AREA, MARINE, NO_TAKE) %>%
  filter(MARINE == "2" | MARINE == "1") %>%
  filter(NO_TAKE == "All") %>%
  group_by(Country)

mpa_area <- aggregate(mpa$REP_M_AREA, by=list(Country=mpa$Country), FUN=sum)
mpa_area

names(mpa_area) <-c("Country", "Area")

mpa_area_10 <- top_n(mpa_area, 10, Area)
mpa_area_10

#all countries minus areas beyond national jurisdiction
mpa_area_nojurisdiction <-filter(mpa_area, Country != "Areas Beyond National Jurisdiction")
mpa_area_nojurisdiction_10 <- top_n(mpa_area_nojurisdiction, 10, Area)
mpa_area_nojurisdiction_10

mpa_area_nojurisdiction_10$Country <- factor(mpa_area_nojurisdiction_10$Country, levels = mpa_area_nojurisdiction_10$Country[order(mpa_area_nojurisdiction_10$Area)])

ggplot(mpa_area_nojurisdiction_10, aes(x = Country, y = Area)) +
  geom_bar(stat = "identity")+
  ggtitle("Top 10 Countries with No Take MPAs (-ABNJ)")+
  coord_flip()+
  theme_bw()+
  ylab("Area km2")

```

###MPAs that are completly No Take or Partial No Take
```{r}
##No Take and Partial Take

mpa_parttake <- mpa_updated %>%
  select(Country, REP_M_AREA, MARINE, NO_TAKE) %>%
  filter(MARINE == "2" | MARINE == "1") %>%
  filter(NO_TAKE == "All" | NO_TAKE == "Part") %>%
  group_by(Country)

mpa_area_part <- aggregate(mpa_parttake$REP_M_AREA, by=list(Country=mpa_parttake$Country), FUN=sum)
mpa_area_part

names(mpa_area_part) <-c("Country", "Area")

mpa_area_part_10 <- top_n(mpa_area_part, 10, Area)
mpa_area_part_10

##all countries
mpa_area_part_10$Country <- factor(mpa_area_part_10$Country, levels = mpa_area_part_10$Country[order(mpa_area_part_10$Area)])

ggplot(mpa_area_part_10, aes(x = Country, y = Area)) +
  geom_bar(stat = "identity")+
  ggtitle("Top 10 Countries with No or Partial Take MPAs")+
  coord_flip()+
  theme_bw()+
  ylab("Area km2")

```

### 2019-01-10 documents/figs-and-calcs.Rmd

---
title: "figures and calculations for global fisheries management"
output: html_notebook
---

```{r load}
library(tidyverse)
library(readxl)
library(tidyxl)
library(here)

fisheries_recent <- read_csv(here("processed_data","fisheries_recent.csv"))%>% 
  janitor::clean_names()

```

# figures

## figure 1 Kobe plot with assessed vs. unassessed (color), size/alpha by size. Medians by size.

A traditional Kobe plot of fishery status. Horizontal axis is $B/Bmsy$ and vertical axis is $F/Fmsy$. Each point is a single fishery. Size and shading indicates $MSY$ of the fishery and color indicates whether the fishery has a stock assessment. Medians for stock assessed, and unassesed fisheries are presented as triangles.

```{r fig-1-kobe}

fig_1 = mtcars %>% 
  ggplot(aes(mpg)) + 
  geom_histogram()

ggsave(here("figures","figure-1.pdf"), fig_1)

```

## figure 2 map of RBFM map of RBFM around the planet Color the country if it has ITQ

Global map of countries that manage at least some of their fish catch with ITQs.

```{r}

```

## figure 3  status by RBFM - Kobe, color is RBFM, size is size. Medians RBFM and RBFM-.

A traditional Kobe plot of fishery status for stocks present in the RAM legacy stock assessment database. Horizontal axis is $B/Bmsy$ and vertical axis is $F/Fmsy$. Each point is a single fishery. Size and shading indicates $MSY$ of the fishery and color indicates whether the fishery is managed with RBFM. Medians for RBFM and non-RBFM fisheries are shown as triangles.

## figure 4 bioeconomic figure to show in principle why you get increase in value from RBFM

Simple bioeconomic model represntation illustrating the mechanisms by which RBFM can increase fishery profit, food provision, and biomass of fish

## figure 5 is global fishing watch, JC

## figure 6 figure of bionomic equilibrium and shift in cost downward

# calculations

## line 22

"and is roughly equivalent to total land and sea production of aquaculture XX"

```{r}

```

## line 53

Famous fisheries such as Alaskan halibut and king crab both experienced derby periods, during which the season could be as short as 24 hours, producing XX in estimated dollars lost

```{r}

```

## line 65

Using data from (Costello et al., 2016), we can identify which of the fisheries identified by the FAO are currently being managed using ITQs, and from there estimate that xx\% of annual global marine capture comes from fisheries currently managed under ITQs

```{r}

```

## line 70

Based on this calculation, we find that up to xx\% of global catch comes from TURFs and up to XX \% comes from cooperatives. In total, based on best available data to date,  we estimate that somewhere between XXX\% and XXX\% of global wild fish catch comes from all forms of RBFM combined. The What kinds of fisheries make up this RBFM catch? RBFM catches come from XX\% of the countries reporting  fish catches in 2016xx.

```{r}

```

## line 92

What factors drive the adoption of various forms of RBFM? Anecdotal evidence suggests that large, industrial fisheries, often for mobile species are most likely to adopt some form of ITQ, while small-scale artisinal fisheries, often for benthic species, are most likely to adopt a TURF. To test this expectation, we built a dataset of XXX ITQ fisheries and XXX TURF fisheries, and matched them to the fishery classification in \cite{Upside}. This provided us with a dataset of XXX fisheries with the country, species or genus name, and some other ecological and economic characteristics. Conditional on adopting some form of RBFM, our goal was to estimate the likelihood of adopting an ITQ versus a TURF. To do so, we ran a logistic regression with ITQ on the left ha

## line 94 regression
 put equation and all regression analysis in this section

$$Pr(ITQ_i) = f(Genus_i, GDP_i, ...) + \epsilon_i$$

## line 107

to all XX non-rbfm fisheries in the (however many fisheries are not catch shares in projection_data)

```{r}

```

As a percentage of fishery potential (estimated maximum sustainable yield, MSY), the breakdown is XXX\% (ITQ) and XXX\% (TURF). The table below presents the results of this extrapolation for the world's top 20 fishing nations.

```{r}

```

## line 118

Using that approach, authors have estimated a benefit of global RBFM between \$XXX Billion and \$XXX Billion per year. see Costello et al. 2016

## line 120

adopt this bottom up approach, and develop fishery-by-fishery bioeconomic models for 4,7XX fisheries around the world, representing XXX\% of global fish catch. Using that sample, \cite{Upside} estimate an increase in catch of XXX, an increase in biomass of XXX, and an annual economic benefit from RBFM of \$XXX Billion. Scaling this number up by the fraction of catch missing in the database, provides an annual estimate of \$XXX Billion.

## line 122

While the methods differ substantially, estimates of the economic benefit from globally adopting RBFM are all in the vicinity of \$XXX Billion - \$XXX Billion. But achieving these benefits would require substantial re-tooling of the institutions used to govern the oceans and will likely come at a significant cost. Estimating this cost is complicated by the lack of consistent data on the cost of fishery management across fisheries and countries. Recent estimates suggest that annual fishery management costs are in the ballpark of \$XXX to \$XXX per MT of fish catch. Applying this globally provides a cursory estimate of \$XXX Billion for fishery management. But the few studies that have been undertaken also suggest that fishery management costs vary significantly across countries (for example, XXXX). And what we really would like is an estimate of the \textit{change} in fishery management cost associated with adopting RBFM. In a recent paper, \cite{Mangin} provide precisely this estimate. Working fishery-by-fishery, they estimate a global increased cost of \$XXX Billion from adopting RBFM at a global scale. Comparing this number to the potential economic benefits strongly suggests that the benefits of RBFM expansion will outweigh the increased costs; a result echoed by \cite{Sumaila}. The following table summarizes the studies of the benefits and costs of global-scale adoption of RBFM.

https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0204258

## line 143
no-take
As a result of these potential conservation and fishery effects, MPAs have been increasingly proposed as a solution to global fisheries sustainability. For example, the Convention on Biological Diversity's Strategic Plan for Biodiversity  call for 10\% of coastal waters to be protected inside MPAs by 2020. This call has been accompanied by the creation of large MPAs in places such as XX and XX. Table XXX shows the area covered by MPAs in the top-10 MPA countries of the world.  Together, the MPAs in these countries represent the vast majority (XXX\%) of global coverage of MPAs, recognizing that the total global ocean covered by MPAs is still very small (XXX\%).

```{r}

```

# rbfm

However, while these fisheries make up XX\% of global captures
```{r}

global_summaries <- fisheries_recent %>% 
  group_by(dbase) %>% 
  summarise(total_catch = sum(catch, na.rm = T),
            n = n_distinct(assess_id_short))

```

# mpas

```{r}

mpas <- readxl::read_xlsx(here("data","MPA Analysis. Country Analysis.xlsx"), sheet = "clean_mpa") %>% janitor::clean_names()

```

### 2019-01-10 draft_figures_01.07.19.Rmd

@@
 
+```{r}
+# by assess id
+fisheries_recent_5years <- read_csv("data/fisheries_recent_5years.csv")
+
+#assuming that when no data is present for itqs/turf that means there are none
+fisheries_recent_5years$turf[is.na(fisheries_recent_5years$turf)] <- "FALSE"
+fisheries_recent_5years$itq[is.na(fisheries_recent_5years$itq)] <- "FALSE"
+fisheries_recent_5years$ivq[is.na(fisheries_recent_5years$ivq)] <- "FALSE"
+fisheries_recent_5years$iq[is.na(fisheries_recent_5years$iq)] <- "FALSE"
+
+###creating new column for management; also merging country and the name of species in order to have a way of IDing the fishery to merge with averages in next code peiece
+fisheries_turf_itqs_5years_1 <- fisheries_recent_5years %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"
+    ))
+
+##get average catch over last 5 years for each fishery
+mean_5years <- aggregate(fisheries_turf_itqs_5years_1[, 7], list(fisheries_turf_itqs_5years_1$assess_id_short), mean)
+
+colnames(mean_5years) <- c("assess_id_short", "FiveYearCatchAvg")
+
+fisheries_turf_itqs_5years_2 <- select(fisheries_turf_itqs_5years_1, "assess_id_short", "rightsbased", "CommName")
+
+fisheries_turf_itqs_5years <-  merge(fisheries_turf_itqs_5years_2, mean_5years, by.x = "assess_id_short")
+
+turfs_catch <- filter(fisheries_turf_itqs_5years, rightsbased == "2")
+itq_catch <- filter(fisheries_turf_itqs_5years, rightsbased == "1")
+no_itq_catch <- filter(fisheries_turf_itqs_5years, rightsbased == "0")
+
+sum(turfs_catch$FiveYearCatchAvg, na.rm = TRUE)
+
+sum(itq_catch$FiveYearCatchAvg, na.rm = TRUE)
+
+sum(no_itq_catch$FiveYearCatchAvg, na.rm = TRUE)
+
+###########
+#by common name
+# end up with same number by common name becuase the fisheries without more infor (just common name, and location don't have ITQs)
+
+fisheries_recent_5years <- read_csv("data/fisheries_recent_5years.csv")
+
+#assuming that when no data is present for itqs/turf that means there are none
+fisheries_recent_5years$turf[is.na(fisheries_recent_5years$turf)] <- "FALSE"
+fisheries_recent_5years$itq[is.na(fisheries_recent_5years$itq)] <- "FALSE"
+fisheries_recent_5years$ivq[is.na(fisheries_recent_5years$ivq)] <- "FALSE"
+fisheries_recent_5years$iq[is.na(fisheries_recent_5years$iq)] <- "FALSE"
+
+###creating new column for management; also merging country and the name of species in order to have a way of IDing the fishery to merge with averages in next code peiece
+fisheries_turf_itqs_5years_1 <- fisheries_recent_5years %>%
+  mutate(rightsbased = case_when(
+    turf == TRUE ~ "2",
+    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
+    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"
+    ))
+
+##get average catch over last 5 years for each fishery
+mean_5years <- aggregate(fisheries_turf_itqs_5years_1[, 9], list(fisheries_turf_itqs_5years_1$CommName), mean)
+
+colnames(mean_5years) <- c("CommName", "FiveYearCatchAvg")
+
+fisheries_turf_itqs_5years_2 <- select(fisheries_turf_itqs_5years_1, "assess_id_short", "rightsbased", "CommName")
+
+fisheries_turf_itqs_5years <-  merge(fisheries_turf_itqs_5years_2, mean_5years, by.x = "CommName")
+
+turfs_catch <- filter(fisheries_turf_itqs_5years, rightsbased == "2")
+itq_catch <- filter(fisheries_turf_itqs_5years, rightsbased == "1")
+no_itq_catch <- filter(fisheries_turf_itqs_5years, rightsbased == "0")
+
+sum(turfs_catch$FiveYearCatchAvg, na.rm = TRUE)
+
+sum(itq_catch$FiveYearCatchAvg, na.rm = TRUE)
+
+sum(no_itq_catch$FiveYearCatchAvg, na.rm = TRUE)
+
+```
+Turf: 234,000
+ITQ: 4,093,520 = 5.1%
+3,200,000 peru anchovies
+
 ##Percent Catch ITQ over last 10 Years
@@
 
+##by common name instead of assess_id ; get same numbers
+##get average catch over last 5 years for each fishery
+mean_10years <- aggregate(fisheries_turf_itqs_10years_1[, 7], list(fisheries_turf_itqs_10years_1$CommName), mean)
+colnames(mean_10years) <- c("CommName", "TenYearCatchAvg")
+
+fisheries_turf_itqs_10years_2 <- select(fisheries_turf_itqs_10years_1, "assess_id_short", "rightsbased", "CommName")
+
+fisheries_turf_itqs_10years <-  merge(fisheries_turf_itqs_10years_2, mean_10years, by.x = "CommName")
+
+turfs_catch <- filter(fisheries_turf_itqs_10years, rightsbased == "2")
+itq_catch <- filter(fisheries_turf_itqs_10years, rightsbased == "1")
+no_itq_catch <- filter(fisheries_turf_itqs_10years, rightsbased == "0")
+
+sum(turfs_catch$TenYearCatchAvg, na.rm = TRUE)
+
+sum(itq_catch$TenYearCatchAvg, na.rm = TRUE)
+
+sum(no_itq_catch$TenYearCatchAvg, na.rm = TRUE)
 ```

### 2019-01-11 documents/figs-and-calcs.Rmd
populated regression portion of figs-calc document

@@
 title: "figures and calculations for global fisheries management"
-output: html_notebook
+output:
+  pdf_document: default
+  html_notebook: default
 ---
@@
 
+GDP data source: UN website
+Regular ISSCAAP Categories
+```{r}
+
+projection_data <- readRDS(here("data","projection_data.rds")) %>% 
+  filter(Scenario == "Historic")
+
+gdp_all <- read_excel(here("data","un_gdp_2016.xls"))
+
+gdp <- gdp_all %>%
+  select(Country, gdp_center) %>%
+  filter( gdp_center != "NA")
+
+join <- left_join(projection_data, gdp, by = "Country")
+
+join$SpeciesCat <- factor(join$SpeciesCat)
+
+glm <- glm(formula = CatchShare ~ gdp_center + SpeciesCat, family = "binomial", data = join)
+glm
+
+summary(glm)
+
+```
+
+Broader ISSCAAP Categories
+22-24 = diadromous fishes = 2
+31-35, 37 = marine fishes = 3
+42-45,47 = crustaceans = 4
+52-58 = molluscs = 5
+74,76,77 = miscellaneous aquatic animals = 7
+
+```{r}
+
+projection_data <- readRDS(here("data","projection_data.rds")) %>% 
+  filter(Scenario == "Historic")
+
+projection_data_mutate <- projection_data  %>%
+  mutate(MainCat = case_when(
+    SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",
+    SpeciesCat == 31 | SpeciesCat == 32 | SpeciesCat == 33 | SpeciesCat == 34 | SpeciesCat     == 35 | SpeciesCat == 37 ~ "3",
+    SpeciesCat == 42 | SpeciesCat == 43 | SpeciesCat == 44 | SpeciesCat == 45 | SpeciesCat      == 47 ~ "4",
+    SpeciesCat == 52 | SpeciesCat == 53 | SpeciesCat ==54 |  SpeciesCat == 55 | SpeciesCat     == 56 | SpeciesCat == 57 | SpeciesCat == 58 ~ "5",
+    SpeciesCat == 74 | SpeciesCat == 76 | SpeciesCat == 77 ~ "7"
+  ))
+
+gdp_all <- read_excel(here("data","un_gdp_2016.xls"))
+
+gdp <- gdp_all %>%
+  select(Country, gdp_center) %>%
+  filter( gdp_center != "NA")
+
+join_mutate <- left_join(projection_data_mutate, gdp, by = "Country")
+
+join_mutate$MainCat <- factor(join_mutate$MainCat)
+
+glm_broad <- glm(formula = CatchShare ~ gdp_center + MainCat, family = "binomial", data = join_mutate)
+glm_broad
+
+summary(glm_broad)
+
+```
+
 ## line 107

### 2019-01-11 documents/figs-and-calcs.Rmd
downsample data to fix class imbalance

@@
 
-glm <- glm(formula = CatchShare ~ gdp_center + SpeciesCat, family = "binomial", data = join)
-glm
+itq_fit <- glm(formula = CatchShare ~ gdp_center + SpeciesCatName, family = "binomial", data = join)
 
-summary(glm)
+summary(itq_fit)
 
+check <- broom::augment(itq_fit)
 ```
@@
 
-join_mutate <- left_join(projection_data_mutate, gdp, by = "Country")
+join_mutate <- left_join(projection_data_mutate, gdp, by = "Country") %>% 
+  filter(Year == max(Year))
 
@@
 
-glm_broad <- glm(formula = CatchShare ~ gdp_center + MainCat, family = "binomial", data = join_mutate)
-glm_broad
+downjoin <- caret::downSample(x = select(join_mutate,-CatchShare),
+                              y = factor(join_mutate$CatchShare),
+                              yname = "CatchShare")
 
-summary(glm_broad)
+itq_broad_fit <-
+  glm(
+    formula = CatchShare ~ gdp_center + MainCat,
+    family = "binomial",
+    data = downjoin
+  )
+
+bayes_itq_broad_fit <-
+  rstanarm::stan_glmer(
+    formula = CatchShare ~ gdp_center + (1|MainCat),
+    family = "binomial",
+    data = downjoin,
+    cores = 4
+  )
+
+summary(itq_broad_fit)
+
+aug_itq_broad_fit <- broom::augment(itq_broad_fit) %>% 
+  mutate(pred = predict(itq_broad_fit, type = "response"))
+
+aug_itq_broad_fit %>% 
+  ggplot(aes(CatchShare, pred, group = CatchShare)) + 
+  geom_boxplot()
+
+aug_itq_broad_fit %>% 
+  ggplot(aes(gdp_center, pred, color = MainCat)) + 
+  geom_point()
+
+aug_itq_broad_fit %>% 
+  ggplot(aes(MainCat, pred)) + 
+  geom_boxplot()
+
+plot(bayes_itq_broad_fit)
+
+pps = rstanarm::posterior_predict(bayes_itq_broad_fit) %>% 
+  colMeans()
+
+aug_itq_broad_fit <- broom::augment(bayes_itq_broad_fit) %>% 
+  mutate(pred = pps)
+
+aug_itq_broad_fit %>% 
+  ggplot(aes(CatchShare, pred, group = CatchShare)) + 
+  geom_boxplot()
+
+aug_itq_broad_fit %>% 
+  ggplot(aes(gdp_center, pred, color = MainCat)) + 
+  geom_point()
+
+aug_itq_broad_fit %>% 
+  ggplot(aes(MainCat, pred)) + 
+  geom_boxplot()
 

### 2019-01-11 documents/figs-and-calcs.Rmd
a few improvements to catch share regression

@@
                               yname = "CatchShare")
+downjoin %>% 
+  ggplot(aes(log(MSY),fill = CatchShare)) + 
+  geom_density()
 
@@
   glm(
-    formula = CatchShare ~ gdp_center + MainCat,
+    formula = CatchShare ~ gdp_center + MainCat + log(MSY),
     family = "binomial",
@@
 
-aug_itq_broad_fit %>% 
-  ggplot(aes(CatchShare, pred, group = CatchShare)) + 
-  geom_boxplot()
+orig_itq_broad_fit <- join_mutate %>% 
+  mutate(pred = predict(itq_broad_fit, type = "response", newdata = join_mutate))
+
+catchshare_pred_plot <- orig_itq_broad_fit %>% 
+  ggplot(aes(pred,CatchShare == 1,fill = CatchShare == 1)) + 
+  ggridges::geom_density_ridges(show.legend = FALSE) +
+  geom_vline(aes(xintercept = 0.5), linetype = 2, color = "red") +
+  labs(y = "Is Catch Share?",
+       x = "Probability of Catch Share",
+       caption = "Classified as catch share if p>0.5")
 
@@
 
-plot(bayes_itq_broad_fit)
+catchshare_pred_plot
 
-pps = rstanarm::posterior_predict(bayes_itq_broad_fit) %>% 
-  colMeans()
+g <- pROC::roc(CatchShare ~ pred, data = orig_itq_broad_fit)
 
-aug_itq_broad_fit <- broom::augment(bayes_itq_broad_fit) %>% 
-  mutate(pred = pps)
-
-aug_itq_broad_fit %>% 
-  ggplot(aes(CatchShare, pred, group = CatchShare)) + 
-  geom_boxplot()
-
-aug_itq_broad_fit %>% 
-  ggplot(aes(gdp_center, pred, color = MainCat)) + 
-  geom_point()
-
-aug_itq_broad_fit %>% 
-  ggplot(aes(MainCat, pred)) + 
-  geom_boxplot()
+pROC::ggroc(g) + 
+  geom_abline(aes(intercept = 1, slope =  1), color = "red")
 

### 2019-01-12 documents/figs-and-calcs.Rmd
make figure nice

@@
 catchshare_pred_plot <- orig_itq_broad_fit %>%
-  ggplot(aes(pred,CatchShare == 1,fill = CatchShare == 1)) + 
-  ggridges::geom_density_ridges(show.legend = FALSE) +
+  ggplot(aes(pred, CatchShare == 1, fill = CatchShare == 1)) +
+  ggridges::geom_density_ridges(show.legend = FALSE, alpha = 0.75) +
   geom_vline(aes(xintercept = 0.5), linetype = 2, color = "red") +
@@
        x = "Probability of Catch Share",
-       caption = "Classified as catch share if p>0.5")
+       caption = "Classified as catch share if p>0.5") +
+  scale_x_continuous(limits = c(0, 1), expand = c(0, .01))
 
@@
 pROC::ggroc(g) + 
-  geom_abline(aes(intercept = 1, slope =  1), color = "red")
+  geom_abline(aes(intercept = 1, slope =  1), color = "red") + 
+  labs(x = "")
 

### 2019-01-12 documents/figs-and-calcs.Rmd
working on mapping

--- 2019-01-11 documents/figs-and-calcs.Rmd
@@
 
+#upside projection data
 projection_data <- readRDS(here("data","projection_data.rds")) %>% 
@@
 
-projection_data_mutate <- projection_data  %>%
+#GDP data
+gdp_all <- read_excel(here("data","un_gdp_2016.xls"))
+
+#EDF TURF data
+edf_turf <- read_excel("data/EDF_TURF_data.xlsx") %>%
+  select("Country", "SciName","CatchShare") %>%
+  filter(SciName != "NA")
+
+#DiscoverTURFs data
+d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx") %>%
+  select("Country", "SciName", "CatchShare") %>%
+  filter(SciName != "NA")
+
+#ISSCAAP Codes
+isscaap <- read_csv("data/meta_isscaap_codes.csv")
+#######################################################
+
+#get turf data to have species category codes
+
+all_turfs <- plyr::join(d_turfs, edf_turf, by= c("Country", "SciName", "CatchShare"), type = "full" ) %>%
+  distinct()
+
+turfs <- plyr::join(all_turfs, isscaap, by= c("SciName")) %>%
+  filter(SciName !="NA")%>%
+  filter(SpeciesCat != "NA")
+
+#add the turf data to upside
+projection_turfs <- merge(projection_data, turfs, by = c("Country", "SciName", "SpeciesCat", "CatchShare"), all = T)
+
+projection_turfs_mutate <- projection_turfs  %>%
   mutate(MainCat = case_when(
@@
 
-join_mutate <- left_join(projection_data_mutate, gdp, by = "Country") %>% 
+#question here, will the filter remove out when year is NA? the turf data doesn't have this resolution; edf does have start date though
+join_mutate <- left_join(projection_turfs_mutate, gdp, by = "Country") %>% 
   filter(Year == max(Year))

### 2019-01-12 updside_turfs.R

@@ -2,26 +2,75 @@ library(tidyverse)
 library(readxl)
 library(tidyxl)
 library(here)
+library(dplyr)
 
+#######
+##Data#
+#######
 
-#Load in upside projection data
+#upside projection data
 projection_data <- readRDS(here("data","projection_data.rds")) %>% 
   filter(Scenario == "Historic")
 
-#Load in GDP data
+#GDP data
 gdp_all <- read_excel(here("data","un_gdp_2016.xls"))
 
-#Load EDF TURF data
-edf_turf <- read_excel("data/EDF_TURF_data.xlsx")
+#EDF TURF data
+edf_turf <- read_excel("data/EDF_TURF_data.xlsx") %>%
+  select("Country", "SciName","CatchShare") %>%
+  filter(SciName != "NA")
 
-#Load in DiscoverTURFs data
-d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx")
+#DiscoverTURFs data
+d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx") %>%
+  select("Country", "SciName", "CatchShare") %>%
+  filter(SciName != "NA")
+
+#ISSCAAP Codes
+isscaap <- read_csv("data/meta_isscaap_codes.csv")
+#######################################################
+
+#get turf data to have species category codes
+
+all_turfs <- plyr::join(d_turfs, edf_turf, by= c("Country", "SciName", "CatchShare"), type = "full" ) %>%
+  distinct()
+
+turfs <- plyr::join(all_turfs, isscaap, by= c("SciName")) %>%
+  filter(SciName !="NA")%>%
+  filter(SpeciesCat != "NA")
+
+#add the turf data to upside
+projection_turfs <- merge(projection_data, turfs, by = c("Country", "SciName", "SpeciesCat", "CatchShare"), all = T)
+
+projection_turfs_mutate <- projection_turfs  %>%
+  mutate(MainCat = case_when(
+    SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",
+    SpeciesCat == 31 | SpeciesCat == 32 | SpeciesCat == 33 | SpeciesCat == 34 | SpeciesCat     == 35 | SpeciesCat == 37 ~ "3",
+    SpeciesCat == 42 | SpeciesCat == 43 | SpeciesCat == 44 | SpeciesCat == 45 | SpeciesCat      == 47 ~ "4",
[…]

### 2019-01-12 documents/figs-and-calcs.Rmd
need to commit, restarting R

@@
 
+projection_data_fig1 <- readRDS(here("data","projection_data.rds")) %>% 
+  filter(Scenario == "Historic") %>%
+  group_by(IdOrig) %>% 
+  filter(Year == max(Year))%>%
+  filter(Dbase != "SOFIA") %>%
+  filter(IdLevel != "Neis")
+
+projection_data_fig1$CatchShare <- as.factor(projection_data_fig1$CatchShare)
+
+fig_1 = projection_data_fig1 %>%
+  ggplot(aes(BvBmsy, FvFmsy, colour = CatchShare, size =MSY, alpha = MSY )) + 
+  geom_point() + 
+  coord_cartesian(xlim = c(0,3), ylim = c(0,4))+
+
+fig_1
+
 ```
@@
 ```{r}
+
+library(sf)
+library(ggplot2)
+#library(tmap)
+
+projection_data_fig2 <- readRDS(here("data","projection_data.rds")) %>% 
+  filter(Scenario == "Historic") %>%
+  group_by(IdOrig) %>% 
+  filter(Year == max(Year))%>%
+  filter(Dbase != "SOFIA") %>%
+  filter(IdLevel != "Neis") %>%
+  select( IdOrig, Country, CatchShare)
+
+colnames(projection_data_fig2) <- c("IdOrig", "CNTRY_NAME","CatchShare")
+projection_data_fig2[projection_data_fig2 =="USA"] <- "United States"
+
+#alreay in 4326; projection = WGS84
+countries <- st_read(dsn = "countries_shapefiles", layer = "Countries_WGS84")%>%
+  select(CNTRY_NAME)
+plot(countries)
+
+projection_spatial <- dplyr::left_join(projection_data_fig2, countries, by = "CNTRY_NAME")
+projection_spatial <- st_as_sf(projection_spatial)
+
+fig_2 = ggplot() +
+  geom_sf(data= projection_spatial, color = CatchShare)
+
+fig_2
+#plot(projection_spatial)
+
+#tm_shape(countries) +
+ # tm_polygons() +
+  #tm_shape(projection_spatial, colour = CatchShare)
 

### 2019-01-12 documents/figs-and-calcs.Rmd
figure 2: mapping countries with an without ITQs

--- 2019-01-12 documents/figs-and-calcs.Rmd
@@
 ```{r}
+
+library(sf)
+library(ggplot2)
+#library(tmap)
+
+projection_data_fig2 <- readRDS(here("data","projection_data.rds")) %>% 
+  filter(Scenario == "Historic") %>%
+  #group_by(IdOrig) %>% 
+  filter(Year == max(Year))%>%
+  filter(Dbase != "SOFIA") %>%
+  filter(IdLevel != "Neis") %>%
+  select(Country, CatchShare) %>%
+  distinct() %>%
+  filter(CatchShare == "1")
+
+colnames(projection_data_fig2) <- c("CNTRY_NAME","CatchShare")
+projection_data_fig2[projection_data_fig2 =="USA"] <- "United States"
+projection_data_fig2$CatchShare <- as.factor(projection_data_fig2$CatchShare)
+
+#alreay in 4326; projection = WGS84
+countries <- st_read(dsn = "countries_shapefiles", layer = "Countries_WGS84")%>%
+  select(CNTRY_NAME)
+#plot(countries)
+
+projection_spatial <- merge(projection_data_fig2, countries, by = "CNTRY_NAME", all.y =TRUE)
+projection_spatial$CatchShare <- as.numeric(projection_spatial$CatchShare)
+projection_spatial[is.na(projection_spatial)] <- 0
+projection_spatial$CatchShare <- as.factor(projection_spatial$CatchShare)
+projection_spatial <- st_as_sf(projection_spatial)
+
+fig_2 = ggplot() +
+  geom_sf(data= projection_spatial, aes(fill = CatchShare))
+
+fig_2
 

### 2019-01-12 lab_notebook.Rmd
figure 2: mapping countries with an without ITQs

@@
 
-#cooperative data from "Conservation incentives and collective choices in cooperative fisheries" paper (Ovando et al 2013)
+#cooperative data from "Conservation incentives and elective choices in cooperative fisheries" paper (Ovando et al 2013)
 jc_coop <- read_csv("data/clean_cooperatives_data.csv")
@@
 ITQ: 4,115,210 = 5.1%
+
+1/11/2019
+
+geom_point(stat=, fun.y="medium") +
+    stat_summary(fun.y="medium", geom="point")

### 2019-01-12 documents/figs-and-calcs.Rmd
worked on fig 3

@@
 library(ggplot2)
-#library(tmap)
 
@@
 Medians for RBFM and non-RBFM fisheries are shown as triangles.
+
+```{r}
+
+projection_data_fig3 <- readRDS(here("data","projection_data.rds")) %>% 
+  filter(Scenario == "Historic") %>%
+  group_by(IdOrig) %>% 
+  filter(Year == max(Year))%>%
+  filter(Dbase == "RAM") %>%
+  filter(IdLevel != "Neis")
+
+#projection_data_fig3$CatchShare <- as.factor(projection_data_fig3$CatchShare)
+
+projection_data_fig3$CatchShare[projection_data_fig3$CatchShare == "0"]<- "No RBFM"
+projection_data_fig3$CatchShare[projection_data_fig3$CatchShare == "1"]<- "RBFM"
+
+fig_3 = projection_data_fig3 %>%
+  ggplot(aes(BvBmsy, FvFmsy, colour = CatchShare, size =MSY, alpha = MSY)) + 
+  geom_point() + 
+  coord_cartesian(xlim = c(0,3), ylim = c(0,4))+
+  scale_alpha(range = c(0.5, 1))+
+  theme_minimal() +
+  geom_hline(aes(yintercept=1))+
+  geom_vline(aes(xintercept=1))+
+  xlab("B/Bmsy")+
+  ylab("F/Fmsy") +
+  ggtitle("Figure 3")
+
+fig_3
+
+```
 

### 2019-01-12 documents/figs-and-calcs.Rmd
saving figures to folder in documents/figures

@@
 
-#projection_data_fig3$CatchShare <- as.factor(projection_data_fig3$CatchShare)
+#seperate out with and without catch sahre and then calcualte geo median
+#download either geo_median or Gmedian once updated computer
+median_math <- projection_data_fig3 %>%
+  ungroup() %>%
+  select(BvBmsy,FvFmsy, CatchShare) %>%
+ group_by(CatchShare) %>%
+    na.omit() %>%
+    summarize( y=median(BvBmsy,FvFmsy))
 

### 2019-01-12 documents/figs-and-calcs.Rmd
finished basic figures 1,2,3 in documents/figures folder

--- 2019-01-12 documents/figs-and-calcs.Rmd
@@
 
-fig_1 = mtcars %>% 
-  ggplot(aes(mpg)) + 
-  geom_histogram()
-
-ggsave(here("figures","figure-1.pdf"), fig_1)
-
 projection_data_fig1 <- readRDS(here("data","projection_data.rds")) %>% 
@@
 
-projection_data_fig1$CatchShare <- as.factor(projection_data_fig1$CatchShare)
+projection_data_fig1$Dbase[projection_data_fig1$Dbase == "RAM"]<- "Stock Assessed"
+projection_data_fig1$Dbase[projection_data_fig1$Dbase == "FAO"]<- "Stock Not Assessed"
+
+assessed <- projection_data_fig1%>% filter(Dbase == "Stock Assessed")
+notassessed <- projection_data_fig1 %>% filter(Dbase == "Stock Not Assessed")
 
 fig_1 = projection_data_fig1 %>%
-  ggplot(aes(BvBmsy, FvFmsy, colour = CatchShare, size =MSY, alpha = MSY )) + 
+  ggplot(aes(BvBmsy, FvFmsy, colour = Dbase, size =MSY, alpha = MSY)) + 
   geom_point() + 
   coord_cartesian(xlim = c(0,3), ylim = c(0,4))+
+  scale_alpha(range = c(0.5, 1))+
+  theme_minimal() +
+  geom_hline(aes(yintercept=1))+
+  geom_vline(aes(xintercept=1))+
+  xlab("B/Bmsy")+
+  ylab("F/Fmsy") +
+  ggtitle("Figure 1")+
+  geom_point(data= assessed, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "red", shape = 17) +
+  geom_point(data= notassessed, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "blue", shape = 17)
 
 fig_1
+
+#ggsave(here("documents/figures","figure-1.pdf"), fig_1)
 
@@
 projection_data_fig2[projection_data_fig2 =="USA"] <- "United States"
+projection_data_fig2[projection_data_fig2 =="Russian Federation"] <- "Russia"
 projection_data_fig2$CatchShare <- as.factor(projection_data_fig2$CatchShare)
@@
 fig_2 = ggplot() +
-  geom_sf(data= projection_spatial, aes(fill = CatchShare))
+  geom_sf(data= projection_spatial, aes(fill = CatchShare)) +
+  ggtitle("Figure 2")
 
 fig_2
+
+#ggsave(here("documents/figures","figure-2.pdf"), fig_2)
 
@@
 
-#projection_data_fig3$CatchShare <- as.factor(projection_data_fig3$CatchShare)
-
 projection_data_fig3$CatchShare[projection_data_fig3$CatchShare == "0"]<- "No RBFM"
 projection_data_fig3$CatchShare[projection_data_fig3$CatchShare == "1"]<- "RBFM"
+
+rbfm <- projection_data_fig3%>% filter(CatchShare == "RBFM")
+no_rbfm <- projection_data_fig3 %>% filter(CatchShare == "No RBFM")
 
@@
   ylab("F/Fmsy") +
-  ggtitle("Figure 3")
+  ggtitle("Figure 3") +
+  geom_point(data= rbfm, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "red", shape = 17) +
+  geom_point(data= no_rbfm, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "blue", shape = 17)
 
@@
 
+#ggsave(here("documents/figures","figure-3.pdf"), fig_3)
 ```
@@
 
+### didn't add turf data here yet because using SpeciesCat seems to not work
+
 projection_data <- readRDS(here("data","projection_data.rds")) %>% 
@@
 #EDF TURF data
-edf_turf <- read_excel("data/EDF_TURF_data.xlsx") %>%
+edf_turf <- read_excel(here("data/EDF_TURF_data.xlsx"))%>%
   select("Country", "SciName","CatchShare") %>%
@@
 #DiscoverTURFs data
-d_turfs <- read_excel("data/DiscoverTURFs_simple.xlsx") %>%
+d_turfs <- read_excel(here("data/DiscoverTURFs_simple.xlsx")) %>%
   select("Country", "SciName", "CatchShare") %>%
@@
 #ISSCAAP Codes
-isscaap <- read_csv("data/meta_isscaap_codes.csv")
+isscaap <- read_csv(here("data/meta_isscaap_codes.csv"))
 #######################################################
@@
 
-gdp_all <- read_excel(here("data","un_gdp_2016.xls"))
-
 gdp <- gdp_all %>%
@@
 join_mutate <- left_join(projection_turfs_mutate, gdp, by = "Country") %>% 
-  filter(Year == max(Year))
+  group_by(IdOrig) %>%
+  dplyr::mutate(max_year = max(Year)) %>% 
+  filter(max_year== 2012)
 

### 2019-01-12 documents/figs-and-calcs.Rmd
worked on calculations

@@
 
-```{r}
-
-```
+http://www.fao.org/3/i9540en/I9540EN.pdf
+"The total production included 80.0 million tonnes of food fish (USD 231.6 billion)"
+- farmed fish has exceeded wild caught
 
@@
 
+= 7%
+
 ```{r}
+
+projection_data_line65 <- readRDS(here("data","projection_data.rds")) %>% 
+  filter(Scenario == "Historic") %>%
+  group_by(IdOrig) %>% 
+  filter(Year == max(Year))%>%
+  filter(Dbase == "FAO") %>%
+  filter(IdLevel != "Neis")%>%
+  filter(CatchShare == "1")
+
+itq_catch <- sum(projection_data_line65$Catch)
+
+percent_global <- (itq_catch/80000000)*100
+percent_global
+#6.995134
 
@@
 
-Based on this calculation, we find that up to xx\% of global catch comes from TURFs and up to XX \% comes from cooperatives.
-In total, based on best available data to date,  we estimate that somewhere between XXX\% and XXX\% of global wild fish catch comes from all forms of RBFM combined.
+Based on this calculation, we find that up to xx\% (1.7%) of global catch comes from TURFs and up to XX \% (0.55%) comes from cooperatives.
+In total, based on best available data to date,  we estimate that somewhere between XXX\% (9.8%) and XXX\% (11.1%) of global wild fish catch comes from all forms of RBFM combined.
 The What kinds of fisheries make up this RBFM catch?
@@
 ```{r}
+
+library(dplyr)
+
+edf_turf <- read_excel(here("data/EDF_TURF_data.xlsx"))%>%
+  select("Country", "SciName","CatchShare") %>%
+  filter(SciName != "NA")%>%
+  mutate(turf = case_when(CatchShare == 1 ~ TRUE))
+
+#DiscoverTURFs data
+d_turfs <- read_excel(here("data/DiscoverTURFs_simple.xlsx")) %>%
+  select("Country", "SciName", "CatchShare") %>%
+  filter(SciName != "NA")%>%
+    mutate(turf = case_when(CatchShare == 1 ~ TRUE))
+
+projection_data_line70 <- readRDS(here("data","projection_data.rds")) %>% 
+  filter(Scenario == "Historic")%>%
+  separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))%>%
+  unite(assess_id_short, agency, stock, sep = "-") %>%
+  group_by(assess_id_short) %>% 
+  filter(Year == max(Year))%>%
+  filter(Dbase != "SOFIA") %>%
+  filter(IdLevel != "Neis")
+
+countries_ITQ <- read_excel(here("data/Countries_ITQ.xlsx"))%>%
+  group_by(assess_id_short) %>% 
+  filter(year == max(year))
+
+projection_corb <- left_join(projection_data_line70, countries_ITQ, by = c("assess_id_short"))
+
+projection_corb_1 <- left_join(projection_corb, d_turfs, by = c("Country", "SciName"))
+
+projection_corb_2 <- left_join(projection_corb_1, edf_turf, by = c("Country", "SciName"))
+
+#####Turf math for upper and lower bounds.
+###lower bounds just includes upside/corbette because those have fishery IDs associated with it so sure that those fisheies have turfs, the upper bound incorporates discover turfs and EDF data and links the country/scienfitic name of species to fisheries
+
+turf_catch_lower <- projection_corb%>%
+  filter(turf == "TRUE")
+sum(turf_catch_lower$Catch)
+#301,000 lower limit
+
+turf_catch_upper <- projection_corb_2%>%
+  filter(turf == "TRUE")
+sum(turf_catch_upper$Catch)
+#1,370,210 upper limit
+#upper bound of total percent of global catch from turf:
+1370210/80000000
+#0.01712763
+
+###cooperative estimates
+coop_catch <- projection_corb%>%
+  filter(coop == "TRUE")
+sum(coop_catch$Catch)
+#443231
+#percent of global catch from coop:
+443231/80000000
+#0.005540387
+
+###all rbfm estimate lower 
+rbfm_catch_low <-projection_corb%>%
+  filter(turf == "TRUE" | itq == "TRUE" | ivq == "TRUE" | iq == "TRUE" | coop == "TRUE")
+sum(rbfm_catch_low$Catch)
+#7863234
+7863234/80000000
+#0.09829043
+
+###all rbfm estimate upper 
+rbfm_catch_up <-projection_corb_2%>%
+  filter(turf == "TRUE" | itq == "TRUE" | ivq == "TRUE" | iq == "TRUE" | coop == "TRUE")
+sum(rbfm_catch_up$Catch)
+#8932444
+8932444/80000000
+#0.1116556
+
+#reported_2016 <- projection_corb_2 %>% filter(Year == "2016")
 
@@
 Anecdotal evidence suggests that large, industrial fisheries, often for mobile species are most likely to adopt some form of ITQ, while small-scale artisinal fisheries, often for benthic species, are most likely to adopt a TURF.
-To test this expectation, we built a dataset of XXX ITQ fisheries and XXX TURF fisheries, and matched them to the fishery classification in \cite{Upside}.
-This provided us with a dataset of XXX fisheries with the country, species or genus name, and some other ecological and economic characteristics.
+To test this expectation, we built a dataset of XXX (94) ITQ fisheries and XXX (221) TURF fisheries, and matched them to the fishery classification in \cite{Upside}.
+This provided us with a dataset of XXX (121) fisheries with the country, species or genus name, and some other ecological and economic characteristics.
 Conditional on adopting some form of RBFM, our goal was to estimate the likelihood of adopting an ITQ versus a TURF.
 To do so, we ran a logistic regression with ITQ on the left ha
+
+```{r}
+
+unique(turf_catch_upper$assess_id_short)
+#27 fisheries with turfs
+
+itqs <-projection_corb%>%
+  filter(itq == "TRUE" | ivq == "TRUE" | iq == "TRUE")
+unique(itqs$assess_id_short)
+#94
+
+turf_all_1 <- full_join(edf_turf, d_turfs, by= c("Country", "SciName"))
+projection_turf <- projection_corb %>%
+  filter(turf == "TRUE") %>%
+  select("Country", "SciName")
+
+turf_all <- full_join(projection_turf, turf_all_1, by= c("Country", "SciName"))%>%
+  ungroup()%>%
+  select(Country, SciName) %>%
+  distinct()
+
+#had information of 221 country/species combo for turf
+
+```
 
@@
 
-to all XX non-rbfm fisheries in the (however many fisheries are not catch shares in projection_data)
+to all XX (5360) non-rbfm fisheries in the (however many fisheries are not catch shares in projection_data)
 
 ```{r}
+
+projection_data_line107 <- readRDS(here("data","projection_data.rds")) %>% 
+  filter(Scenario == "Historic")%>%
+  group_by(IdOrig) %>% 
+  filter(Year == max(Year))%>%
+  select(IdOrig, CatchShare)%>%
+  filter(CatchShare == "0") %>%
+  distinct()
+#5360 fisheries without catch share
 
@@
 
-Using that approach, authors have estimated a benefit of global RBFM between \$XXX Billion and \$XXX Billion per year. see Costello et al. 2016
+Using that approach, authors have estimated a benefit of global RBFM between \$XXX ( $31 billion) Billion and \$XXX ($53 billion) Billion per year. see Costello et al. 2016
+
+1. Costello et al 2016 
+2050
+
+-	RBFM policy applied to just stocks of conservation concern = $31 billion in fisheries profit
+
+-	RBFM policy applied to all stocks = $53 billion in fisheries profit
+
+2. Original Sunken Billions (2009)
+
+- “current annual net benefits from marine capture fisheries are tens of billions of U.S. dollars less than the potential benefits”
+```{r}
+include_graphics("sunkenbillionstable.png")
+```
+
+3. Updated Sunken Billions (2012)
+
+-	economic losses of about $83 billion
 

### 2019-01-13 documents/figs-and-calcs.Rmd
prep for turfs
three types of classification up

@@
   select(Country, SciName) %>%
-  distinct()
+  distinct() %>% 
+  left_join(projection_data %>% select(Country, SciName,IdOrig) %>% unique())
 
@@
 
-all_turfs <- plyr::join(d_turfs, edf_turf, by= c("Country", "SciName", "CatchShare"), type = "full" ) %>%
+all_turfs <- dplyr::full_join(d_turfs, edf_turf, by= c("Country", "SciName", "CatchShare")) %>%
   distinct()
 
-turfs <- plyr::join(all_turfs, isscaap, by= c("SciName")) %>%
-  filter(SciName !="NA")%>%
-  filter(SpeciesCat != "NA")
+turfs <-
+  dplyr::left_join(all_turfs, unique(isscaap), by = c("SciName")) %>%
+  filter(SciName != "NA") %>%
+  filter(SpeciesCat != "NA") %>%
+  select(-CatchShare) %>%
+  mutate(turf = 1,
+         Year = 2012)
 
 #add the turf data to upside
-projection_turfs <- merge(projection_data, turfs, by = c("Country", "SciName", "SpeciesCat", "CatchShare"), all = T)
+projection_turfs <- full_join(projection_data, turfs, by = c("Country", "SciName", "SpeciesCat","Year"), all = T) %>% 
+  mutate(turf = ifelse(is.na(turf),0,1)) %>% 
+  mutate(CatchShare = ifelse(turf == 1,2, CatchShare))
 
-projection_turfs_mutate <- projection_turfs  %>%
-  mutate(MainCat = case_when(
-    SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",
-    SpeciesCat == 31 | SpeciesCat == 32 | SpeciesCat == 33 | SpeciesCat == 34 | SpeciesCat     == 35 | SpeciesCat == 37 ~ "3",
-    SpeciesCat == 42 | SpeciesCat == 43 | SpeciesCat == 44 | SpeciesCat == 45 | SpeciesCat      == 47 ~ "4",
-    SpeciesCat == 52 | SpeciesCat == 53 | SpeciesCat ==54 |  SpeciesCat == 55 | SpeciesCat     == 56 | SpeciesCat == 57 | SpeciesCat == 58 ~ "5",
-    SpeciesCat == 74 | SpeciesCat == 76 | SpeciesCat == 77 ~ "7"
-  ))
+check <- projection_turfs %>% 
+  filter(turf == 1)
+
+projection_turfs %>% 
+  group_by(CatchShare) %>% 
+  count()
+
+main_cat <- str_extract_all(projection_turfs$SpeciesCat,"^\\d", simplify = TRUE)
+
+projection_turfs$MainCat <- main_cat
+
+# projection_turfs <- projection_turfs  %>%
+#   mutate(MainCat = case_when(
+#     SpeciesCat == 22 | SpeciesCat == 23 | SpeciesCat == 24 ~ "2",
+#     SpeciesCat == 31 | SpeciesCat == 32 | SpeciesCat == 33 | SpeciesCat == 34 | SpeciesCat     == 35 | SpeciesCat == 37 ~ "3",
+#     SpeciesCat == 42 | SpeciesCat == 43 | SpeciesCat == 44 | SpeciesCat == 45 | SpeciesCat      == 47 ~ "4",
+#     SpeciesCat == 52 | SpeciesCat == 53 | SpeciesCat ==54 |  SpeciesCat == 55 | SpeciesCat     == 56 | SpeciesCat == 57 | SpeciesCat == 58 ~ "5",
+#     SpeciesCat == 74 | SpeciesCat == 76 | SpeciesCat == 77 ~ "7"
+#   ))
 
@@
 #question here, will the filter remove out when year is NA? the turf data doesn't have this resolution; edf does have start date though
-join_mutate <- left_join(projection_turfs_mutate, gdp, by = "Country") %>% 
+catch_shares <- left_join(projection_turfs, gdp, by = "Country") %>% 
   group_by(IdOrig) %>%
   dplyr::mutate(max_year = max(Year)) %>% 
-  filter(max_year== 2012)
+  filter(max_year== 2012,
+         CatchShare %in% c(0,1),
+         !is.na(gdp_center),
+         !is.na(MainCat),
+         Year == max_year) %>% 
+  ungroup() %>% 
+  mutate(MainCat = factor(MainCat))
 
-join_mutate$MainCat <- factor(join_mutate$MainCat)
+catch_shares_and_turfs <- left_join(projection_turfs, gdp, by = "Country") %>% 
+  group_by(IdOrig) %>%
+  dplyr::mutate(max_year = max(Year)) %>% 
+  filter(max_year== 2012,
+         CatchShare %in% c(1,2),
+          !is.na(gdp_center),
+         Year == max_year) %>% 
+  ungroup() %>% 
+  mutate(MainCat = factor(MainCat)) %>% 
+  mutate(CatchShare = CatchShare - 1)
 
-downjoin <- caret::downSample(x = select(join_mutate,-CatchShare),
-                              y = factor(join_mutate$CatchShare),
+everything <- left_join(projection_turfs, gdp, by = "Country") %>% 
+  group_by(IdOrig) %>%
+  dplyr::mutate(max_year = max(Year)) %>% 
+  filter(max_year== 2012,
+         Year == max_year,
+                   !is.na(gdp_center)) %>% 
+  ungroup() %>% 
+  mutate(MainCat = factor(MainCat))
+
+```
+
+```{r is-catch-share}
+
+downjoin <- caret::upSample(x = select(catch_shares,-CatchShare),
+                              y = factor(catch_shares$CatchShare),
                               yname = "CatchShare")
-downjoin %>% 
-  ggplot(aes(log(MSY),fill = CatchShare)) + 
-  geom_density()
 
@@
 
-bayes_itq_broad_fit <-
-  rstanarm::stan_glmer(
-    formula = CatchShare ~ gdp_center + (1|MainCat),
-    family = "binomial",
-    data = downjoin,
-    cores = 4
-  )
-
 summary(itq_broad_fit)
@@
 
-orig_itq_broad_fit <- join_mutate %>% 
-  mutate(pred = predict(itq_broad_fit, type = "response", newdata = join_mutate))
+orig_itq_broad_fit <- catch_shares %>% 
+  ungroup() %>% 
+  mutate(pred = predict(itq_broad_fit, type = "response", newdata = catch_shares))
 
@@
 
-aug_itq_broad_fit %>% 
-  ggplot(aes(gdp_center, pred, color = MainCat)) + 
-  geom_point()
-
-aug_itq_broad_fit %>% 
-  ggplot(aes(MainCat, pred)) + 
-  geom_boxplot()
-
-catchshare_pred_plot
-
 g <- pROC::roc(CatchShare ~ pred, data = orig_itq_broad_fit)
 
-pROC::ggroc(g) + 
+catch_share_roc <- pROC::ggroc(g) + 
   geom_abline(aes(intercept = 1, slope =  1), color = "red") + 
   labs(x = "")
+
+```
+
+```{r turf-v-cs}
+
+upjoin <-
+  caret::upSample(
+    x = select(catch_shares_and_turfs, -CatchShare),
+    y = factor(catch_shares_and_turfs$CatchShare),
+    yname = "CatchShare"
+  )
+
+cs_or_turf_fit <-
+  glm(
+    formula = CatchShare ~ gdp_center + SpeciesCatName,
+    family = "binomial",
+    data = upjoin
+  )
+
+summary(cs_or_turf_fit)
+
+aug_fit <- broom::augment(cs_or_turf_fit) %>% 
+  mutate(pred = predict(cs_or_turf_fit, type = "response"))
+
+orig_cs_or_turf_fit <- catch_shares_and_turfs %>%
+  ungroup() %>%
+  mutate(pred = predict(cs_or_turf_fit, type = "response", newdata = catch_shares_and_turfs))
+
+  cs_or_turf_pred_plot <- orig_cs_or_turf_fit %>%
+  ggplot(aes(pred, CatchShare == 1, fill = CatchShare == 1)) +
+  ggridges::geom_density_ridges(show.legend = FALSE, alpha = 0.75) +
+  geom_vline(aes(xintercept = 0.5), linetype = 2, color = "red") +
+  labs(y = "Is TURF?",
+       x = "Probability of TURF",
+       caption = "Classified as TURF if p>0.5") +
+  scale_x_continuous(limits = c(0, 1), expand = c(0, .01))
+
+g <- pROC::roc(CatchShare ~ pred, data = orig_cs_or_turf_fit)
+
+catch_share_turf_roc <- pROC::ggroc(g) + 
+  geom_abline(aes(intercept = 1, slope =  1), color = "red") + 
+  labs(x = "")
+
+```
+
+```{r multinom}
+
+upjoin <-
+  caret::upSample(
+    x = select(everything, -CatchShare),
+    y = factor(everything$CatchShare),
+    yname = "CatchShare"
+  )
+
+everything_fit <-
+  multinom(
+    formula = CatchShare ~ gdp_center + SpeciesCatName,
+    family = "binomial",
+    data = upjoin
+  )
+
+orig_everything_fit <- everything %>%
+  ungroup() %>%
+  mutate(pred = predict(everything_fit, type = "class", newdata = everything))
+
+confusion_matrix <- orig_everything_fit %>% 
+  group_by(CatchShare,pred) %>% 
+  summarise(n = length(MSY), tmsy = sum(MSY, na.rm = T)) %>% 
+  filter(!is.na(pred)) %>% 
+  ungroup() %>% 
+  # group_by(CatchShare) %>% 
+  mutate(pn = n / sum(n),
+         pmsy = tmsy / sum(tmsy)) %>% 
+  mutate(pnn = scales::percent(pn, accuracy = 1),
+         pnm = scales::percent(pmsy, accuracy = 1)) %>% 
+  ungroup() %>% 
+  mutate(CatchShare = fct_recode(factor(CatchShare),"Catch Share" = "1", "Non-RBFM" = "0", "TURF" = "2")) %>% 
+  mutate(pred = fct_recode(factor(pred),"Catch Share" = "1", "Non-RBFM" = "0", "TURF" = "2"))
+
+confusion_matrix %>% 
+  ggplot() + 
+  geom_tile(aes(pred,CatchShare,fill = pn),color = "black",alpha = 0.25) +
+  geom_text(aes(pred, CatchShare, label = pnn)) +
+  scale_fill_viridis_c() + 
+  scale_x_discrete(position = "top", name = "Predicted Management") + 
+  labs(y = "Observed Management")
+
+confusion_matrix %>% 
+  ggplot() + 
+  geom_tile(aes(pred,CatchShare,fill = pmsy),color = "black",alpha = 0.25) +
+  geom_text(aes(pred, CatchShare, label = pnm)) +
+  scale_fill_viridis_c() + 
+  scale_x_discrete(position = "top", name = "Predicted Management") + 
+  labs(y = "Observed Management")
 

### 2019-01-14 documents/figs-and-calcs.Rmd
added in example economic figures, started standardizing figure formats

@@
 library(here)
+library(hrbrthemes)
+library(extrafont)
+
+extrafont::loadfonts()
 
@@
   janitor::clean_names()
+
+fig_width <- 8
+
+fig_height <- 6
+
+theme_set(theme_ipsum(base_size = 14))
 
@@
 projection_data_fig1$Dbase[projection_data_fig1$Dbase == "RAM"]<- "Stock Assessed"
-projection_data_fig1$Dbase[projection_data_fig1$Dbase == "FAO"]<- "Stock Not Assessed"
+projection_data_fig1$Dbase[projection_data_fig1$Dbase == "FAO"]<- "Unassessed"
 
 assessed <- projection_data_fig1%>% filter(Dbase == "Stock Assessed")
-notassessed <- projection_data_fig1 %>% filter(Dbase == "Stock Not Assessed")
+notassessed <- projection_data_fig1 %>% filter(Dbase == "Unassessed")
+
+medians <- assessed %>% 
+  bind_rows(notassessed) %>% 
+  group_by(Dbase) %>% 
+  summarise(median_b = median(BvBmsy),
+            median_f = median(FvFmsy))
 
 fig_1 = projection_data_fig1 %>%
-  ggplot(aes(BvBmsy, FvFmsy, colour = Dbase, size =MSY, alpha = MSY)) + 
-  geom_point() + 
-  coord_cartesian(xlim = c(0,3), ylim = c(0,4))+
-  scale_alpha(range = c(0.5, 1))+
-  theme_minimal() +
+  ggplot() + 
   geom_hline(aes(yintercept=1))+
   geom_vline(aes(xintercept=1))+
+  geom_point(aes(BvBmsy, FvFmsy, colour = Dbase, size =MSY, alpha = MSY)) + 
+  coord_cartesian(xlim = c(0,2.5), ylim = c(0,4))+
+  theme_minimal() +
   xlab("B/Bmsy")+
   ylab("F/Fmsy") +
-  ggtitle("Figure 1")+
-  geom_point(data= assessed, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "red", shape = 17) +
-  geom_point(data= notassessed, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "blue", shape = 17)
+    geom_point(data= medians, aes(x=median_b,y=median_f, fill = Dbase),shape = 24, size = 10, alpha = 0.75)  + 
+  scale_color_discrete(name = '') + 
+    scale_fill_discrete(name = '') + 
+  scale_size_continuous(labels = scales::comma) + 
+  scale_alpha_continuous(labels = scales::comma, range = c(0.25,1))
 
@@
 
-#ggsave(here("documents/figures","figure-1.pdf"), fig_1)
+ggsave(here("figures","figure-1.pdf"), fig_1, width = fig_width, height = fig_height)
 
@@
 fig_2 = ggplot() +
-  geom_sf(data= projection_spatial, aes(fill = CatchShare)) +
-  ggtitle("Figure 2")
+  geom_sf(data= projection_spatial, aes(fill = CatchShare == 1), size = 0.1) +
+  scale_fill_discrete(name = "Has Catch Shares?") + 
+  ggthemes::theme_map()
 
-fig_2
+# fig_2
 
-#ggsave(here("documents/figures","figure-2.pdf"), fig_2)
+ggsave(here("figures","figure-2.pdf"), fig_2, height = fig_height, width = fig_width)
 
@@
 
+medians <- rbfm %>% 
+  bind_rows(no_rbfm) %>% 
+  group_by(CatchShare) %>% 
+  summarise(median_b = median(BvBmsy),
+            median_f = median(FvFmsy))
+
 fig_3 = projection_data_fig3 %>%
-  ggplot(aes(BvBmsy, FvFmsy, colour = CatchShare, size =MSY, alpha = MSY)) + 
-  geom_point() + 
-  coord_cartesian(xlim = c(0,3), ylim = c(0,4))+
-  scale_alpha(range = c(0.5, 1))+
-  theme_minimal() +
+  # mutate(CatchShare = ifelse(CatchShare == 1, "RBFM","No RBFM")) %>% 
+  ggplot() + 
   geom_hline(aes(yintercept=1))+
   geom_vline(aes(xintercept=1))+
+  geom_point(aes(BvBmsy, FvFmsy, colour = CatchShare, size =MSY, alpha = MSY)) + 
+  coord_cartesian(xlim = c(0,2.5), ylim = c(0,4))+
+  theme_minimal() +
   xlab("B/Bmsy")+
   ylab("F/Fmsy") +
-  ggtitle("Figure 3") +
-  geom_point(data= rbfm, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "red", shape = 17) +
-  geom_point(data= no_rbfm, aes(x=median(BvBmsy),y=median(FvFmsy)),size = 3 ,color= "blue", shape = 17)
+    geom_point(data= medians, aes(x=median_b,y=median_f, fill = CatchShare),shape = 24, size = 10, alpha = 0.75)  + 
+  scale_color_discrete(name = '') + 
+    scale_fill_discrete(name = '') + 
+  scale_size_continuous(labels = scales::comma) + 
+  scale_alpha_continuous(labels = scales::comma, range = c(0.25,1))
 
@@
 
-#ggsave(here("documents/figures","figure-3.pdf"), fig_3)
+ggsave(here("figures","figure-3.pdf"), fig_3, height = fig_height, width = fig_width)
+
 ```
@@
 ## figure 4 bioeconomic figure to show in principle why you get increase in value from RBFM
+
+```{r fig-4}
+r <- 0.2
+
+k <- 100
+
+p <- 2
+
+msy <- r*k/4
+
+b_oa <- 0.25
+
+f_oa <- 2 - b_oa
+
+cost <- (p*msy * f_oa * b_oa) / (f_oa * r/2)^2
+
+demo <- tibble(biomass = seq(0,k, by = .1)) %>% 
+  mutate(b = biomass / (k / 2),
+         f = 2 - b,
+         Costs = cost * (f * r/2)^2,
+         Profits = p * msy * f * b - Costs,
+         Revenue =  p * msy * f * b,
+         catch = msy * f * b)
+
+b_mey <- demo$biomass[demo$Profits == max(demo$Profits)][1]
+
+demo <- demo %>% 
+  gather(metric,value, -biomass)
+
+figure_4 <- demo %>% 
+  filter(tolower(metric) %in% c("profits", "costs", "revenue")) %>% 
+  ggplot() + 
+  geom_line(aes(biomass,value, color = metric), size = 2) + 
+  ggsci::scale_color_simpsons(name = "") + 
+  theme_classic() + 
+  labs(y = "Value", x = "Fish Biomass") + 
+  geom_vline(aes(xintercept = b_oa * k / 2), color = "red", linetype = 2) + 
+  geom_vline(aes(xintercept = b_mey), color = "blue", linetype = 2) + 
+  scale_x_continuous(expand = c(0,0)) + 
+  scale_y_continuous(expand = expand_scale(mult = 0, add = c(0, .2)), limits = c(0,NA),
+                     breaks = c(0,max(demo$value)), labels = c("Low","High"))
+
+figure_4
+ggsave(here("figures","figure-4.pdf"), figure_4, height = fig_height, width = fig_width)
+```
 
@@
 ## figure 6 figure of bionomic equilibrium and shift in cost downward
+
+repeat analysis but with a grid of F/Fmsy by discount rate and cost parameter
+
+find fopt for any given scenario
+```{r fig-6, cache = TRUE}
+
+scenes <- purrr::cross_df(list(cost = seq(100,1500, by = 50), 
+                               discount = seq(0,0.5, by = 0.01)))
+
+popfoo <- function(f,cost, discount,r,k,p,d0 = 1,beta, time = 100, use = 0){
+
+  out <-
+    tibble(
+      b = rep(NA, time)
+    )
+
+  out$b[1] <- k * d0
+
+  for (t in 2:(time)) {
+    out$b[t] <-
+      out$b[t - 1] + out$b[t - 1] * r * (1 - out$b[t - 1] / k) - f * out$b[t - 1]
+
+  }
+
+  out <- out %>% 
+    mutate(f_rate = f,
+           catches = b * f_rate,
+           revenue = p * catches,
+           costs = cost*f_rate^2,
+           profits = revenue - costs,
+           year = seq_along(b))
+
+  npv <- sum(out$profits * (1 + discount)^-(0:(time - 1)))
+
+if (use == 0){
+  out <- -npv
+} else {
+  out <- out
+}
+
+}
+
+test <- nlminb(.05, popfoo, cost = 0, discount = 0, r = 0.2, k = 100, p = 2, beta = 2, lower = 0, upper = 0.99, time = 1000)
+
+check <- popfoo(f = test$par,cost = 0, discount = 0, r = 0.2, k = 100, p = 2, beta = 2,use = 2, time = 1000)
+
+fmeyfoo <- function(cost,discount,r = 0.2,k = 100,p = 2,beta = 2, time = 1000){
+
+  out <- nlminb(r/2,popfoo,cost = cost, discount = discount, r = r, k = k, p = p, beta = beta,use = 0, time = time)
+
+  out <- out$par
+
+}
+
+r <- 0.2
+
+k <- 100
+
+p <- 2
+
+beta <- 2
+
+time <- 200
+
+results <- scenes %>%
+  mutate(fmey = map2_dbl(
+    cost,
+    discount,
+    fmeyfoo,
+    r = r,
+    k = k,
+    p = p,
+    beta = beta,
+    time = time
+  )) %>%
+  mutate(mey_pop = pmap(
+    list(
+      f = fmey,
+      cost = cost,
+      discount = discount
+    ),
+    popfoo,
+      r = r,
+      k = k,
+      p = p,
+      beta = beta,
+      use = 2,
+      time = time
+    )
+  )
+
+results <- results %>% 
+  unnest()
+
+figure_6 <- results %>%
+  filter(year == max(year)) %>%
+  ggplot() +
+  geom_raster(aes(cost, discount, fill = b / (k/2)),
+              interpolate = TRUE) +
+  scale_x_continuous(
+    expand = c(0, 0),
+    breaks = c(min(scenes$cost), 750, 1500),
+    labels = c("Low", "Medium", "High"),
+    name = "Fishing Costs"
+  ) +
+  scale_y_continuous(expand = c(0, 0),
+                     name = "Discount Rate",
+                     labels = scales::percent) +
+  scale_fill_gradient2(
+    low = "tomato",
+    mid = "white",
+    high = "steelblue",
+    midpoint = 1,
+    name = "Bmey",
+    guide = guide_colorbar(frame.colour = "black",
+                           barheight = unit(15, "lines")),
+    limits = c(0,2)
+  ) + 
+  theme(panel.border = element_rect(color = "black",
+                                    fill = "transparent"))
+
+figure_6
+
+ggsave(here("figures","figure-6.pdf"), figure_6, height = fig_height, width = fig_width)
+```
 
@@
 
+projection_data <- readRDS(here("data","projection_data.rds")) %>% 
+  filter(Scenario == "Historic")
 unique(turf_catch_upper$assess_id_short)
@@
   filter(itq == "TRUE" | ivq == "TRUE" | iq == "TRUE")
-unique(itqs$assess_id_short)
+# unique(itqs$assess_id_short)
 #94
@@
 turf_all_1 <- full_join(edf_turf, d_turfs, by= c("Country", "SciName"))
+
 projection_turf <- projection_corb %>%
@@
 everything_fit <-
-  multinom(
+  nnet::multinom(
     formula = CatchShare ~ gdp_center + SpeciesCatName,

### 2019-01-15 documents/figs-and-calcs.Rmd
added in cooperatives, will check results in the morning

@@
   group_by(IdOrig) %>% 
-  filter(Year == max(Year))%>%
-  filter(Dbase == "FAO") %>%
-  filter(IdLevel != "Neis")%>%
-  filter(CatchShare == "1")
+  filter(Year == 2012) %>%
+  filter(CatchShare == 1)
 
@@
 turf_catch_lower <- projection_corb%>%
-  filter(turf == "TRUE")
+  filter(turf == TRUE)
 sum(turf_catch_lower$Catch)
@@
 turf_catch_upper <- projection_corb_2%>%
-  filter(turf == "TRUE")
-sum(turf_catch_upper$Catch)
+  filter(turf == TRUE)
+scales::percent(sum(turf_catch_upper$Catch) / 80e6, 1)
 #1,370,210 upper limit
@@
   filter(coop == "TRUE")
-sum(coop_catch$Catch)
+(sum(coop_catch$Catch)/ 80e6) %>% scales::percent(1)
 #443231
@@
 
+```
+
+## line 69
+
+based on this calculation, we find that
+
+```{r}
+
+a= projection_data %>% 
+  filter(Year == 2012) %>% 
+  group_by(Country, CatchShare) %>% 
+  count()
+
+scales::percent(mean(a$CatchShare),1)
 ```
@@
 
-```{r}
+```{r prepare-data}
 
@@
 
+taxa_lookup <- projection_data %>% 
+  select(SciName, SpeciesCat, SpeciesCatName) %>% unique()
+
+projection_data$clean_country <- countrycode::countrycode(projection_data$Country,"country.name","country.name")
+
 #GDP data
-gdp_all <- read_excel(here("data","un_gdp_2016.xls"))
+gdp <- read_excel(here("data","un_gdp_2016.xls")) %>% 
+  mutate(clean_country = countrycode::countrycode(Country,"country.name","country.name"))
 
 #EDF TURF data
-edf_turf <- read_excel(here("data/EDF_TURF_data.xlsx"))%>%
-  select("Country", "SciName","CatchShare") %>%
-  filter(SciName != "NA")
+edf_turf <- read_excel(here("data/EDF_TURF_data.xlsx")) %>%
+  select("Country", "SciName", "CatchShare") %>%
+  filter(SciName != "NA") %>%
+  mutate(clean_country = countrycode::countrycode(Country, "country.name", "country.name"))
 
@@
   select("Country", "SciName", "CatchShare") %>%
-  filter(SciName != "NA")
+  filter(SciName != "NA") %>% 
+    mutate(clean_country = countrycode::countrycode(Country,"country.name","country.name"))
 
@@
 
-all_turfs <- dplyr::full_join(d_turfs, edf_turf, by= c("Country", "SciName", "CatchShare")) %>%
+all_turfs <- dplyr::full_join(d_turfs, edf_turf, by= c("clean_country", "SciName", "CatchShare")) %>%
   distinct()
@@
 
+cooperatives <- read_csv(here("data","clean_cooperatives_data.csv"))
+
+coop_scinames <- taxize::comm2sci(unique(cooperatives$target_species))
+
+coops_names <- tibble(target_species = unique(cooperatives$target_species), SciName =  coop_scinames)  %>% 
+  unnest()
+
+coops <- cooperatives %>% 
+  select(fishery_id, host_country, target_species) %>% 
+  left_join(coops_names, by = "target_species") %>% 
+  left_join(taxa_lookup, by = c("SciName" = "SciName")) %>% filter(!is.na(SpeciesCat)) %>% 
+     mutate(clean_country = countrycode::countrycode(host_country,"country.name","country.name")) %>% 
+  mutate(cooperative = 1)
+
+projection_data %>% 
+  filter(Year == 2012) %>% 
+  group_by(CatchShare) %>% 
+  summarise(tc = sum(Catch, na.rm = T))
+
 #add the turf data to upside
-projection_turfs <- full_join(projection_data, turfs, by = c("Country", "SciName", "SpeciesCat","Year"), all = T) %>% 
+projection_turfs <- full_join(projection_data, turfs, by = c("clean_country", "SciName", "SpeciesCat","Year"), all = T) %>% 
   mutate(turf = ifelse(is.na(turf),0,1)) %>% 
-  mutate(CatchShare = ifelse(turf == 1,2, CatchShare))
+  mutate(CatchShare = ifelse(turf == 1,2, CatchShare)) %>%
+  left_join(coops %>% select(SciName, clean_country, cooperative), by = c("SciName", "clean_country")) %>% 
+  left_join(gdp, by = "clean_country") %>% 
+    mutate(turf = ifelse(cooperative == 1,1,turf))
+
+projection_turfs %>% 
+  filter(Year == 2012) %>% 
+  group_by(CatchShare) %>% 
+  summarise(tc = sum(Catch, na.rm = T))
 
@@
 
-gdp <- gdp_all %>%
-  select(Country, gdp_center) %>%
-  filter( gdp_center != "NA")
+# gdp <- gdp_all %>%
+#   select(Country, gdp_center) %>%
+#   filter( gdp_center != "NA")
 
 #question here, will the filter remove out when year is NA? the turf data doesn't have this resolution; edf does have start date though
-catch_shares <- left_join(projection_turfs, gdp, by = "Country") %>% 
+catch_shares <- projection_turfs %>% 
   group_by(IdOrig) %>%
@@
 
-catch_shares_and_turfs <- left_join(projection_turfs, gdp, by = "Country") %>% 
+catch_shares_and_turfs <- projection_turfs %>% 
   group_by(IdOrig) %>%
@@
   mutate(MainCat = factor(MainCat)) %>% 
-  mutate(CatchShare = CatchShare - 1)
+  mutate(CatchShare = CatchShare - 1) %>% 
+  select(-gdp) %>% 
+  rename(TURF = CatchShare,
+         gdp = gdp_center)
 
-everything <- left_join(projection_turfs, gdp, by = "Country") %>% 
+everything <- projection_turfs %>% 
   group_by(IdOrig) %>%
@@
 
+catch_shares_and_turfs %>% 
+  filter(Year == 2012) %>% 
+group_by(TURF) %>% 
+  summarise(n = length(Catch),
+            tc = sum(Catch, na.rm = T))
 upjoin <-
   caret::upSample(
-    x = select(catch_shares_and_turfs, -CatchShare),
-    y = factor(catch_shares_and_turfs$CatchShare),
-    yname = "CatchShare"
+    x = select(catch_shares_and_turfs, -TURF),
+    y = factor(catch_shares_and_turfs$TURF),
+    yname = "TURF"
   )
@@
   glm(
-    formula = CatchShare ~ gdp_center + SpeciesCatName,
+    formula = TURF ~ gdp + SpeciesCatName,
     family = "binomial",
-    data = upjoin
+    data = catch_shares_and_turfs 
   )
 
-summary(cs_or_turf_fit)
+covar_names <-  broom::tidy(cs_or_turf_fit)$term %>% 
+  str_replace_all("SpeciesCatName","")
+
+stargazer::stargazer(cs_or_turf_fit,
+                     covariate.labels =covar_names,
+                     intercept.top = TRUE,
+                     intercept.bottom = FALSE)
 
@@
 
+temp <- projection_turfs %>%
+  filter(SpeciesCatName %in% unique(catch_shares_and_turfs$SpeciesCatName),
+         Year == 2012) %>% 
+  select(-gdp) %>% 
+  rename(gdp = gdp_center)
+
+global_cs_or_turf_fit <- temp %>%
+  ungroup() %>%
+  mutate(pred = 1 - predict(cs_or_turf_fit, type = "response", newdata = temp)) %>% 
+  mutate(rbfm_type = ifelse(pred > 0.5, "ITQ","TURF"))
+
+rbfm_pred_summary <- global_cs_or_turf_fit %>% 
+  filter(!is.na(rbfm_type), CatchShare == 0) %>% 
+  group_by(rbfm_type) %>% 
+  summarise(n = length(MSY),
+            tmsy = sum(MSY, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  mutate(pn = n / sum(n),
+         pmsy = tmsy / sum(tmsy))
+
+country_pred_summary <- global_cs_or_turf_fit %>%
+  filter(!is.na(rbfm_type), CatchShare == 0,!is.na(clean_country)) %>%
+  group_by(clean_country, rbfm_type) %>%
+  summarise(n = length(MSY),
+            tmsy = sum(MSY, na.rm = TRUE)) %>%
+  group_by(clean_country) %>%
+  mutate(pn = n / sum(n),
+         pmsy = tmsy / sum(tmsy)) %>%
+  mutate(ttmsy = sum(tmsy)) %>% 
+  ungroup() %>% 
+  select(clean_country,ttmsy, rbfm_type,pmsy) %>% 
+  spread(rbfm_type,pmsy, fill = 0) %>% 
+  arrange(desc(ttmsy)) %>% 
+  slice(1:20) %>% 
+  mutate(`MSY Rank` = 1:nrow(.)) %>% 
+  select(-ttmsy) %>% 
+  rename("Country" = "clean_country") %>% 
+  select(Country, `MSY Rank`, ITQ,TURF) %>% 
+  mutate(ITQ = scales::percent(ITQ,1),
+         TURF = scales::percent(TURF,1))
+
+knitr::kable(country_pred_summary, format = "latex", longtable = TRUE)
+
   cs_or_turf_pred_plot <- orig_cs_or_turf_fit %>%
-  ggplot(aes(pred, CatchShare == 1, fill = CatchShare == 1)) +
+  ggplot(aes(pred, TURF == 1, fill = TURF == 1)) +
   ggridges::geom_density_ridges(show.legend = FALSE, alpha = 0.75) +
@@
 
-g <- pROC::roc(CatchShare ~ pred, data = orig_cs_or_turf_fit)
+g <- pROC::roc(TURF ~ pred, data = orig_cs_or_turf_fit)
 
@@
 ```{r}
-include_graphics("sunkenbillionstable.png")
+knitr::include_graphics("sunkenbillionstable.png")
 ```
@@
 -	economic losses of about $83 billion
+
+## line 249
+
+```{r}
+
+recent <- projection_data %>% 
+  filter(Year == 2012,
+         Scenario == "Historic")
+
+dim(recent)
+
+sum(recent$Catch)
+
+62399651 / 80e6
+
+```
 

### 2019-01-16 documents/figs-and-calcs.Rmd
updated tasks for juliette

@@
 ```
+
+# line 246
+
+XXX Get this table from Juliette
+
+\begin{center}
+\begin{tabular}{c|c|c|c|}
+Benefit or Cost & Estimate (Annual) & Method & Source\\\hline\hline
+Benefit & \$50 Billion & Global Aggregate & \shortcite{Sunken2009}\\
+Benefit & \$80 Billion & Global Aggregate & \shortcite{Sunken2017}\\
+Benefit & \$XX Billion & Fishery-by-Fishery & \shortcite{Costello2016}\\\hline
+Cost & \$XX Billion & Fishery-by-Fishery & \shortcite{Mangin2018}\\
+\end{tabular}
+\end{center}
+
+# mpa table
+
+As a result of these potential conservation and fishery effects, MPAs have been increasingly proposed as a solution to global fisheries sustainability.
+For example, the Convention on Biological Diversity's Strategic Plan for Biodiversity  call for 10\% of coastal waters to be protected inside MPAs by 2020.
+This call has been accompanied by the creation of large MPAs in places such as XX and XX.
+Table XXX shows the area covered by MPAs in the top-10 MPA countries of the world.
+Together, the MPAs in these countries represent the vast majority (XXX\%) of global coverage of MPAs, recognizing that the total global ocean covered by MPAs is still very small (XXX\%).
+
+XXX Juliette please fill out this table using spreadsheet I sent
+\begin{center}
+\begin{tabular}{c|c|c|c|c|}
+Country & MPA Size (km2) & \% EEZ Covered & Cum. \% Global MPAs & Cum. \% Ocean Coverage\\\hline\hline
+USA & 100 & 10\% & 2\% & .1\%\\\hline
+Global & xx & xx & xx & xx\\
+\end{tabular}
+\end{center}

### 2019-01-19 documents/figs-and-calcs.Rmd
commit to pull
figure tweeks

@@
 
-theme_set(theme_ipsum(base_size = 14))
+theme_set(theme_ipsum(base_size = 16) + theme(axis.title.x = element_text(size = 18), axis.title.y = element_text(size = 18)))
+
+projection_data <- readRDS(here("data","projection_data.rds")) %>% 
+  filter(Scenario == "Historic")
 
@@
 projection_spatial <- st_as_sf(projection_spatial)
+
+projection_spatial <-  projection_spatial %>% 
+    st_transform(crs = "+proj=moll +datum=WGS84")
 
@@
 
+labels <- demo %>% 
+  spread(metric,value) %>% 
+  mutate(oa = abs(Costs - Revenue))
+
+oa_y <- labels$Costs[labels$oa == min(labels$oa)][1]
+
+profits_y <- labels$Costs[labels$Profits == max(labels$Profits)][1]
+
+labs <- dplyr::tibble(x = c(b_oa * k / 2,b_mey),
+                      y = c(oa_y, profits_y),
+                      labs = c("A","B"))
+
 figure_4 <- demo %>% 
@@
   scale_y_continuous(expand = expand_scale(mult = 0, add = c(0, .2)), limits = c(0,NA),
-                     breaks = c(0,max(demo$value)), labels = c("Low","High"))
+                     breaks = c(0,max(demo$value)), labels = c("Low","High")) + 
+  ggrepel::geom_text_repel(data = labs,aes(x, y, label = labs),
+                            force =  20, size = 10)
 
@@
   ) +
+  stat_contour(breaks=c(1),aes(cost, discount, z = b / (k/2)), color ="black")+
   scale_y_continuous(expand = c(0, 0),
@@
 
+prices <- read_csv(here("data", "Exvessel Price Database.csv")) %>%
+  janitor::clean_names() %>%
+  rename(scientificname = scientific_name) %>%
+  mutate(log_exvessel = log(exvessel)) %>%
+  group_by(asfis_species, pooled_commodity, group_for_pairing) %>%
+  mutate(lag_exvessel = lag(exvessel)) %>%
+  ungroup()
+
 taxa_lookup <- projection_data %>% 
@@
 #add the turf data to upside
-projection_turfs <- full_join(projection_data, turfs, by = c("clean_country", "SciName", "SpeciesCat","Year"), all = T) %>% 
-  mutate(turf = ifelse(is.na(turf),0,1)) %>% 
-  mutate(CatchShare = ifelse(turf == 1,2, CatchShare)) %>%
-  left_join(coops %>% select(SciName, clean_country, cooperative), by = c("SciName", "clean_country")) %>% 
+projection_turfs <-
+  full_join(
+    projection_data,
+    turfs,
+    by = c("clean_country", "SciName", "SpeciesCat", "Year"),
+    all = T
+  ) %>%
+  mutate(turf = ifelse(is.na(turf), 0, 1)) %>%
+  left_join(
+    coops %>% select(SciName, clean_country, cooperative),
+    by = c("SciName", "clean_country")
+  ) %>%
+  mutate(cooperative = ifelse(is.na(cooperative), 0, 1)) %>%
   left_join(gdp, by = "clean_country") %>%
-    mutate(turf = ifelse(cooperative == 1,1,turf))
+  mutate(CatchShare = ifelse(is.na(CatchShare), 0, CatchShare)) %>%
+  mutate(CatchShare2 = dplyr::case_when(CatchShare == 1 ~ 1,
+                                        turf == 1 ~ 2,
+                                        cooperative == 1 ~ 3,
+                                        TRUE ~ 0)) %>%
+  mutate(turf = ifelse(cooperative == 1, 1, turf)) %>%
+  mutate(CatchShare = ifelse(turf == 1, 2, CatchShare)) %>%
+  left_join(prices, by = c("SciName" = "scientificname", 'Year' = 'year')) %>%
+  filter(Year == 2012) %>%
+  group_by(CatchShare) %>%
+  mutate(Catch = ifelse(is.na(Catch), mean(Catch, na.rm = TRUE), Catch)) %>%
+  ungroup()
 
@@
   filter(Year == 2012) %>% 
-  group_by(CatchShare) %>% 
-  summarise(tc = sum(Catch, na.rm = T))
+  group_by(CatchShare2) %>% 
+  summarise(tc = sum(Catch, na.rm = T)) %>% 
+  mutate(pcatch = scales::percent(tc / 80e6, accuracy = 1))
 
@@
   glm(
-    formula = CatchShare ~ gdp_center + MainCat + log(MSY),
+    formula = CatchShare ~ gdp_center + MainCat + log(MSY) + exvessel,
     family = "binomial",
@@
   glm(
-    formula = TURF ~ gdp + SpeciesCatName,
+    formula = TURF ~ gdp + SpeciesCatName + Catch,
     family = "binomial",

### 2019-01-20 documents/figs-and-calcs.Rmd
df for cost/benefits estimates table

--- 2019-01-16 documents/figs-and-calcs.Rmd
@@
 Together, the MPAs in these countries represent the vast majority (XXX\%) of global coverage of MPAs, recognizing that the total global ocean covered by MPAs is still very small (XXX\%).
-
 ```{r}
@@
 
+```{r}
+
+##note: estimate from mangin paper is in 2012. she gives an estimate for 2050 which is 15 billion, but I figured we want the more current one
+bene_cost <- c("Benefit", "Benefit", "Benefit", "Cost")
+estimate <- c("$50 Billion", "$80 Billion", "$53 Billion", "$7.6 Billion")
+method <- c("Global Aggregate", "Global Aggregate", "Fishery-by-Fishery", "Fishery-by-Fishery")
+source <- c("Sunken Billions 2009", "Sunken Billions 2017", "Costello et al 2016", "Mangin et al 2018")
+
+benefit_cost_table <- data.frame(bene_cost, estimate, method, source)
+
+colnames(benefit_cost_table) <-c("Benefit or Cost", "Estimate", "Method", "Source")
+
+```
+
 # mpa table

### 2019-01-21 documents/figs-and-calcs.Rmd
pre pull

--- 2019-01-19 documents/figs-and-calcs.Rmd
@@
     midpoint = 1,
-    name = "Bmey",
+    name = "B*/Bmsy",
     guide = guide_colorbar(frame.colour = "black",
@@
             tc = sum(Catch, na.rm = T))
+
+catch_shares_and_turfs %>% 
+  group_by(MainCat) %>% 
+  count()
+
 upjoin <-
@@
 
+ fit_recipe <- recipes::recipe( ~ SpeciesCat, data = catch_shares_and_turfs) %>% 
+     step_other(SpeciesCat, threshold = .02, other = "other values")
+
+rec <- prep(fit_recipe, training = catch_shares_and_turfs, retain = TRUE)
+
+dat <- juice(rec)
+ dat %>% group_by(SpeciesCat) %>% count()
+
+ catch_shares_and_turfs$short_SpeciesCat <- dat$SpeciesCat
+
 cs_or_turf_fit <-
   glm(
-    formula = TURF ~ gdp + SpeciesCatName + Catch,
+    formula = TURF ~ gdp + short_SpeciesCat,
     family = "binomial",
@@
 
-stargazer::stargazer(cs_or_turf_fit,
-                     covariate.labels =covar_names,
-                     intercept.top = TRUE,
-                     intercept.bottom = FALSE)
-
 aug_fit <- broom::augment(cs_or_turf_fit) %>% 
@@
 
+pROC::auc(pROC::roc(TURF ~ pred, data = orig_cs_or_turf_fit))
+
+spcat_match <- catch_shares_and_turfs %>% 
+  select(SpeciesCat, short_SpeciesCat) %>% 
+  unique()
+
 temp <- projection_turfs %>%
-  filter(SpeciesCatName %in% unique(catch_shares_and_turfs$SpeciesCatName),
-         Year == 2012) %>% 
+  left_join(spcat_match, by = "SpeciesCat") %>% 
+  filter(!is.na(short_SpeciesCat)) %>% 
   select(-gdp) %>% 
@@
 
-knitr::kable(country_pred_summary, format = "latex", longtable = TRUE)
+knitr::kable(country_pred_summary, format = "latex", longtable = TRUE, booktabs = TRUE)
 
@@
 
+summary(cs_or_turf_fit)
 ```
